### 2019-03-26 report.tex
updated version

\documentclass[twocolumn]{aastex62}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{color}
\usepackage{appendix}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}

\newcommand{\Log}{{\rm Log}}
\newcommand{\Ms}{{\rm M}_\odot}
\newcommand{\Zs}{{\rm Z}_\odot}
\newcommand{\au}{{\rm AU}}
\newcommand{\gw}{{\rm GW}}
\newcommand{\kl}{{\rm KL}}
\newcommand{\ibh}{{\rm IMBH}}
\newcommand{\imbh}{{\rm IMBH}}
\newcommand{\inn}{{\rm in}}
\newcommand{\out}{{\rm out}}
\newcommand{\bh}{{\rm BH}}
\newcommand{\bhu}{{\rm BH1}}
\newcommand{\bhd}{{\rm BH2}}
\newcommand{\ARGdf}{\texttt{ARGdf}}
\newcommand{\ARCHAIN}{\texttt{ARCHAIN}}

\graphicspath{{./}{./}}

\received{}
\revised{revised to \today}
\accepted{}

\submitjournal{ApJ (not yet ..)}

\shorttitle{IMRIs in GCs}
\shortauthors{Arca Sedda, M. and Amaro-Seoane, P.}

\begin{document}

\title{Intermediate mass ratio formation in globular clusters: perspectives for LISA sources formation}

\correspondingauthor{Manuel Arca Sedda}
\email{m.arcasedda@gmail.com}

\author{Manuel Arca Sedda and Pau Amaro-Seoane}
\affil{Zentrum f\"{u}r Astronomie der Universit\"{a}t  Heidelberg\\
Astronomisches Rechen-Institut\\
M\"onchhofstrasse 12-14\\
Heidelberg, D-69120, DE}
\affil{...}

\begin{abstract}
We study the formation and evolution of intermediate mass ratio inspirals (IMRIs) triggered by the interactions between stellar black holes and an intermediate black hole (IMBH) inhabiting. We show the probability for an IMRI to form is an increasing function of the IMBH mass, representing a viable channel for the development of gravitational wave sources that can be possibly observed with the future generation of detectors.
\end{abstract}

\keywords{black holes - supermassive black holes - galactic nuclei - gravitational waves}

\section{Introduction}

Intermediate mass black holes, with masses in the range $10^2-10^5\Ms$, might represent the missing link between stellar and supermassive mass black holes. Dense stellar systems, such as globular clusters (GCs), are thought to be ideal factories for IMBH production via formation and collapse of a very massive stars through stellar collisions \citep{zwart02, giersz15, mapelli16} or via multiple interactions and mergers between stars and stellar-mass BHs \citep{giersz15}. Unfortunately, a striking observational evidence for the presence of IMBHs inhabiting GCs is still missing due to the the little dynamical effects that these objects have on their surroundings. Indeed, models suggest that several processes can mimic an IMBH, like anisotropies in the GC kinematical properties \citep{zocchi}, or the presence of a dense cluster of stellar mass BHs that dominate the inner cluster centre \citep{AAG18a,AAG18b,AS16,vandermarel10}. Nevertheless, a few observational IMBHs candidates have been found for Galactic GCs \citep{noyola10,lu13,lanzoni13,kiziltan17} and their mass and influence radius might be possibly connected with the host cluster observational properties \citep{AAG18a}. Due to this, finding an unique way to unravel the presence of IMBHs in GCs represents one of the most interesting challenges in modern astronomy. Beside this, the presence of an IMBH sitting in the centre of a dense cluster represents a scenario particularly appealing from the perspectives of gravitational waves (GW) astronomy. Indeed, a compact remnants orbiting the IMBH can enter a regime where GWs emission dominates, leading to the formation of an intermediate mass-ratio inspiral \citep[IMRI,][]{konstantinidis13,haster16,leigh14}, a class of sources possible audible with the next generation of GW observatories like LISA \citep{seoane07,amaro12,seoane18}

However, in the highly dense regions that characterize star clusters centres, the formation of IMRIs is not a smooth process. Indeed, due to the continuous interactions with stars, an IMRI ``progenitor'', namely a tight IMBH-BH binary, might be subjected to strong perturbation induced, for instance by a passing-by BH. The three-body interaction involving the IMBH and the two BHs can lead to a variety of end states, including the formation of an IMRI, a stellar BH binary, the ejection of one BH, or even both, or the development of a head-on collision.

Quantifying the branching ratio for IMRIs formation constitute a fundamental step to assess the probability to observe these GW sources with the next generation of space-based detectors like LISA\footnote{\url{https://www.elisascience.org/}} \citep{seoane07}, TianQin \citep{tianqin16} or Taiji \citep{taiji17}.

In this paper, we model the potential formation of an IMRI from the interactions between an IMBH and two stellar mass BHs. To reach the aim, we use $N$-body simulations that take into account in particles' equations of motion both the star cluster gravitational potential and post-Newtonian corrections up to 2.5 order. Varying the IMBH and BHs masses, their orbital configuration, and the host cluster structural properties, we build-up three sets consisting of 2000 models each, which allow us to uncover three possible scenarios for IMRIs formation.

The paper is organized as follows: in Section \ref{num} we present and summarize the numerical setup used to model the IMBH - BH interaction, in Section \ref{met} we discuss the main properties of the simulations outputs, and the implications for GW astronomy, while Section \ref{res} is devoted to the results summary and conclusions.

\section{Initial conditions}
\label{met}

In this work, we study IMRIs formation via triple interactions involving an IMBH and two stellar mass BHs that inhabit in the centre of a massive star cluster. 
One of the two BHs is bound to the IMBH, while the second BH orbits around the IMBH-BH binary centre of mass. The triple orbital configuration can be dissected into an inner and an outer binary, as sketched in Figure \ref{fig:f1}. This simple picture is complicated by the fact that the triple cannot be considered as an isolated system, as other cluster members can affect its evolution.

\begin{figure}
    \centering
    \includegraphics[width=7cm]{triple}
    \caption{Sketch of the IMBH-BH-BH triple configuration.}
    \label{fig:f1}
\end{figure}

Therefore, the phase space that characterises the triple's main properties can be dissected into three groups:
\begin{itemize}
    \item {\bf Inner binary (IMBH+BH)}: depends on the IMBH and BH masses, $M_\ibh$ and $M_\bhu$, the binary semi-major axis $a_\inn$ and its eccentricity $e_\inn$.
    \item {\bf Outer binary (IMBH+BH+BH)}: depends on the third BH mass, $M_\bhd$, semi-major axis $a_\out$, eccentricity $e_\out$.
    \item {\bf Host cluster}: we model the host cluster as a \cite{Deh93} sphere, characterized by total mass, $M_c$, scale radius, $r_c$, and the inner slope of the density profile $\gamma$.
\end{itemize}

In order to unveil the link between IMRIs formation and IMBH properties, we select the IMBH mass among eight different values ${\rm Log}(M_\ibh/\Ms) = 2-2.5-3-3.5-4-4.5-5-5.5$. This range covers typical values of putative IMBH masses forming in stellar systems of various sizes, from young and open clusters, to globular clusters, and up to low-mass nuclear clusters and dwarf galaxies.

Stellar BH masses are selected between $M_{\rm min} = 10\Ms$ and $M_{\rm max} = 30\Ms$, a mass range typical of stellar environments with a metallicity $Z<0.25\Zs$ \citep{belczynski16,spera16}. 
From Figure 5 of \cite{belczynski16}, we find that the BH mass can be connected to the initial star mass via a simple power-law 
\begin{equation}
\left(\frac{m_\bh}{\Ms}\right) = A(Z) \left(\frac{m_*}{\Ms}\right)^{C(Z)} + B(Z),
\end{equation}
with the coefficient depending on the metallicity as summarized in Table \ref{tab:t1}.

Assuming that BH progenitor stars follow initially a standard \cite{kroupa01} initial mass function, $f(m_*) \propto m_*^-s$, we can infer BHs final mass distribution simply as $f(m_\bh)\propto m_\bh^{-s/C(Z)}$. This simple approximation leads to a slope $s/C(Z) = 1.71-1.92$.

However, we must take into account the fact that during clusters' early evolutionary stages stellar BHs sink into the centre due to mass segregation and start interacting strongly among each other.
As interactions take place, the heaviest BHs are expected to be either kicked out or accreted onto the IMBH seed \citep{giersz15,AAG18a}, potentially causing a strong depletion of BHs especially in the high-end tail of the mass distribution. We assume that the probability for a BH to be ejected or consumed in a merger scales with a weak power of the BH mass, namely $ \propto m_\bh^0.5$. Although quite arbitrary, such choice serves to account for the crucial role played by BHs interactions during the phases that contribute to the IMBH buildup. Given the assumptions above, our models are characterized by a mass function with total slope $\delta_\bh = -2.2$.

\begin{table}
    \centering
    \caption{Stellar - BH mass relation}
    \begin{tabular}{cccc}
        \hline
        \hline
        $Z$ & $A$ & $B$ & $C$ \\
        $\Zs$   &  & &  \\
    \hline    
        $0.005 $& $0.076\pm0.008$ & $3.8\pm0.3$ & $1.35\pm0.02$\\
        $0.25$  & $0.11\pm0.04$   & $0  $       & $1.20\pm0.07$\\
    \hline
    \end{tabular}
    \label{tab:t1}
\end{table}

Inner binary semi-major axis, $a_\inn$, is selected according to a distribution flat in logarithmic values, limited between $10$ and $315$ AU. Same distribution is assumed for the outer binary, but in this case $a_\out$ is chosen in two different ranges, either $a_\out=20-630$ AU or $630-1580$ AU. As detailed below, these ranges characterize two sets of simulations.
The eccentricity is assumed to follow a thermal distribution \citep{jeans19}, $P(e){\rm d}e = 2e{\rm d}e$ for both inner ($e_\inn$) and outer ($e_\out$) binary.

The cosine of the mutual orbital inclination between the inner and outer orbit, $\cos(i)$ is selected randomly between $-1$ and $1$.

The host cluster is assumed to be described by a \cite{Deh93} sphere, characterized by 
total mass $M_c$, scale radius $r_c$ and slope of the density profile $\gamma$.
The cluster length scale $r_c$ is selected randomly between 0.2 and 1.0 pc. For the cluster density slope, we assume a flat distribution with upper limit $\gamma \leq 1$.
To assign clusters' mass we either assume a scaling relation between the IMBH and the cluster mass, $M_\ibh - M_c$, or between the IMBH mass and the cluster velocity dispersion, $M_\ibh-\sigma_c$.

In the first case, we take advantage of the scaling relations based on numerical models of IMBH formation and observations of putative IMBHs in globular clusters \citep{zwart02,Lutzgendorf13,AS16}. In particular, we adopt the scaling provided by \cite{AS16}, connecting the host cluster mass $M_c$ with the total ''dark'' mass, inhabiting the cluster's centre, comprised of either an IMBH or a sizable population of stellar BHs
\begin{equation}
\Log \left(\frac{M_c}{\Ms}\right) = \alpha \Log \left(\frac{M_\ibh}{\Ms}\right) + \beta.
\label{mcmibh}
\end{equation}
with $\alpha = 0.999 \pm 0.001$ and $\beta = 2.23 \pm 0.009$.

Similarly to super-massive BHs in galactic nuclei, we can define the IMBH influence radius $R_{\rm inf}$, which delimits the region of space where IMBH dominates dynamics. This quantity can be connected to the cluster structural properties, namely
 \begin{equation}
 R_{\rm inf} = \frac{GM_\ibh}{\sigma_c^2} = \frac{M_\ibh}{M_c}R_{\rm hm},
 \end{equation}
 where we substituted the cluster velocity dispersion $\sigma_c$ with its value calculated at the cluster half-mass radius $R_{\rm hm}$, which in turn can be expressed in terms of the length scale and slope as
\begin{equation}
R_{\rm hm} = r_c(2^{1/(3-\gamma)}-1)^{-1}.
\end{equation} 
Combining the two equations above lead to 
\begin{equation}
R_{\rm inf} = \mu r_c(2^{1/(3-\gamma)}-1)^{-1},
\end{equation}
where $\mu = M_\ibh/M_c = 0.0058$ via Equation \ref{mcmibh}, thus implying that the the IMBH sphere of influence depends only on the cluster scale length and density slope.

In the second case, instead, we assume that GCs central regions represent a downsized version of galactic nuclei, thus the IMBH mass can be connected to the velocity dispersion inverting the so-called $M_\ibh - \sigma_c$ relation as 
\begin{equation}
     \Log \left(\frac{\sigma_c}{200{\rm km~s}^{-1}}\right) = \frac{1}{\alpha}\left(\left(\frac{\Log M_\ibh}{\Ms}\right) - \beta\right) ,
\end{equation}
with $\alpha = 4.24\pm0.41$ and $\beta=8.12\pm 0.08$ \citep{gultekin09}. Additionally, we associate to the cluster randomly a concentration parameter $c$ between $10.7$ and $131.4$, a range of values typical of dense star clusters characterized by an adimensional potential well $W_0 = 6-9$ \citep{king62}. The cluster mass is then calculated as $M_c = 2\sigma_c^2 c R_c / G$.

We develop three simulations sets, depending on the allowed range for $a_\out$ and the relation assumed to connect the IMBH and host cluster properties. For each set, we run a total of 2000 simulations equally distributed among 8 IMBH mass bins. Therefore, for each value of $M_\ibh$ we gather 250 simulations. The main properties of our runs are summarized in Table \ref{tab:t2}.

Our simulations are performed taking advantage of \ARGdf \citep{ASCD19}, a modified version of \ARCHAIN that implements post-Newtonian dynamics up to order 2.5 and {\it algorithmic regularization} to handle close encounters and strong collisions \citep{mikkola99,mikkola08}. Additionally, \ARGdf allows the user to take into account in particles' equations of motion the gravitational field generated by the host stellary system and a dynamical friction term. Simulations are halted either if one of the two BH merge with the IMBH, if one of the BHs is ejected away of if the simulated time exceeds $t = 10^3 P_{\rm max}$, where $P_{\rm max}$ identifies the maximum between the inner and outer binary orbital period.

\begin{table*}
\begin{center}
\caption{Main properties of our models}
\begin{tabular}{cccccccccccc}
\hline
model   & $f(\Log M_\ibh)$ & $M_\ibh$ & $\delta_\bh$ & $M_\bh$ & $a_\inn$ & $P(e_\inn)$ & $a_\out$ & $P(e_\out)$ &$P(\cos(i))$ &Cluster scaling & $N_{\rm sim}$\\ 
        &             & $\Ms$    &            & $\Ms$   & $\au$    &          & $\au$    &         &  &relation &\\
\hline 
0 & const & $10^2-5\times 10^5$ & $-2.2$ & $10-30$ & $10-315$ & $e^2$ & $20-630$ & $e^2$ & const&$M_\ibh -M_c$ & 2000\\
1 & const & $10^2-5\times 10^5$ & $-2.2$ & $10-30$ & $10-315$ & $e^2$ & $20-630$ & $e^2$ & const&$M_\ibh -\sigma_c$ & 2000\\
2 & const & $10^2-5\times 10^5$ & $-2.2$ & $10-30$ & $10-315$ & $e^2$ & $630-1580$ & $e^2$ &const &$M_\ibh -M_c$ & 2000\\
\hline
\end{tabular}
\end{center}
\label{tab:t2}
\end{table*}

\section{Results}
\label{res}

\subsection{IMRIs formation channels and subsequent evolution}

The evolution of the IMBH-BH-BH triple immersed in the host cluster gravitational field can lead to very different outcomes, as shown in Figure \ref{fig:f3}:
\begin{itemize}
    \item {\bf Disrupted triple} The three-body interaction undergoes a chaotic phases that ultimately lead to the ejection of a stellar BHs, whereas the inner binary either preserves its original components or undergoes a component swap.
    \item {\bf Hierarchical triple.} The triple arranges in a hierarchical configuration, with the outer BHs perturbing secularly the evolution of the inner binary. In this case, the inner binary can develop Kozai-Lidov oscillations \citep{kozai62,lidov62} that can trigger its eccentricity to grow to values close to unity. 
    \item {\bf Unstable triple.} The inner and outer binary are in an unstable configuration, whose evolution is mostly dominated by chaos.
\end{itemize}

\begin{figure*}
    \centering
    \includegraphics[width=16cm]{Sketch_IMRI}
    \caption{Schematic view of IMBH-BH-BH triple evolution.}
    \label{fig:f3}
\end{figure*}

In case of BH ejection, the evolution of remaining IMBH-BH will be due to the sum of two contributes, namely energy removal from binary-single interactions and GW emission. If the IMBH-BH entered the IMRI phase, binary-single interactions are expected to play little to no effect on its evolution \citep{seoane18}. In this case, the IMRI will continuously shrink emitting GW until coalescence, which takes place on a timescale \citep{peters64}
\begin{align}
t_\gw =&  \displaystyle \frac{5}{256}\frac{c^5 a_\inn^4 (1-e_\inn^2)^{7/2}}{G^3M_\ibh M_\bh(M_\ibh+M_\bh)} = \nonumber \\
       & 10^6{\rm ~yr}\left(\frac{a_\inn}{0.1\au}\right)^4\left(1-e_\inn^2\right)^{7/2}\times \nonumber \\ 
       & \times \left(\frac{10^3\Ms}{M_\ibh}\right) \left(\frac{30\Ms}{M_\bh}\right)\left(\frac{1030\Ms}{M_\ibh+M_\bh}\right).
\label{peters}
\end{align}

We note that for circular IMBH-BH binary in our model ($a_\inn=10\au$) the corresponding merger timescale is $t_\gw \sim 10^{14}$ yr, thus implying that some external perturbation is needed to trigger IMRI formation within a Hubble time.

In the second case, the triple arranges in a hierarchical configuration, whose evolution is dominated by secular perturbations. This mechanism, known as Kozai-Lidov \citep{kozai62,lidov62}, can induce periodic oscillations in the mutual inclination and the inner binary eccentricity. A parameter widely used to discern hierarchical triples is defined as \citep{Lithwick11,naoz11}
\begin{equation}
\epsilon_\kl = \frac{M_\imbh - m_\bh }{M_\imbh + m_\bh} \frac{a_{\inn}}{a_{\out}}\frac{e_{\out}}{(1-e_{\out}^2)},
\end{equation}
being the triple hierarchical if $|\epsilon| > 0.01$.

In this configuration, the eccentricity can increase up to values close to unity \citep{naoz11,naoz16}, leading the inner binary to continuously lose energy via bursts of GWs emitted at each pericentral passage. Therefore, the periodic eccentricity increase can drive the inner binary into the GW emission-dominated regime and trigger the formation of the IMRI. Kozai-Lidov oscillations cause a reduction of the merging timescale \citep[see for instance]{antonini12}
\begin{equation}
    t_{\rm gwKL} = \frac{t_\gw}{\sqrt{1-e_{\rm max}^2}},
\label{kozai}
\end{equation}
being $e_{\rm max}$ the maximum eccentricity achieved by the inner binary.

In the case of an unstable triple, the inner and outer binaries have similar orbital properties and dynamics is mostly dominated by chaotic interactions. According to the \cite{mardling01} criterion, a triple is unstable if
\begin{equation}
    \frac{a_\out}{a_\inn} < \frac{2.8}{1-e_\out}\left(1-\frac{0.3i}{\pi}\right)\left[\frac{(1+q_\out)(1+e_\out}{\sqrt{1-e_\out}}\right]^{2/5}, 
\end{equation}
being $q_\out = m_\out/(m_\imbh + m_\bh)$.

In our models, we calculate $\epsilon_\kl$ and $a_\out/a_\inn$ at the end of the simulations, in order to identify to which category a triple belongs. The merger time for the inner binary is calculated through Equation \ref{peters} for models categorized as ``Disrupted'' or ``Unstable'', whereas we use Equation \ref{kozai} for those identified as ``Hierarchical''.

\subsection{IMRIs properties}

We mark as IMRI candidates all IMBH-BH that, by the end of the simulations, have a merger time below 13 Gyr.

We find quite similar results in both SET0 and SET1, thus implying that both the host cluster mass does not change significantly from one method to the other, and that the external potential has a little effect on the triple evolution. The latter is due to the fact that we are looking in the immediate cluster centre vicinity, where dynamics is dominated by the IMBH.

In SET0, an IMRI develop in $212$ cases out of 2000, i.e. $f_{\rm mer} = 10.6\%$ of formation probability. Concerning the formation channel, $8\%$ of IMRIs formed from Disrupted, $66.5\%$ from Hierarchical, and $25.5\%$ from Unstable . Similarly, in SET1 we find $268$ IMRIs ($13.4\%$), $4.9\%$ of them formed from Disrupted, $67.9\%$ from Hierarchical triples, and $27.2\%$ from Unstable. All IMRIs formation probability for different channels are summarized in Table \ref{tab:t3}.

\begin{table}
    \centering
    \caption{IMRIs formation probability}
    \begin{tabular}{cccccc}
        \hline
        \hline 
        model& $f_{\rm mer}$ & $f_{\rm mer,D}$ & $f_{\rm mer,H}$ & $f_{\rm mer,U}$\\
             & $\%$& $\%$& $\%$& $\%$\\
        \hline
        SET0 & $10.6$ & $8.0$ & $66.5$ & $25.5$ \\
        SET1 & $13.4$ & $4.9$ & $67.9$ & $27.2$ \\
        \hline
    \end{tabular}
    \label{tab:t3}
\end{table}

Figure \ref{fig:f4} shows a comparison between the initial and final distribution of IMRI candidates' semi-major axis and eccentricity. We stress that both $a_\inn$ and $e_\inn$ are calculated from the last snapshot, thus they do not necessarily represent the binary orbital parameters promptly before the mergers. We postpone the discussion on the last stages of the IMRIs evolution to the next section.

The top panel shows clearly that the semi-major axis distribution of merging binaries differs significantly from the initial values, which is nearly uniform in the logarithms by assumption. The final distribution shows a peak at $\sim 10\au$, with a low-end extending down to $\lesssim 0.1 \au$. The eccentricity distribution, which is shown in the bottom panel, highlights that merging binaries tend to have a distribution steeper than the initial, thus implying that merger candidates are characterised by high eccentricities. Note that these distribution does not differentiate models with a different IMBH mass.

\begin{figure}
\centering
\includegraphics[width=8cm]{semiaxis}\\
\includegraphics[width=8cm]{ecce}
\caption{Top panel: semi-major axis distribution for the inner binary. The black steps refer to initial values for all the simulations performed, while the red filled steps refer only to merger binaries and final values. Bottom panel: the same as in top panel, but for the inner binary eccentricity.}
\label{fig:f4}
\end{figure}

\subsection{The role of the IMBH mass}

To explore the dependence between IMRI candidates eccentricity at formation and IMBH mass, we take the eccentricity directly from the last snapshot for models targeted as ``Disrupted'' and ``Unstable'', while for ``Hierarchical'' we record the maximum eccentricity. We then calculate the mean eccentricity value $\langle e_\gw\rangle$  in different mass bins, making the same for the subset of IMRI candidates, as shown in Figure \ref{fig:f4}. In general, it seems that, regardless of the set, IMRI candidates with masses below $5\times10^3\Ms$ have, on average, $\langle e_\gw\rangle$ larger compared to the whole simulations sample, while this trend reverses for heavier IMRIs.

The average eccentricity increases in the $10^2-5\times10^3\Ms$ mass range, peaking at around $500-1000\Ms$, and than decreases rapidly at increasing the IMBH mass.This implies that the evolution of the inner binary leads the eccentricity to achieve larger values in correspondence of lighter IMBHs.

We find that IMBHs with masses typical of star clusters $10^3<M_\ibh/\Ms<10^4$ are expected to form, on average, extremely eccentric IMRIs, while the eccentricity at formation attains more moderate values at IMBH masses typical of low-mass dwarf galaxies and nuclear clusters.

While affecting the eccentricity, the IMBH mass does not have a significant effect on the companion BH mass. Indeed, IMRIs light component masses follows the assumed BH mass distribution.

\begin{figure}
\centering
\includegraphics[width=8cm]{average_ecc_sets}\\
\caption{The average eccentricity ($\langle e_{\rm mer}\rangle$), calculated at the end of simulaitons in different IMBH mass bins, as a function of the IMBH mass and for different sets. We show the IMRIs average eccentricity SET0 (filled red points), SET1 (open blue squares), and SET2 (filled black points). The total average value is also marked for SET0 (dashed red line), SET1 (dotted blue line), and SET2 (dot-dashed black line). }
\label{fig:f5}
\end{figure}

In order to uncover what is the role played by the IMBH in determining IMRIs formation, we calculate the 
percentage of IMRIs formed in different mass bins. This quantity, namely $f_{\rm mer}$, represents {\it de facto} IMRIs formation probability. We find that $f_{¦rm mer}$ follows quite a precise trend, regardless of the set, thus in what follows we focus on SET0 only, for clarity's sake. Figure \ref{fig:f5} shows the $f_{\rm mer}-M_\ibh$ relation. We differentiate between IMRIs forming in disrupted triples, in a hierarchical or unstable configuration. 
Our results suggest that an IMBH-BH-BH has a $10\%$ of probability to arrange in a hierarchical configuration, regardless of the IMBH mass or the GW timescale. IMRIs formation probability, instead, increases weakly with IMBH mass, increasing from $\sim 2\%$ for $M_\ibh \simeq 10^2$ to up to $15\%$ for heavy IMBH, $M_\ibh>10^5\Ms$.

At IMBH mass values below $10^4\Ms$, we find that Hierarchical and Unstable systems contribute equally to the whole IMRI population, while at larger IMBH masses the majority of IMRIs is comprised of Unstable triples. IMRIs forming out of Disrupted triples give little contribution to the population, being their formation probability only $0.5-1\%$.

In the IMBH mass range $M_\ibh>10^3\Ms$, the IMRIs formation probability is well described by a simple powerlaw
\begin{equation}
f_{\rm mer} = \alpha \left(\frac{M_\ibh}{10^2\Ms}\right)^\beta,
\end{equation}  
with $\alpha = 0.7\pm0.2$ and $\beta = 0.45\pm0.03$.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{mergers.eps}
    \caption{Percentage for IMRIs formation as a function of IMBH mass. Red open squares shows all the models that are hierarchical at the end of the simulation. Open dark blue circles identify IMRIs. From larger to smaller circles, blue filled circles represent IMRIs formed from unstable, hierarchical, and disrupted triples.}
    \label{fig:f5}
\end{figure}

Our simulations suggest that whenever a three-body encounter occurs in a GC containing a $10^4\Ms$ IMBH, there is a $\sim 10\%$ of the probability for IMRIs formation and the eccentricity at formation is of the order of 0.95.

\subsection{Serendipitous formation of stellar BH binaries around an IMBH}

Among all the runs performed, we find two interesting cases, namely s151 and s400, in which the stellar mass BHs are initially sufficiently close to form a tight binary. In both cases, the IMBH mass is relatively small $M_{\ibh} = 100\Ms$, and the inner binary is comprised of the other two, stellar-mass, BHs. It is not surprising that a BH-BH pair forms in a model with low-mass IMBH, due to the lower velocity dispersion and the larger tidal radius needed for the binary to form without being ripped apart from the IMBH. In both cases, the BH-BH binary undergoes Kozai-Lidov oscillations, which periodically induce an increase in the binary eccentricity and the mutual inclination.

In model s400, the amplitude of the oscillation is minimal, the mutual inclination ranges between $i = 126-130^\circ$, while the eccentricity varies in the range $e = 0.882-0.904$. Although the KL effect is not very efficient in affecting the BH-BH evolution, the binary is sufficiently tight to have a short merger timescale, being $t_{\rm gw} \simeq 3\times 10^7$ yr.

In model s151, instead, the Kozai-Lidov effect is more effective, leading the inclination to vary strongly in the range $\sim 40-90^\circ$ and the eccentricity to rise up to $e = 0.99$. The time evolution of both $e$ and $i$ is shown in Figure \ref{F9}, together with the associated merger time-scale. 
In this particular simulation, the reduction of the merger time related to the episodic GW emission as described in Equation \ref{kozai}, trigger the BH binary coalesce in a time $5600$ times smaller than the time needed for the same binary to merge in isolation.

In both the cases that we find, the IMBH mass is $M_\ibh=100\Ms$. Heavier IMBHs would make BH-BH pairing much harder, because of the higher velocity dispersion and the larger gravitational influence. Having 250 simulations with $M_\ibh=100\Ms$ in each set, we can infer BH-BH formation probability as $P_{\rm bhb} = 0.8\%$.

\begin{figure}
\centering 
\includegraphics[width=8cm]{kozai_151}
\caption{Top panel: time evolution of the merger timescale for model number 151, in which two BHs pair together while the IMBH acts as a perturber. Central panel: mutual inclination as a function of time for the BH-BH pair in simulation number 151. Bottom panel: ecentricity as a function of time for the BH-BH pair in simulation number 151.}
\label{F9}
\end{figure}

\section{Gravitational waves}

In this section we investigate the properties of IMRIs formed in our model from the perspective of GW emission. To perform our study, we take from the last snapshot of all the simulations the inner binary semi-major axis and either the maximum eccentricity, if the triple is marked as ``Hierarchical'', or the actual eccentricity, if the triple is marked as ``Disrupted'' or ``Unstable''.

In the following, we indicate semi-major axis and eccentricity with $a$ and $e$, respectively, while the IMRI mass is labelled with $M_{\rm bin}$.

As long as the binary preserve a residual eccentricity, the GW signal is audible in a range of frequency, rather than being monochromatic. The peak frequency can be approximated as \citep{wen03, antonini12}
\begin{equation}
f_\gw = \frac{1}{\pi}\sqrt{\frac{GM_{\rm bin}}{a^3}}\frac{\left(1+e\right)^{1.1954}}{\left(1-e^2\right)^{3/2}},
\end{equation}  
being $M_{\rm bin}$ the merging binary total mass. Using this definition, we show in Figure \ref{F10} how the peak frequency and eccentricity vary for mergers in our models. In order to understand whether these sources can be audible to GW observatories, we superpose our calculations to the observational windows of the Laser Interferometer Space Antenna \citep[LISA\footnote{\url{https://www.elisascience.org/}},][]{amaro12}, the Deciherz Gravitational-Wave Observatory \citep[DECIGO\footnote{\url{http://tamago.mtk.nao.ac.jp/spacetime/decigo_e.html}},][]{seto01}, and the Einstein Telescope \citep[ET\footnote{\url{http://www.et-gw.eu/}},][]{punturo10}.

\begin{figure}
\centering
\includegraphics[width=8cm]{freq_evo}\\
\caption{Frequency (x-axis) and eccentricity (y-axis) evolution for merging binaries in our models. The color coding identifies the semi-major axis evolution. Black boxes are a coarse representation of observational windows for LISA, DECIGO and the Einstein Telescope. The horizontal lines mark two values of the eccentricity, namely $e=0.01-0.1$.}
\label{F10}
\end{figure}

We find that more than $95\%$ of the sources in both models transit into the $5\times 10^{-4} - 5\times 10^{-3}$ Hz band, where LISA is sensitive. Approximately $10\%$ instead are characterized by GW emission in DHz regime, being potentially observed with LIGO and, in the future, with DECIGO and ET.
The numbers of sources appearing in different bands are summarized in Table \ref{tab:t4}

 \begin{table*}
     \centering
     \caption{IMRI frequency bands}
     \begin{tabular}{ccccccc}
        \hline
        \hline
        model & IMRI - total number & $N_{\rm mHz}$ & $N_{\rm cHz}$ & $N_{\rm dHz}$ & $N_{\rm Hz}$ & $N_{\rm DHz}$ \\ 
              &                     &$0.5-5$ mHz    & $ 0.5-5$ cHz  &  $0.5-5$ dHz & $0.5-10$ Hz & $>1$ DHz \\
        \hline
        SET0 & $211$ & $204$ &  $207$ & $120$ & $46$ & $22$   \\
        SET1 & $268$ & $256$ &  $259$ & $144$ & $56$ & $28$   \\
        \hline
     \end{tabular}
     \label{tab:t4}
 \end{table*}

It is interesting to note that a handful of sources could have a non-negligible eccentricity both in the LISA and DECIGO observational band, while at larger frequencies the binaries are already completely circular. In order to better highlight the probability for low-frequency detectors to observe eccentric IMRIs, we show in Figure \ref{F11} the eccentricity distribution of sources entering the mHz and Hz frequency bands. We find that only $10\%$ of sources have high eccentricity in the LISA band, while for DECIGO this quantity is slightly smaller ($\sim 7\%$).

\begin{figure}
\centering
\includegraphics[width=8cm]{mergers_eccen}\\
\caption{Eccentricity distribution for IMRIs in our models. The eccentricity is calculated at the moment in which a source cross the mHz (red filled steps) or Hz frequency band (black steps).}
\label{F11}
\end{figure}

In order to infer whether these sources might be audible to GW observatories, we calculated the strain following \cite{kocsis12} for all the frequencies containing the $95\%$ of the emitted power. We assume a luminosity distance $D_L = 463$ Mpc (redshift $z=0.1$), and a 5 yr observation time. Figure \ref{F12} shows the evolution of the strain-frequency evolution for two different mergers, altogether with the eccentricity decrease due to GW circularization. One merger refers to an IMRI with total mass $M_H$

For the sake of visibility, we only show the strain associated to the dominant frequency. In the two models shown in the plot, the mergers outshine in the LISA band, where they spend most of their life, and slowly shift toward higher frequency, merging inside the LIGO observational band. These sources are of extreme interest since they can be used to further constrain and test the General Relativity theory, as their evolution can be monitored in both the low- and high-frequency regime.

\begin{figure}
\centering
\includegraphics[width=8cm]{example_signal}\\
\caption{Strain calculated for the dominant frequency for two different models, assuming an infinite observational time. We overlap the simulated data with sensitivity curves from several GW observatories.}
\label{F12}
\end{figure}

\section{Conclusions}

\begin{itemize}
\item {\bf Make your point!}
\end{itemize}

\section*{Acknowledgements}

Sonderforschungsbereich SFB 881 "The Milky Way System" (subproject Z2) of the German Research Foundation (DFG) for the financial support provided. This work benefited of financial support from the Alexander von Humboldt Foundation, which granted MAS research program ``The evolution of black holes from stellar to galactic scales''. 
This work benefited from support by the ISSI (Bern), through its Intern. Team prog. ref. no. 393 {\it The Evolution of Rich Stellar Populations \& BH Binaries} (2017-18).

\footnotesize{
\bibliographystyle{mn2e}
\bibliography{ASetal2015}
}

\end{document}

### 2019-03-27 report.tex
changed non-ascii character
Added section on merger rates

@@
 \newcommand{\gw}{{\rm GW}}
+\newcommand{\gc}{{\rm GC}}
 \newcommand{\kl}{{\rm KL}}
@@
 This quantity, namely $f_{\rm mer}$, represents {\it de facto} IMRIs formation probability.
-We find that $f_{¦rm mer}$ follows quite a precise trend, regardless of the set, thus in what follows we focus on SET0 only, for clarity's sake.
+We find that $f_{\rm mer}$ follows quite a precise trend, regardless of the set, thus in what follows we focus on SET0 only, for clarity's sake.
 Figure \ref{fig:f5} shows the $f_{\rm mer}-M_\ibh$ relation.
@@
 f_{\rm mer} = \alpha \left(\frac{M_\ibh}{10^2\Ms}\right)^\beta,
+\label{fmerg}
 \end{equation}  
-with $\alpha = 0.7\pm0.2$ and $\beta = 0.45\pm0.03$.
+with $\alpha = (7\pm2)\times 10^{-3}$ and $\beta = 0.45\pm0.03$.
 
@@
 Our simulations suggest that whenever a three-body encounter occurs in a GC containing a $10^4\Ms$ IMBH, there is a $\sim 10\%$ of the probability for IMRIs formation and the eccentricity at formation is of the order of 0.95.
+
+\subsection{IMRIs merger rate}
+
+{\bf Previous studies based on full consistent N-body simulations of star clusters containing IMBHs with various masses and general properties  \citep{konstantinidis13,haster16,leigh14, macleod16} have shown that binary formation involving an IMBH takes place at a rate of $R_{\rm bin} \sim 10^{-7}$ yr.
+Assuming typical ages for globular-like star clusters of $t_{\rm age}\sim 10^{10}$ yr and assuming that IMBH buildup occurs in the clusters early lifetime ($\lesssim 1$ Gyr), we can use the merger probability fitting function depicted in Equation \ref{fmerg} to infer IMRIs merger rate per typical cluster
+\begin{equation}
+    \Gamma(M_\ibh) = R_{\rm bin}t_{\rm age}f_{\rm mer} \sim 0.7\left(\frac{M_{\ibh}}{10^2\Ms}\right)^{0.45},
+\end{equation}
+ranging from $\Gamma_{\rm IMRI} = 7-50$ yr$^{-1}$ for $M_\ibh = 10^2-10^4\Ms$, respectively.
+
+To put such a quantity in the context of MW-like galaxies, we need to make assumptions on the IMBH putative mass function.
+As recently suggested by Arca Sedda et al (in prep.), out of the 151 Galactic GCs currently known, around 35 might be harbouring, at present time, an IMBH with mass in the range $10^3-10^4\Ms$.
+They find that the mass distribution of these putative IMBHs can be described by a Maxwellian in the form
+\begin{equation}
+    f(x_\ibh) = \frac{a}{\sigma\sqrt(2\pi)}\exp{\left(-\frac{\left(x_\ibh - \mu\right)^2}{ (2\sigma^2)}\right)},
+\end{equation}
+with $x_\ibh\equiv \Log M_\ibh$, and $a=0.14\pm0.3$ , $\mu = 4.01\pm0.09$ and $\sigma = 0.4\pm0.1 $.
+
+Combining equations above, we can define a IMRI merger rate for MW-like galaxies as
+\begin{equation}
+    \Gamma_{\rm MW} = f_\ibh N_\gc \int \Gamma(M_\ibh) f(x_\ibh) {\rm d}M_\ibh,
+\end{equation}
+where $f_\ibh N_\gc$ is the number of GCs containing an IMBH. This equation has analytical solution
+which has analytical solution
+\begin{align}
+ \frac{\Gamma_{\rm MW} (x_\ibh)}{f_\ibh N_\gc} =&   \frac{a}{2} (A + B\mu) {\rm erf}\left(\frac{x_\ibh-\mu}{\sigma\sqrt{2\pi}} \right) + \nonumber\\
+                                & - \frac{a}{\sqrt(2\pi)}B \sigma \exp{\left(\frac{-\left(x_\ibh-\mu\right)^2}{2\sigma^2}\right)},
+\end{align}
+ the coefficients $A = \alpha -\beta \Log(100)$ and $B \equiv \beta$ are conveniently manipulated from Equation \ref{fmerg}.
+
+Assuming a typical IMBH population spanning the mass range $10^2-10^4\Ms$, a number of GCs $N_\gc = 151$, a fraction $f_\ibh \simeq 35/151$ of GCs hosting an IMBH we can infer the MW-IMRI rate 
+\begin{equation}
+\Gamma_{\rm MW,IMRI} \simeq 4\times 10^{-3} {\rm MW}^{-1} {\rm yr}^{-1}
+\end{equation}
+
+}
 

### 2019-04-19 article.tex
Converted to MNRAS style, the file is now mn tex

--- 2019-03-27 report.tex
@@
 
-\shorttitle{IMRIs in GCs}
+\shorttitle{Formation of IMRIs}
 \shortauthors{Arca Sedda, M. and Amaro-Seoane, P.}
@@
 
-\title{Intermediate mass ratio formation in globular clusters: perspectives for LISA sources formation}
+\title{Formation and evolution of intermediate-mass ratio inspirals}
 
@@
 Heidelberg, D-69120, DE}
-\affil{...}
+\affil{
+Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC)\\
+at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain\\
+Institute of Applied Mathematics, Academy of Mathematics and Systems Science, CAS, Beijing 100190, China\\
+Kavli Institute for Astronomy and Astrophysics, Beijing 100871, China\\
+Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36, 10623 Berlin, Germany
+}
 
 \begin{abstract}
+%
+% Motivation: Why do we care about the problem and the results?
+% ==============================================================
+%
+
+%
+% Problem statement: What problem are we trying to solve?
+% ========================================================
+%
+
+%
+% Approach: How did we go about solving or making progress on the problem?
+% =========================================================================
+%
+
+%
+% Results: What's the answer?
+% ===========================
+%
+
+%
+% Conclusions: What are the implications of our answer?
+% ======================================================
+%
 We study the formation and evolution of intermediate mass ratio inspirals (IMRIs) triggered by the interactions between stellar black holes and an intermediate black hole (IMBH) inhabiting.
@@
 
-Intermediate mass black holes, with masses in the range $10^2-10^5\Ms$, might represent the missing link between stellar and supermassive mass black holes.
-Dense stellar systems, such as globular clusters (GCs), are thought to be ideal factories for IMBH production via formation and collapse of a very massive stars through stellar collisions \citep{zwart02, giersz15, mapelli16} or via multiple interactions and mergers between stars and stellar-mass BHs \citep{giersz15}.
-Unfortunately, a striking observational evidence for the presence of IMBHs inhabiting GCs is still missing due to the the little dynamical effects that these objects have on their surroundings.
-Indeed, models suggest that several processes can mimic an IMBH, like anisotropies in the GC kinematical properties \citep{zocchi}, or the presence of a dense cluster of stellar mass BHs that dominate the inner cluster centre \citep{AAG18a,AAG18b,AS16,vandermarel10}.
-Nevertheless, a few observational IMBHs candidates have been found for Galactic GCs \citep{noyola10,lu13,lanzoni13,kiziltan17} and their mass and influence radius might be possibly connected with the host cluster observational properties \citep{AAG18a}.
-Due to this, finding an unique way to unravel the presence of IMBHs in GCs represents one of the most interesting challenges in modern astronomy.
-Beside this, the presence of an IMBH sitting in the centre of a dense cluster represents a scenario particularly appealing from the perspectives of gravitational waves (GW) astronomy.
-Indeed, a compact remnants orbiting the IMBH can enter a regime where GWs emission dominates, leading to the formation of an intermediate mass-ratio inspiral \citep[IMRI,][]{konstantinidis13,haster16,leigh14}, a class of sources possible audible with the next generation of GW observatories like LISA \citep{seoane07,amaro12,seoane18}
+Intermediate mass black holes, with masses in the range $10^2-10^5\Ms$, might
+represent the missing link between stellar and supermassive mass black holes.
+Dense stellar systems, such as globular clusters (GCs), are thought to be ideal
+factories for IMBH production via formation and collapse of a very massive
+stars through stellar collisions \citep{zwart02, giersz15, mapelli16} or via
+multiple interactions and mergers between stars and stellar-mass BHs
+\citep{giersz15}. Unfortunately, a striking observational evidence for the
+presence of IMBHs inhabiting GCs is still missing due to the the little
+dynamical effects that these objects have on their surroundings. Indeed, models
+suggest that several processes can mimic an IMBH, like anisotropies in the GC
+kinematical properties \citep{zocchi}, or the presence of a dense cluster of
+stellar mass BHs that dominate the inner cluster centre
+\citep{AAG18a,AAG18b,AS16,vandermarel10}. Nevertheless, a few observational
+IMBHs candidates have been found for Galactic GCs
+\citep{noyola10,lu13,lanzoni13,kiziltan17} and their mass and influence radius
+might be possibly connected with the host cluster observational properties
+\citep{AAG18a}. Due to this, finding an unique way to unravel the presence of
+IMBHs in GCs represents one of the most interesting challenges in modern
+astronomy. Beside this, the presence of an IMBH sitting in the centre of a
+dense cluster represents a scenario particularly appealing from the
+perspectives of gravitational waves (GW) astronomy. Indeed, a compact remnants
+orbiting the IMBH can enter a regime where GWs emission dominates, leading to
+the formation of an intermediate mass-ratio inspiral
+\citep[IMRI,][]{konstantinidis13,haster16,leigh14}, a class of sources possible
+audible with the next generation of GW observatories like LISA
+\citep{seoane07,amaro12,seoane18}
 
-However, in the highly dense regions that characterize star clusters centres, the formation of IMRIs is not a smooth process.
-Indeed, due to the continuous interactions with stars, an IMRI ``progenitor'', namely a tight IMBH-BH binary, might be subjected to strong perturbation induced, for instance by a passing-by BH.
-The three-body interaction involving the IMBH and the two BHs can lead to a variety of end states, including the formation of an IMRI, a stellar BH binary, the ejection of one BH, or even both, or the development of a head-on collision.
+However, in the highly dense regions that characterize star clusters centres,
+the formation of IMRIs is not a smooth process. Indeed, due to the continuous
+interactions with stars, an IMRI ``progenitor'', namely a tight IMBH-BH binary,
+might be subjected to strong perturbation induced, for instance by a passing-by
+BH. The three-body interaction involving the IMBH and the two BHs can lead to a
+variety of end states, including the formation of an IMRI, a stellar BH binary,
+the ejection of one BH, or even both, or the development of a head-on
+collision.
 
-Quantifying the branching ratio for IMRIs formation constitute a fundamental step to assess the probability to observe these GW sources with the next generation of space-based detectors like LISA\footnote{\url{https://www.elisascience.org/}} \citep{seoane07}, TianQin \citep{tianqin16} or Taiji \citep{taiji17}.
+Quantifying the branching ratio for IMRIs formation constitute a fundamental
+step to assess the probability to observe these GW sources with the next
+generation of space-based detectors like
+LISA\footnote{\url{https://www.elisascience.org/}} \citep{seoane07}, TianQin
+\citep{tianqin16} or Taiji \citep{taiji17}.
 
-In this paper, we model the potential formation of an IMRI from the interactions between an IMBH and two stellar mass BHs.
-To reach the aim, we use $N$-body simulations that take into account in particles' equations of motion both the star cluster gravitational potential and post-Newtonian corrections up to 2.5 order.
-Varying the IMBH and BHs masses, their orbital configuration, and the host cluster structural properties, we build-up three sets consisting of 2000 models each, which allow us to uncover three possible scenarios for IMRIs formation.
+In this paper, we model the potential formation of an IMRI from the
+interactions between an IMBH and two stellar mass BHs. To reach the aim, we use
+$N$-body simulations that take into account in particles' equations of motion
+both the star cluster gravitational potential and post-Newtonian corrections up
+to 2.5 order. Varying the IMBH and BHs masses, their orbital configuration, and
+the host cluster structural properties, we build-up three sets consisting of
+2000 models each, which allow us to uncover three possible scenarios for IMRIs
+formation.
 
-The paper is organized as follows: in Section \ref{num} we present and summarize the numerical setup used to model the IMBH - BH interaction, in Section \ref{met} we discuss the main properties of the simulations outputs, and the implications for GW astronomy, while Section \ref{res} is devoted to the results summary and conclusions.
+The paper is organized as follows: in Section \ref{num} we present and
+summarize the numerical setup used to model the IMBH - BH interaction, in
+Section \ref{met} we discuss the main properties of the simulations outputs,
+and the implications for GW astronomy, while Section \ref{res} is devoted to
+the results summary and conclusions.
 
-\section{Initial conditions}
-\label{met}
+\section{Initial conditions} \label{met}
 
-In this work, we study IMRIs formation via triple interactions involving an IMBH and two stellar mass BHs that inhabit in the centre of a massive star cluster. 
-One of the two BHs is bound to the IMBH, while the second BH orbits around the IMBH-BH binary centre of mass.
-The triple orbital configuration can be dissected into an inner and an outer binary, as sketched in Figure \ref{fig:f1}.
-This simple picture is complicated by the fact that the triple cannot be considered as an isolated system, as other cluster members can affect its evolution.
+In this work, we study IMRIs formation via triple interactions involving an
+IMBH and two stellar mass BHs that inhabit in the centre of a massive star
+cluster.  One of the two BHs is bound to the IMBH, while the second BH orbits
+around the IMBH-BH binary centre of mass. The triple orbital configuration can
+be dissected into an inner and an outer binary, as sketched in Figure
+\ref{fig:f1}. This simple picture is complicated by the fact that the triple
+cannot be considered as an isolated system, as other cluster members can affect
+its evolution.
 
@@
 
-Sonderforschungsbereich SFB 881 "The Milky Way System" (subproject Z2) of the German Research Foundation (DFG) for the financial support provided.
-This work benefited of financial support from the Alexander von Humboldt Foundation, which granted MAS research program ``The evolution of black holes from stellar to galactic scales''.
-This work benefited from support by the ISSI (Bern), through its Intern. Team prog. ref. no. 393 {\it The Evolution of Rich Stellar Populations \& BH Binaries} (2017-18).
+Sonderforschungsbereich SFB 881 "The Milky Way System" (subproject Z2) of the
+German Research Foundation (DFG) for the financial support provided. This work
+benefited of financial support from the Alexander von Humboldt Foundation,
+which granted MAS research program ``The evolution of black holes from stellar
+to galactic scales''.  This work benefited from support by the ISSI (Bern),
+through its Intern. Team prog. ref. no. 393 {\it The Evolution of Rich Stellar
+Populations \& BH Binaries} (2017-18).  PAS acknowledges support from the
+Ram{\'o}n y Cajal Programme of the Ministry of Economy, Industry and
+Competitiveness of Spain, as well as the COST Action GWverse CA16104. This work
+was supported by the National Key R\&D Program of China (2016YFA0400702) and
+the National Science Foundation of China (11721303).
 
@@
 \bibliographystyle{mn2e}
-\bibliography{ASetal2015}
+\bibliography{aamnem99,biblio,ASetal2015}
 }

### 2019-04-19 mn.tex
Converted to MNRAS style, the file is now mn tex

--- 2019-04-19 article.tex
@@
-\documentclass[twocolumn]{aastex62}
-\usepackage[latin1]{inputenc}
-\usepackage[english]{babel}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{makeidx}
-\usepackage{graphicx}
-%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
+\documentclass[useAMS,usenatbib]{mn2e}
+\usepackage{epsfig,graphicx,latexsym,amsmath,amssymb}
+\usepackage[export]{adjustbox}[2011/08/13]
+% Centers the content in the given length
+% Use as:
+% \includegraphics[width=1.2\textwidth,center]{image}
+
+\usepackage{natbib}
+\usepackage{hyperref}
+\usepackage{mathrsfs}
+\usepackage{lastpage}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\usepackage{draftwatermark}          %
+%\SetWatermarkText{Do not circulate}  %
+%\SetWatermarkLightness{0.8}          %
+%\SetWatermarkScale{0.7}              %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \usepackage{color}
-\usepackage{appendix}
-\usepackage{multirow}
-\usepackage[flushleft]{threeparttable}
 
@@
 
-\graphicspath{{./}{./}}
+\newcommand{\pau}[1]{\textcolor{cyan}{{\bf Comment from Pau:} ``#1.''}}
 
-\received{}
-\revised{revised to \today}
-\accepted{}
+\bibpunct[,]{(}{)}{;}{a}{}{,}
 
-\submitjournal{ApJ (not yet ..)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\shorttitle{Formation of IMRIs}
-\shortauthors{Arca Sedda, M. and Amaro-Seoane, P.}
+\title[Formation of intermediate-mass ratio inspirals]
+      {The relativistic capture of compact objects by intermediate-mass black holes}
+
+\author[M. Arca Sedda \& P. Amaro-Seoane] % Running authors, % use abbrev. names here
+{
+Manuel Arca Sedda$^{1}$
+                        \thanks{E-mail: m.arcasedda@gmail.com (MAS)} \&
+Pau Amaro-Seoane$^{2}$
+                        \thanks{E-mail: pau@ice.cat (PAS)},
+                                % Thanks goes to 1rst author only
+                                % Continue with other authors, full names
+   \\
+                                % Now addresses come
+                                % Separate with \\ but for
+                                % the last one
+$^{1}$Zentrum f\"{u}r Astronomie, Astronomisches Rechen-Institut, M\"onchhofstrasse 12-14, Heidelberg, D-69120, Germany\\
+$^{2}$Institut de Ci{\`e}ncies de l'Espai (CSIC-IEEC) at Campus UAB,
+Carrer de Can Magrans s/n 08193 Barcelona, Spain\\
+Institute of Applied Mathematics, Academy of Mathematics and Systems Science,
+CAS, Beijing 100190, China\\
+Kavli Institute for Astronomy and Astrophysics, Beijing 100871, China\\
+Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36,
+10623 Berlin, Germany
+}
 
@@
 
-\title{Formation and evolution of intermediate-mass ratio inspirals}
+\date{draft \today}
 
-\correspondingauthor{Manuel Arca Sedda}
-\email{m.arcasedda@gmail.com}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{}
 
-\author{Manuel Arca Sedda and Pau Amaro-Seoane}
-\affil{Zentrum f\"{u}r Astronomie der Universit\"{a}t  Heidelberg\\
-Astronomisches Rechen-Institut\\
-M\"onchhofstrasse 12-14\\
-Heidelberg, D-69120, DE}
-\affil{
-Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC)\\
-at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain\\
-Institute of Applied Mathematics, Academy of Mathematics and Systems Science, CAS, Beijing 100190, China\\
-Kavli Institute for Astronomy and Astrophysics, Beijing 100871, China\\
-Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36, 10623 Berlin, Germany
-}
+\maketitle
+
+\label{firstpage}
 
@@
 %
-We study the formation and evolution of intermediate mass ratio inspirals (IMRIs) triggered by the interactions between stellar black holes and an intermediate black hole (IMBH) inhabiting.
-We show the probability for an IMRI to form is an increasing function of the IMBH mass, representing a viable channel for the development of gravitational wave sources that can be possibly observed with the future generation of detectors.
 \end{abstract}
 
-\keywords{black holes - supermassive black holes - galactic nuclei - gravitational waves}
+\begin{keywords}
+% Llista sencera: http://oxfordjournals.org/our_journals/mnrasl/for_authors/mnraskey.pdf
+a keyword -- another.
+\end{keywords}
 
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 
-Sonderforschungsbereich SFB 881 "The Milky Way System" (subproject Z2) of the
-German Research Foundation (DFG) for the financial support provided. This work
-benefited of financial support from the Alexander von Humboldt Foundation,
-which granted MAS research program ``The evolution of black holes from stellar
-to galactic scales''.  This work benefited from support by the ISSI (Bern),
-through its Intern. Team prog. ref. no. 393 {\it The Evolution of Rich Stellar
-Populations \& BH Binaries} (2017-18).  PAS acknowledges support from the
-Ram{\'o}n y Cajal Programme of the Ministry of Economy, Industry and
-Competitiveness of Spain, as well as the COST Action GWverse CA16104. This work
-was supported by the National Key R\&D Program of China (2016YFA0400702) and
-the National Science Foundation of China (11721303).
+MAS thanks the Sonderforschungsbereich SFB 881 ``The Milky Way System''
+(subproject Z2) of the German Research Foundation (DFG) for the financial
+support provided. This work benefited of financial support from the Alexander
+von Humboldt Foundation, which granted MAS' research program ``The evolution of
+black holes from stellar to galactic scales''.  This work benefited from
+support by the ISSI (Bern), through its Intern. Team prog. ref. no. 393 {\it
+The Evolution of Rich Stellar Populations \& BH Binaries} (2017-18).  PAS
+acknowledges support from the Ram{\'o}n y Cajal Programme of the Ministry of
+Economy, Industry and Competitiveness of Spain, as well as the COST Action
+GWverse CA16104. This work was supported by the National Key R\&D Program of
+China (2016YFA0400702) and the National Science Foundation of China (11721303).
+PAS is indebted with the Edoardo Amaldi Center at La Sapienza University in
+Rome for two visits in 2019.
 
-\footnotesize{
-\bibliographystyle{mn2e}
-\bibliography{aamnem99,biblio,ASetal2015}
-}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{mn}            %
+\bibliography{aamnem99,biblio,ASetal2015}    %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{LastPage}
 \end{document}

### 2019-04-19 mn.tex
added paragraph about rates for LISA, ET, LIGO/Virgo etc

@@
 %
-
+The gravitational capture of a stellar-mass compact object by a 
+massive black hole constitutes a unique a probe of spacetime in the
+strong regime of gravity.
 %
@@
 %
-
+Intermediate-mass black holes (IMBHs) with masses between $10^2$ and
+$10^4\,M_{\odot}$ are probably lurking in globular clusters, but we still lack
+observational evidence.  The detection of the gravitational waves of an
+intermediate-mass ratio inspiral (IMRI) are twofold. First, a proof that black
+holes exist in that mass range, necessary to understand how supermassive black
+holes gained their masses.  Second, we can map spacetime and extract the
+redshifted parameters with high precision.
 %
@@
 %
-
+Because IMBHs are not fixed at the centre of the cluster, to address the
+formation and evolution of IMRIs analytically is very challenging, and the
+problem requires numerical simulations. We present a detailed study of the
+parameter space of IMRIs in globular clusters using a high-accurate,
+direct-summation integrator.
 %
@@
 %
-
+XXX
 %
@@
 %
+YYY
+Moreover, we estimate that a Milky Way-like galaxy should have an IMRI event rate of approximately
+$5\times 10^{-4}\,\textrm{yr}^{-1}$.
 \end{abstract}
@@
 
+\pau{Dovremmo calcolare il tasso per LISA, ET, LIGO/Virgo... e' semplice... solo bisogna calcolare quante galassie ci sono
+nel loro volume di osservazione e prendere una relazione come quella di Mc Laughlin. Prendiamo la distanzia all'orizzonte,
+calcoliamo quante galassie ci sono e moltiplichiamo da 0.25:
+\cite{McLaughlin99} derives a formation efficiency of cluster formation of
+$\epsilon \equiv M_{GCs}/M_{\rm gas}$, with $M_{GCs}$ the initial
+population of globulars and $M_{\rm gas}$ the available gas in the
+protogalaxy. By evaluating a sample including giant ellipticals, faint dwarfs
+and brightest cluster galaxies, the author obtains $\epsilon \simeq 0.25\%$,
+and we note that the results are almost identical for the Population II
+spheroid of the Milky Way.}
+
 \subsection{Serendipitous formation of stellar BH binaries around an IMBH}

### 2019-06-03 mn.tex
abstract and introduction revised

@@
 
-Intermediate mass black holes, with masses in the range $10^2-10^5\Ms$, might
-represent the missing link between stellar and supermassive mass black holes.
-Dense stellar systems, such as globular clusters (GCs), are thought to be ideal
-factories for IMBH production via formation and collapse of a very massive
-stars through stellar collisions \citep{zwart02, giersz15, mapelli16} or via
+Intermediate-mass black holes, with masses in the range $10^2-10^5\Ms$
+represent the missing link between stellar-mass and supermassive black holes.
+Dense stellar systems, such as globular clusters (GCs), could be the place
+where IMBH form via the creation of a very massive stars through a runaway
+process which would eventually collapse
+\citep{PortegiesZwartMcMillan00,GurkanEtAl04,PortegiesZwartEtAl04,
+FreitagEtAl06, giersz15, mapelli16}.  This process however depends on a number
+of assumptions, such as the metallicity, stellar winds, and the actualy outcome
+of the stellar collisions
+\citep[see][]{BelkusEtAl07,SuzukiEtAl07,GlebbeekEtAl09}.
+Another possibility is through
 multiple interactions and mergers between stars and stellar-mass BHs
 \citep{giersz15}. Unfortunately, a striking observational evidence for the
-presence of IMBHs inhabiting GCs is still missing due to the the little
+presence of IMBHs inhabiting GCs is still missing due to the little
 dynamical effects that these objects have on their surroundings. Indeed, models
-suggest that several processes can mimic an IMBH, like anisotropies in the GC
-kinematical properties \citep{zocchi}, or the presence of a dense cluster of
-stellar mass BHs that dominate the inner cluster centre
+suggest that several processes can mimic the presence of an IMBH, like anisotropies in the
+kinematical properties of the GC \citep{zocchi}, or the presence of a dense cluster of
+stellar-mass black holes that dominate the inner cluster centre
 \citep{AAG18a,AAG18b,AS16,vandermarel10}. Nevertheless, a few observational
@@
 might be possibly connected with the host cluster observational properties
-\citep{AAG18a}. Due to this, finding an unique way to unravel the presence of
-IMBHs in GCs represents one of the most interesting challenges in modern
-astronomy. Beside this, the presence of an IMBH sitting in the centre of a
-dense cluster represents a scenario particularly appealing from the
-perspectives of gravitational waves (GW) astronomy. Indeed, a compact remnants
-orbiting the IMBH can enter a regime where GWs emission dominates, leading to
-the formation of an intermediate mass-ratio inspiral
-\citep[IMRI,][]{konstantinidis13,haster16,leigh14}, a class of sources possible
-audible with the next generation of GW observatories like LISA
-\citep{seoane07,amaro12,seoane18}
+\citep{AAG18a}.
 
-However, in the highly dense regions that characterize star clusters centres,
-the formation of IMRIs is not a smooth process. Indeed, due to the continuous
-interactions with stars, an IMRI ``progenitor'', namely a tight IMBH-BH binary,
-might be subjected to strong perturbation induced, for instance by a passing-by
-BH. The three-body interaction involving the IMBH and the two BHs can lead to a
-variety of end states, including the formation of an IMRI, a stellar BH binary,
-the ejection of one BH, or even both, or the development of a head-on
-collision.
+It has been shown in the literature that a compact object, such as a
+stellar-mass black hole, could be gravitationally captured by the IMBH, to
+eventually merge with it. The first numerical simulation of this scenario was
+presented by \cite{konstantinidis13}, who used dedicated direct-summation
+$N-$body simulations with all relativistic phenomena included at least at the
+lowest order (periapsis shift, energy loss due to gravitational radiation, and
+the relativistic recoil). They observed an intermediate-mass ratio inspiral
+\citep{Amaro-SeoaneLRR2012,Amaro-SeoaneEtAl07} forming and follow it down to
+the merger, which leads to the ejection of the IMBH. Other studies have
+followed their findings, in particular the work of
+\cite{leigh14,MacLeodEtAl2016}; also, because the initial setup of
+\cite{haster16} is almost identical to that of \cite{konstantinidis13} but they
+use a different integrator, it can be envisaged as a confirmation of their
+results. This source of gravitational waves (GWs) can be observed with a the
+Laser Interferometer Space Antenna (LISA, see the LISA Consortium study
+\citealt{Amaro-SeoaneEtAl2017} and also
+\citealt{Amaro-SeoaneEtAl2013,Amaro-SeoaneEtAl2012}), or other space-borne
+observatories alternatives, currently under study, Taiji \citep{taiji17} or
+Tianqin \citep{tianqin16}. Moreover, IMRIs could be jointly detected with LISA and
+ground-based detectors such as LIGO/Virgo, and LISA could warn them years in
+advance and with seconds of precision \citep{Amaro-Seoane2018}.
 
-Quantifying the branching ratio for IMRIs formation constitute a fundamental
-step to assess the probability to observe these GW sources with the next
-generation of space-based detectors like
-LISA\footnote{\url{https://www.elisascience.org/}} \citep{seoane07}, TianQin
-\citep{tianqin16} or Taiji \citep{taiji17}.
+Due to the fact that the IMBH is lighter than a supermassive black hole in a
+galactic nucleus, we cannot assume anymore that it is fixed at the centre of
+the system. This makes an analytical study of the problem arduous and
+challenging.  In this article we model the potential formation of an IMRI in a
+dense stellar system, a cluster, via the interactions between an IMBH and
+stellar-mass black holes. The outcome of such process is varied and could lead
+to different end states, including the formation of an IMRI, a stellar-mass
+black hole binary, the ejection of one or both stellar-mass black holes, or
+even a head-on collision between the compact objects.  To this end, we use a
+direct-summation $N-$body code that includes post-Newtonian to account for the
+periapsis shift and the loss of energy via gravitational radiation \citep[as
+presented for the first time in][]{KupiEtAl06}, as well as the cluster
+gravitational potential \textbf{(REF: Manuel, your first fork of ARCHAIN cited
+here)}. We scan the parameter space, in particular the IMBH and stellar-mass
+black hole masses, their orbital configuration, and the host cluster structural
+properties with a set of 2,000 models.
 
-In this paper, we model the potential formation of an IMRI from the
-interactions between an IMBH and two stellar mass BHs. To reach the aim, we use
-$N$-body simulations that take into account in particles' equations of motion
-both the star cluster gravitational potential and post-Newtonian corrections up
-to 2.5 order. Varying the IMBH and BHs masses, their orbital configuration, and
-the host cluster structural properties, we build-up three sets consisting of
-2000 models each, which allow us to uncover three possible scenarios for IMRIs
-formation.
-
-The paper is organized as follows: in Section \ref{num} we present and
-summarize the numerical setup used to model the IMBH - BH interaction, in
-Section \ref{met} we discuss the main properties of the simulations outputs,
-and the implications for GW astronomy, while Section \ref{res} is devoted to
-the results summary and conclusions.
+In Section \ref{num} we present and summarise the numerical setup used to model
+the interactions; in Section \ref{met} we discuss the main properties of the
+simulations outputs, and the implications for GW astronomy; while Section
+\ref{res} is devoted to the results and conclusions.
 

### 2019-06-03 mn.tex
work on 1st section

@@
 black hole masses, their orbital configuration, and the host cluster structural
-properties with a set of 2,000 models.
+properties with a set of 2,000 models. \textbf{(Manuel, is the number right or did
+you run more?)}
 
@@
 
-In this work, we study IMRIs formation via triple interactions involving an
-IMBH and two stellar mass BHs that inhabit in the centre of a massive star
-cluster.  One of the two BHs is bound to the IMBH, while the second BH orbits
-around the IMBH-BH binary centre of mass. The triple orbital configuration can
-be dissected into an inner and an outer binary, as sketched in Figure
-\ref{fig:f1}. This simple picture is complicated by the fact that the triple
-cannot be considered as an isolated system, as other cluster members can affect
-its evolution.
+Based on the numerical studies of
+\cite{konstantinidis13,leigh14,MacLeodEtAl2016,haster16}, we consider a
+stellar-mass black hole which has formed a binary with the IMBH and a second
+stellar-mass black hole, orbiting around the binary centre-of-mass. We depict
+this configuration in Figure~(\ref{fig:f1}) as an inner and outer binary, and
+note that this triple configuration is not isolated, but embedded in a cluster.
 
@@
     \includegraphics[width=7cm]{triple}
-    \caption{Sketch of the IMBH-BH-BH triple configuration.}
+    \caption{The inner binary is formed by the stellar-mass black hole of mass  $M_\ibh$ and $M_\bhu$, 
+the binary semi-major axis $a_\inn$ and its eccentricity $e_\inn$. The outer binary depends on the mass of the
+second stellar-mass black hole, $M_\bhd$, it has a semi-major axis  $a_\out$ and an eccentricity $e_\out$.
+These three compact objects are embedded in a host cluster which is modelled following a Dehnen profile \citep{Deh93},
+characterised by a total mass $M_c$, a scale radius, $r_c$, and the inner slope of the density profile $\gamma$. The angular
+momentum of the inner binary $L_{\rm in}$ and the outer one $L_{\rm out}$ subtend and angle $i$.}
     \label{fig:f1}
@@
 
-Therefore, the phase space that characterises the triple's main properties can be dissected into three groups:
-\begin{itemize}
-    \item {\bf Inner binary (IMBH+BH)}: depends on the IMBH and BH masses, $M_\ibh$ and $M_\bhu$, the binary semi-major axis $a_\inn$ and its eccentricity $e_\inn$.
-    \item {\bf Outer binary (IMBH+BH+BH)}: depends on the third BH mass, $M_\bhd$, semi-major axis $a_\out$, eccentricity $e_\out$.
-    \item {\bf Host cluster}: we model the host cluster as a \cite{Deh93} sphere, characterized by total mass, $M_c$, scale radius, $r_c$, and the inner slope of the density profile $\gamma$.
-\end{itemize}
+We choose the IMBH mass to range among eight different values ${\rm
+Log}(M_\ibh/\Ms) = 2-2.5,\,3-3.5,\,4-4.5,\,5-5.5$, so as to cover typical values of
+IMBH forming in stellar systems of various sizes, from young and open clusters,
+to globular clusters, and up to low-mass nuclear clusters and dwarf galaxies.
+Stellar-mass black hole (BH) masses are selected between $M_{\rm min} = 10\,\Ms$ and
+$M_{\rm max} = 30\,\Ms$, a mass range typical of stellar environments with a
+metallicity $Z<0.25\,\Zs$ \citep{belczynski16,spera16}.
 
-In order to unveil the link between IMRIs formation and IMBH properties, we select the IMBH mass among eight different values ${\rm Log}(M_\ibh/\Ms) = 2-2.5-3-3.5-4-4.5-5-5.5$.
-This range covers typical values of putative IMBH masses forming in stellar systems of various sizes, from young and open clusters, to globular clusters, and up to low-mass nuclear clusters and dwarf galaxies.
+From Figure 5 of \cite{belczynski16}, the BH mass can be connected to the
+initial stellar mass via a simple power-law \textbf{(Manuel, didn't you derive
+a similar result? why not credit yourself?)}
 
-Stellar BH masses are selected between $M_{\rm min} = 10\Ms$ and $M_{\rm max} = 30\Ms$, a mass range typical of stellar environments with a metallicity $Z<0.25\Zs$ \citep{belczynski16,spera16}. 
-From Figure 5 of \cite{belczynski16}, we find that the BH mass can be connected to the initial star mass via a simple power-law 
 \begin{equation}
@@
 \end{equation}
+
+\noindent
 with the coefficient depending on the metallicity as summarized in Table \ref{tab:t1}.

### 2020-01-16 article.tex

@@
 
+\newcommand{\derd}{{\rm d}}
 \newcommand{\Log}{{\rm Log}}
@@
 \newcommand{\imbh}{{\rm IMBH}}
+\newcommand{\imri}{{\rm IMRI}}
 \newcommand{\inn}{{\rm in}}
@@
 %
-We study the formation and evolution of intermediate mass ratio inspirals (IMRIs) triggered by the interactions between stellar black holes and an intermediate black hole (IMBH) inhabiting.
-We show the probability for an IMRI to form is an increasing function of the IMBH mass, representing a viable channel for the development of gravitational wave sources that can be possibly observed with the future generation of detectors.
+We study the formation and evolution of intermediate mass ratio inspirals (IMRIs) triggered by the interactions between two stellar black holes (BHs) and an intermediate black hole (IMBH) inhabiting a globular cluster.
+We show that the probability for IMRIs formation is an increasing function of the IMBH mass that is well described by a power-law for IMBH masses above $M_\ibh = 10^3\Ms$.
+We find that IMRIs have a formation probability $\sim 15\%$, regardless of the assumptions made.
+Our results suggest that in low-density clusters these interactions lead to the formation of stable triples, a fraction of which arrange in a hierarchical configurations and undergo Kozai-Lidov oscillations.
+In dense clusters, instead, the most frequent configuration is unstable, with the IMBH and the closest BH being strongly affected by the chaotic perturbations exerted by the third BH.
+We calculate IMRIs horizon redshift for several ground- and space-based gravitational waves (GWs) observatories.
+Combining this information with our results and observational limits on the cosmological distribution of galaxies and star clusters, we infer the IMRI merger rate for different detectors.
+Assuming a 4 yr observation timespan, we infer a merger rate of 1-4 events yr$^{-1}$ for LIGO in the IMRIs mass range $100-250\Ms$ up to redshift $z=0.1-0.6$, 1-30 yr$^{-1}$ for LISA ($M_{\rm imri} > 10^3\Ms$) up to redshift $z=1.5$.
+The next generation of detectors will allow us to observe IMRI out to the peak of GC formation and even beyond, with an expected rate of $200-2000$ yr$^{-1}$ for ET ($M_{\rm imri} < 10^3\Ms$) and $250-4400$ yr$^{-1}$ for DECIGO ($M_{\rm imri} < 60 - 5\times 10^4 \Ms$).
+We show that a considerable number of sources can be observed are multiband thus can be observed with both low- and high-frequency detectors, especially in the case of future detectors.
+Although highly eccentric at formation, we find that only $\sim 1\%$ of IMRI will preserve a high eccentricity when entering the mHz frequency band.
 \end{abstract}
@@
     \item {\bf Outer binary (IMBH+BH+BH)}: depends on the third BH mass, $M_\bhd$, semi-major axis $a_\out$, eccentricity $e_\out$.
-    \item {\bf Host cluster}: we model the host cluster as a \cite{Deh93} sphere, characterized by total mass, $M_c$, scale radius, $r_c$, and the inner slope of the density profile $\gamma$.
+    \item {\bf Host cluster}: we model the host cluster as a \cite{Deh93} sphere, characterized by total mass, $M_\gc$, scale radius, $r_\gc$, and the inner slope of the density profile $\gamma$.
 \end{itemize}
@@
 The host cluster is assumed to be described by a \cite{Deh93} sphere, characterized by 
-total mass $M_c$, scale radius $r_c$ and slope of the density profile $\gamma$.
-The cluster length scale $r_c$ is selected randomly between 0.2 and 1.0 pc. For the cluster density slope, we assume a flat distribution with upper limit $\gamma \leq 1$.
-To assign clusters' mass we either assume a scaling relation between the IMBH and the cluster mass, $M_\ibh - M_c$, or between the IMBH mass and the cluster velocity dispersion, $M_\ibh-\sigma_c$.
+total mass $M_\gc$, scale radius $r_\gc$ and slope of the density profile $\gamma$.
+The cluster length scale $r_\gc$ is selected randomly between 0.2 and 1.0 pc. For the cluster density slope, we assume a flat distribution with upper limit $\gamma \leq 1$.
+To assign clusters' mass we either assume a scaling relation between the IMBH and the cluster mass, $M_\ibh - M_\gc$, or between the IMBH mass and the cluster velocity dispersion, $M_\ibh-\sigma_\gc$.
 
 In the first case, we take advantage of the scaling relations based on numerical models of IMBH formation and observations of putative IMBHs in globular clusters \citep{zwart02,Lutzgendorf13,AS16}.
-In particular, we adopt the scaling provided by \cite{AS16}, connecting the host cluster mass $M_c$ with the total ''dark'' mass, inhabiting the cluster's centre, comprised of either an IMBH or a sizable population of stellar BHs
+In particular, we adopt the scaling provided by \cite{AS16}, connecting the host cluster mass $M_\gc$ with the total ''dark'' mass, inhabiting the cluster's centre, comprised of either an IMBH or a sizable population of stellar BHs
 \begin{equation}
-\Log \left(\frac{M_c}{\Ms}\right) = \alpha \Log \left(\frac{M_\ibh}{\Ms}\right) + \beta.
+\Log \left(\frac{M_\gc}{\Ms}\right) = \alpha \Log \left(\frac{M_\ibh}{\Ms}\right) + \beta.
 \label{mcmibh}
@@
  \begin{equation}
- R_{\rm inf} = \frac{GM_\ibh}{\sigma_c^2} = \frac{M_\ibh}{M_c}R_{\rm hm},
+ R_{\rm inf} = \frac{GM_\ibh}{\sigma_\gc^2} = \frac{M_\ibh}{M_\gc}R_{\rm hm},
  \end{equation}
- where we substituted the cluster velocity dispersion $\sigma_c$ with its value calculated at the cluster half-mass radius $R_{\rm hm}$, which in turn can be expressed in terms of the length scale and slope as
+ where we substituted the cluster velocity dispersion $\sigma_\gc$ with its value calculated at the cluster half-mass radius $R_{\rm hm}$, which in turn can be expressed in terms of the length scale and slope as
 \begin{equation}
-R_{\rm hm} = r_c(2^{1/(3-\gamma)}-1)^{-1}.
+R_{\rm hm} = r_\gc(2^{1/(3-\gamma)}-1)^{-1}.
 \end{equation} 
@@
 \begin{equation}
-R_{\rm inf} = \mu r_c(2^{1/(3-\gamma)}-1)^{-1},
+R_{\rm inf} = \mu r_\gc(2^{1/(3-\gamma)}-1)^{-1},
 \end{equation}
-where $\mu = M_\ibh/M_c = 0.0058$ via Equation \ref{mcmibh}, thus implying that the the IMBH sphere of influence depends only on the cluster scale length and density slope.
+where $\mu = M_\ibh/M_\gc = 0.0058$ via Equation \ref{mcmibh}, thus implying that the the IMBH sphere of influence depends only on the cluster scale length and density slope.
 
-In the second case, instead, we assume that GCs central regions represent a downsized version of galactic nuclei, thus the IMBH mass can be connected to the velocity dispersion inverting the so-called $M_\ibh - \sigma_c$ relation as
+In the second case, instead, we assume that GCs central regions represent a downsized version of galactic nuclei, thus the IMBH mass can be connected to the velocity dispersion inverting the so-called $M_\ibh - \sigma_\gc$ relation as
 \begin{equation}
-     \Log \left(\frac{\sigma_c}{200{\rm km~s}^{-1}}\right) = \frac{1}{\alpha}\left(\left(\frac{\Log M_\ibh}{\Ms}\right) - \beta\right) ,
+     \Log \left(\frac{\sigma_\gc}{200{\rm km~s}^{-1}}\right) = \frac{1}{\alpha}\left(\left(\frac{\Log M_\ibh}{\Ms}\right) - \beta\right) ,
 \end{equation}
@@
 Additionally, we associate to the cluster randomly a concentration parameter $c$ between $10.7$ and $131.4$, a range of values typical of dense star clusters characterized by an adimensional potential well $W_0 = 6-9$ \citep{king62}.
-The cluster mass is then calculated as $M_c = 2\sigma_c^2 c R_c / G$.
+The cluster mass is then calculated as $M_\gc = 2\sigma_\gc^2 c r_\gc / G$.
 
@@
 \caption{Main properties of our models}
-\begin{tabular}{cccccccccccc}
+\begin{tabular}{cccccccccc}
 \hline
-model   & $f(\Log M_\ibh)$ & $M_\ibh$ & $\delta_\bh$ & $M_\bh$ & $a_\inn$ & $P(e_\inn)$ & $a_\out$ & $P(e_\out)$ &$P(\cos(i))$ &Cluster scaling & $N_{\rm sim}$\\ 
-        &             & $\Ms$    &            & $\Ms$   & $\au$    &          & $\au$    &         &  &relation &\\
+model   & $M_\ibh$ & $\delta_\bh$ & $M_\bh$ & $a_\inn$ & $a_\out$ & $P(e)$ &$P(\cos(i))$ &Cluster scaling & $N_{\rm sim}$\\ 
+        & $\Ms$    &            & $\Ms$   & $\au$    &  $\au$    &         &  &relation &\\
 \hline 
-0 & const & $10^2-5\times 10^5$ & $-2.2$ & $10-30$ & $10-315$ & $e^2$ & $20-630$ & $e^2$ & const&$M_\ibh -M_c$ & 2000\\
-1 & const & $10^2-5\times 10^5$ & $-2.2$ & $10-30$ & $10-315$ & $e^2$ & $20-630$ & $e^2$ & const&$M_\ibh -\sigma_c$ & 2000\\
-2 & const & $10^2-5\times 10^5$ & $-2.2$ & $10-30$ & $10-315$ & $e^2$ & $630-1580$ & $e^2$ &const &$M_\ibh -M_c$ & 2000\\
+0 & $10^2-5\times 10^5$ & $-2.2$ & $10-30$ & $10-315$ & $20-630$ & $2e$ & const&$M_\ibh -M_\gc$ & 2000\\
+1 & $10^2-5\times 10^5$ & $-2.2$ & $10-30$ & $10-315$ & $20-630$ & $2e$ & const&$M_\ibh -\sigma_\gc$ & 2000\\
+2 & $10^2-5\times 10^5$ & $-2.2$ & $10-30$ & $10-315$ & $630-1580$ & $2e$ &const &$M_\ibh -M_\gc$ & 2000\\
 \hline
 \end{tabular}
+\begin{tablenotes}
+\item Col.
+1: model ID.
+Col.
+2: mass of the IMBH, we adopt a sampling flat in logarithmic values.
+Col.
+3: slope of the BH mass function adopted.
+Col.
+4: range of masses adopted for stellar BHs.
+Col.
+5-6: range of initial values for the inner/outer semimajor axis, we adopt a sampling flat in  logarithmic values.
+Col.
+7-8: adopted distribution for initial eccentricity/inclination.
+Col.
+9: adopted scaling to connect the IMBH and the cluster masses.
+Col.
+10: Number of simulations performed.
+\end{tablenotes}
 \end{center}
@@
 \subsection{IMRIs formation channels and subsequent evolution}
-
+\label{sec:imris}
 The evolution of the IMBH-BH-BH triple immersed in the host cluster gravitational field can lead to very different outcomes, as shown in Figure \ref{fig:f3}:
 \begin{itemize}
-    \item {\bf Disrupted triple} The three-body interaction undergoes a chaotic phases that ultimately lead to the ejection of a stellar BHs, whereas the inner binary either preserves its original components or undergoes a component swap.
+    \item {\bf Disrupted triple.} The three-body interaction undergoes a chaotic phases that ultimately lead to the ejection of a stellar BHs, whereas the inner binary either preserves its original components or undergoes a component swap.
+    \item {\bf Stable triple.} The triple arranges in a configuration that satisfies the stability criterion for three-body systems. 
+	\begin{itemize}
 		\item {\bf Hierarchical triple.}  The triple arranges in a hierarchical configuration, with the outer BHs perturbing secularly the evolution of the inner binary.
 In this case, the inner binary can develop Kozai-Lidov oscillations \citep{kozai62,lidov62} that can trigger its eccentricity to grow to values close to unity.
+	\end{itemize}
     \item {\bf Unstable triple.} The inner and outer binary are in an unstable configuration, whose evolution is mostly dominated by chaos.
@@
 
-In the second case, the triple arranges in a hierarchical configuration, whose evolution is dominated by secular perturbations.
-This mechanism, known as Kozai-Lidov \citep{kozai62,lidov62}, can induce periodic oscillations in the mutual inclination and the inner binary eccentricity.
+In the second case, the triple is dynamically stable and the effects of perturbations arising from one of the component emerges secularly.
+According to the \cite{mardling01} criterion, a triple is stable if
+\begin{equation}
+    \frac{a_\out}{a_\inn} > \frac{2.8}{1-e_\out}\left(1-\frac{0.3i}{\pi}\right)\left[\frac{(1+q_\out)(1+e_\out}{\sqrt{1-e_\out}}\right]^{2/5}, 
+\label{stabcri}
+\end{equation}
+being $q_\out = m_\out/(m_\imbh + m_\bh)$.
+
+If the triple arranges in a hierarchical configuration, its evolution can be dominated by secular perturbations known as Kozai-Lidov \citep{kozai62,lidov62}, which can induce periodic oscillations in the mutual inclination and the inner binary eccentricity.
 A parameter widely used to discern hierarchical triples is defined as \citep{Lithwick11,naoz11}
@@
 In the case of an unstable triple, the inner and outer binaries have similar orbital properties and dynamics is mostly dominated by chaotic interactions.
-According to the \cite{mardling01} criterion, a triple is unstable if
-\begin{equation}
-    \frac{a_\out}{a_\inn} < \frac{2.8}{1-e_\out}\left(1-\frac{0.3i}{\pi}\right)\left[\frac{(1+q_\out)(1+e_\out}{\sqrt{1-e_\out}}\right]^{2/5}, 
-\end{equation}
-being $q_\out = m_\out/(m_\imbh + m_\bh)$.
 
 In our models, we calculate $\epsilon_\kl$ and $a_\out/a_\inn$ at the end of the simulations, in order to identify to which category a triple belongs. 
-The merger time for the inner binary is calculated through Equation \ref{peters} for models categorized as ``Disrupted'' or ``Unstable'', whereas we use Equation \ref{kozai} for those identified as ``Hierarchical''.
+In the case of models categorized as ``Disrupted'', the merger time is calculated simply via 
+Equation \ref{peters}.
+For ``Hierarchical'' models, instead, we adopt Equation \ref{kozai}.
+Finally, for both ``Stable'' and ``Unstable'' models, the merger time is inferred as the average of the initial and final merger time and the same quantity evaluated in correspondence of the maximum eccentricity.
+Note that for ``Stable'' triples the merger time does not change dramatically over the simulated time.
 
@@
 
-In SET0, an IMRI develop in $212$ cases out of 2000, i.e.
-$f_{\rm mer} = 10.6\%$ of formation probability.
-Concerning the formation channel, $8\%$ of IMRIs formed from Disrupted, $66.5\%$ from Hierarchical, and $25.5\%$ from Unstable .
-Similarly, in SET1 we find $268$ IMRIs ($13.4\%$), $4.9\%$ of them formed from Disrupted, $67.9\%$ from Hierarchical triples, and $27.2\%$ from Unstable.
+In SET0, an IMRI develop in $259$ cases out of 2000, i.e.
+$f_{\rm mer} = 12.95\%$ of formation probability.
+Concerning the formation channel, $6.6\%$ of IMRIs formed from Disrupted, $61.4\%$ from Stable, and $32\%$ from Hierarchical.
+Similarly, in SET1 we find $312$ IMRIs ($15.6\%$), $4.2\%$ of them formed from Disrupted, $62.8\%$ from Stable triples, and $33\%$ from Hierarchical.
+In SET2, we still find a similar merger probability ($f_{\rm mer} = 15.36\%$), but in this case the number of Hierarchical configurations outnumbers the other class of merger candidates covering the $83.7\%$ of the whole merger population.
+This is due to the fact that a larger outer semiaxis makes easier to satisfy the stability criterion in Equation \ref{stabcri}.
 All IMRIs formation probability for different channels are summarized in Table \ref{tab:t3}.
@@
         \hline 
-        model& $f_{\rm mer}$ & $f_{\rm mer,D}$ & $f_{\rm mer,H}$ & $f_{\rm mer,U}$\\
+        model& $f_{\rm mer}$ & $f_{\rm mer,D}$ & $f_{\rm mer,U}$ & $f_{\rm mer,H}$\\
              & $\%$& $\%$& $\%$& $\%$\\
         \hline
-        SET0 & $10.6$ & $8.0$ & $66.5$ & $25.5$ \\
-        SET1 & $13.4$ & $4.9$ & $67.9$ & $27.2$ \\
+		SET0 & $12.95$ & $6.6$ & $61.4$ & $32$ \\
+		SET1 & $15.60$ & $4.2$ & $62.8$ & $33$ \\
+		SET2 & $15.36$ & $2.3$ & $14$   & $83.7$ \\
         \hline
@@
 \centering
-\includegraphics[width=8cm]{semiaxis}\\
-\includegraphics[width=8cm]{ecce}
+\includegraphics[width=\columnwidth]{semiaxis}\\
+\includegraphics[width=\columnwidth]{ecce}
 \caption{Top panel: semi-major axis distribution for the inner binary.
@@
 In general, it seems that, regardless of the set, IMRI candidates with masses below $5\times10^3\Ms$ have, on average, $\langle e_\gw\rangle$ larger compared to the whole simulations sample, while this trend reverses for heavier IMRIs.
-
 The average eccentricity increases in the $10^2-5\times10^3\Ms$ mass range, peaking at around $500-1000\Ms$, and than decreases rapidly at increasing the IMBH mass.This implies that the evolution of the inner binary leads the eccentricity to achieve larger values in correspondence of lighter IMBHs.
-
 We find that IMBHs with masses typical of star clusters $10^3<M_\ibh/\Ms<10^4$ are expected to form, on average, extremely eccentric IMRIs, while the eccentricity at formation attains more moderate values at IMBH masses typical of low-mass dwarf galaxies and nuclear clusters.
-
 While affecting the eccentricity, the IMBH mass does not have a significant effect on the companion BH mass. Indeed, IMRIs light component masses follows the assumed BH mass distribution.
@@
 \centering
-\includegraphics[width=8cm]{average_ecc_sets}\\
+\includegraphics[width=\columnwidth]{average_ecc_sets}\\
 \caption{The average eccentricity ($\langle e_{\rm mer}\rangle$), calculated at the end of simulaitons in different IMBH mass bins, as a function of the IMBH mass and for different sets.
@@
 
-In order to uncover what is the role played by the IMBH in determining IMRIs formation, we calculate the 
-percentage of IMRIs formed in different mass bins.
+The merger times associated with IMRIs show a broad distribution regardless of the models set considered.
+Figure \ref{fig:f6} shows the cumulative distribution of $t_\gw$ calculated as discussed in Section \ref{sec:imris}.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{TGW_distribution}
+\caption{Cumulative distribution of IMRI merger times for all the models investigated.}
+\label{fig:f6}
+\end{figure}
+
+In order to uncover what is the role played by the IMBH in determining IMRIs formation, we calculate the percentage of IMRIs formed in different mass bins.
 This quantity, namely $f_{\rm mer}$, represents {\it de facto} IMRIs formation probability.
 We find that $f_{\rm mer}$ follows quite a precise trend, regardless of the set, thus in what follows we focus on SET0 only, for clarity's sake.
-Figure \ref{fig:f5} shows the $f_{\rm mer}-M_\ibh$ relation.
-We differentiate between IMRIs forming in disrupted triples, in a hierarchical or unstable configuration.
+
+\begin{figure}
+	\centering
+    \includegraphics[width=\columnwidth]{mergers}
+	\caption{IMRIs formation probability as a function of the IMBH mass for SET0.
+Red open squares shows all the models that are in an either stable or hierarchical configuration at the end of the simulation.
+Open dark blue circles identify IMRIs.
+From larger to smaller circles, blue filled circles represent IMRIs formed from unstable, hierarchical, and disrupted triples.}
+	\label{fig:f7}
+\end{figure}
+
+Figure \ref{fig:f7} shows the $f_{\rm mer}-M_\ibh$ relation in the case of SET0. We differentiate between IMRIs forming in disrupted triples, in a hierarchical or unstable configuration. 
 Our results suggest that an IMBH-BH-BH has a $10\%$ of probability to arrange in a hierarchical configuration, regardless of the IMBH mass or the GW timescale.
@@
 
-In the IMBH mass range $M_\ibh>10^3\Ms$, the IMRIs formation probability is well described by a simple powerlaw
+Figure \ref{fig:f8} shows how $f_{\rm mer}$ varies for the three set explored. In the IMBH mass range $M_\ibh>10^3\Ms$, this relation is well described by a simple powerlaw
 \begin{equation}
@@
 \end{equation}  
-with $\alpha = (7\pm2)\times 10^{-3}$ and $\beta = 0.45\pm0.03$.
+with $\alpha = (1.5\pm0.2)\times 10^{-2}$ and $\beta = 0.39\pm0.02$.
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{mergers.eps}
-    \caption{Percentage for IMRIs formation as a function of IMBH mass.
-Red open squares shows all the models that are hierarchical at the end of the simulation.
-Open dark blue circles identify IMRIs.
-From larger to smaller circles, blue filled circles represent IMRIs formed from unstable, hierarchical, and disrupted triples.}
-    \label{fig:f5}
+    \includegraphics[width=\columnwidth]{merger_sets.eps}
+    \caption{IMRIs formation probability as a function of the IMBH mass for the three simulated sets.}
+    \label{fig:f8}
 \end{figure}
@@
 
-\subsection{IMRIs merger rate}
-
-{\bf Previous studies based on full consistent N-body simulations of star clusters containing IMBHs with various masses and general properties  \citep{konstantinidis13,haster16,leigh14, macleod16} have shown that binary formation involving an IMBH takes place at a rate of $R_{\rm bin} \sim 10^{-7}$ yr.
-Assuming typical ages for globular-like star clusters of $t_{\rm age}\sim 10^{10}$ yr and assuming that IMBH buildup occurs in the clusters early lifetime ($\lesssim 1$ Gyr), we can use the merger probability fitting function depicted in Equation \ref{fmerg} to infer IMRIs merger rate per typical cluster
-\begin{equation}
-    \Gamma(M_\ibh) = R_{\rm bin}t_{\rm age}f_{\rm mer} \sim 0.7\left(\frac{M_{\ibh}}{10^2\Ms}\right)^{0.45},
-\end{equation}
-ranging from $\Gamma_{\rm IMRI} = 7-50$ yr$^{-1}$ for $M_\ibh = 10^2-10^4\Ms$, respectively.
-
-To put such a quantity in the context of MW-like galaxies, we need to make assumptions on the IMBH putative mass function.
-As recently suggested by Arca Sedda et al (in prep.), out of the 151 Galactic GCs currently known, around 35 might be harbouring, at present time, an IMBH with mass in the range $10^3-10^4\Ms$.
-They find that the mass distribution of these putative IMBHs can be described by a Maxwellian in the form
-\begin{equation}
-    f(x_\ibh) = \frac{a}{\sigma\sqrt(2\pi)}\exp{\left(-\frac{\left(x_\ibh - \mu\right)^2}{ (2\sigma^2)}\right)},
-\end{equation}
-with $x_\ibh\equiv \Log M_\ibh$, and $a=0.14\pm0.3$ , $\mu = 4.01\pm0.09$ and $\sigma = 0.4\pm0.1 $.
-
-Combining equations above, we can define a IMRI merger rate for MW-like galaxies as
-\begin{equation}
-    \Gamma_{\rm MW} = f_\ibh N_\gc \int \Gamma(M_\ibh) f(x_\ibh) {\rm d}M_\ibh,
-\end{equation}
-where $f_\ibh N_\gc$ is the number of GCs containing an IMBH. This equation has analytical solution
-which has analytical solution
-\begin{align}
- \frac{\Gamma_{\rm MW} (x_\ibh)}{f_\ibh N_\gc} =&   \frac{a}{2} (A + B\mu) {\rm erf}\left(\frac{x_\ibh-\mu}{\sigma\sqrt{2\pi}} \right) + \nonumber\\
-                                & - \frac{a}{\sqrt(2\pi)}B \sigma \exp{\left(\frac{-\left(x_\ibh-\mu\right)^2}{2\sigma^2}\right)},
-\end{align}
- the coefficients $A = \alpha -\beta \Log(100)$ and $B \equiv \beta$ are conveniently manipulated from Equation \ref{fmerg}.
-
-Assuming a typical IMBH population spanning the mass range $10^2-10^4\Ms$, a number of GCs $N_\gc = 151$, a fraction $f_\ibh \simeq 35/151$ of GCs hosting an IMBH we can infer the MW-IMRI rate 
-\begin{equation}
-\Gamma_{\rm MW,IMRI} \simeq 4\times 10^{-3} {\rm MW}^{-1} {\rm yr}^{-1}
-\end{equation}
-
-}
-
-\subsection{Serendipitous formation of stellar BH binaries around an IMBH}
+\subsection{The serendipitous formation of stellar BH binaries around an IMBH}
 
@@
 \centering 
-\includegraphics[width=8cm]{kozai_151}
+\includegraphics[width=\columnwidth]{kozai_151}
 \caption{Top panel: time evolution of the merger timescale for model number 151, in which two BHs pair together while the IMBH acts as a perturber.
@@
 \end{figure}
+
+\subsection{IMRIs merger rate}
+
+Previous studies based on full consistent N-body simulations of star clusters containing IMBHs with various masses and general properties  \citep{konstantinidis13,haster16,leigh14, macleod16} have shown that binary formation involving an IMBH takes place at a rate of $R_{\rm bin} \sim 10^{-7}$ yr.
+Assuming typical ages for globular-like star clusters of $t_{\rm age}\sim 10^{10}$ yr and assuming that IMBH buildup occurs in the clusters early lifetime ($\lesssim 1$ Gyr), we can use the merger probability fitting function depicted in Equation \ref{fmerg} to infer the total number of IMRIs formed for a given IMBH mass and over a cluster lifetime $t_{\rm age}$
+\begin{equation}
+    N_\gc(M_\ibh) = R_{\rm bin}t_{\rm age}f_{\rm mer} \sim 15\left(\frac{M_{\ibh}}{10^2\Ms}\right)^{0.38},
+\end{equation}
+ranging from $\Gamma_{\imri} = 15-90$ yr$^{-1}$ for $M_\ibh = 10^2-10^4\Ms$, respectively.
+To put such a quantity in the context of MW-like galaxies, we need to make assumptions on the IMBH putative mass function.
+Assuming that the initial mass function of GCs follows a power-law and exploiting Equation \ref{mcmibh}, we can write the IMBH mass function as $f(M_\ibh) = k (M_\ibh/10^\alpha)^{1/beta}$.
+The normalization constant $k$ can be calculated by assuming that the mass in clusters constitute a fraction of the total galaxy mass:
+\begin{equation}
+k = \frac{\delta M_g (2-s)}{(M_{\gc 2}^{2-s} - M_{\gc 1}^{2-s})},
+\label{normal}
+\end{equation}
+with $\delta = 5\times 10^{-4}$ \citep{webb15,belczinski17}, $M_g = 6\times 10^{10}\Ms$ and $M_{\gc 1,2} = (5\times 10^3 - 8\times 10^6)\Ms$ the range of GC initial masses allowed.
+
+%As recently suggested by \cite{AAG19}, out of the 151 Galactic GCs currently known, around 35 might be harbouring, at present time, an IMBH with mass in the range $10^3-10^4\Ms$.
+They find that the mass distribution of these putative IMBHs can be described by a Maxwellian in the form
+%\begin{equation}
+%    f(x_\ibh) = \frac{a}{\sigma\sqrt(2\pi)}\exp{\left(-\frac{\left(x_\ibh - \mu\right)^2}{ (2\sigma^2)}\right)},
+%\end{equation}
+%with $x_\ibh\equiv \Log M_\ibh$, and $a=0.14\pm0.3$ , $\mu = 4.01\pm0.09$ and $\sigma = 0.4\pm0.1 $.
+Combining equations above, we can infer the total number of IMRIs  MW-like galaxies as
+\begin{align}
+    N_{\rm MW} =& f_\ibh N_\gc \int_{M_{\ibh ,1}}^{M_{\ibh ,2}} \Gamma(M_\ibh) \times \nonumber \\
+    & \times f(M_\ibh) \frac{\derd M_\gc}{\derd M_\ibh} {\rm d}M_\ibh,
+\end{align}
+where $f_\ibh N_\gc$ is the number of GCs containing an IMBH, and the term $\derd M_\gc / \derd M_\ibh$ is used to perform a change of variable from the GC to the IMBH mass.
+The integral has analytical solution in the form
+\begin{equation}
+N_{\rm MW} = K \frac{M_{\ibh ,2}^{\beta + b(1-s)} - M_{\ibh ,1}^{\beta + b(1-s)}}{\beta + b(1-s)},
+\end{equation}
+with the parameter $K$ containining all the constant factors.
+
+%
+%
+%
+% \frac{\Gamma_{\rm MW} (x_\ibh)}{f_\ibh N_\gc} =&   \frac{a}{2} (A + B\mu) {\rm erf}\left(\frac{x_\ibh-\mu}{\sigma\sqrt{2\pi}} \right) + \nonumber\\
+%                                & - \frac{a}{\sqrt(2\pi)}B \sigma \exp{\left(\frac{-\left(x_\ibh-\mu\right)^2}{2\sigma^2}\right)},
+%\end{align}
+% the coefficients $A = \alpha - \beta\ln(100)$ and $B \equiv \beta$ are conveniently manipulated from Equation \ref{fmerg}.
+%Assuming a typical IMBH population spanning the mass range $10^2-10^4\Ms$, a number of GCs $N_\gc = 151$, a fraction $f_\ibh \simeq 35/151$ of GCs hosting an IMBH we can infer the MW-IMRI rate 
+%\begin{equation}
+%\Gamma_{\rm MW,IMRI} \simeq 4\times 10^{-3} {\rm MW}^{-1} {\rm yr}^{-1}
+%\end{equation}
+Assuming $t_{\rm age} = 10$ Gyr and in the IMBH mass range of $10^2 - 10^4\Ms$, we derive an IMRI merger rates for MW-like galaxies of
+\begin{equation}
+\Gamma_{\rm MW} = 2.26\times 10^{-5} {\rm ~yr} \left(\frac{10{\rm ~Gyr}}{t_{\rm age}}\right)\left(\frac{f_\ibh}{0.2}\right)\left(\frac{N_\gc}{180}\right).
+\end{equation}
+The number of MW-analogs in the local Universe (redshift $z<0.1$) is roughly proportional to the luminosity distance $D_L$, namely $P_{\rm MW} = 4\pi/3 \times 0.0116(2.26)^{-3}D_L^3$ with $D_L$ expressed in Mpc \citep{abadie10}.
+Thus a rough estimate of potential IMRIs developing in MW-like galaxies in the local Universe is given by $\Gamma_{\rm MW} \times P_{\rm MW} = 10.5$ yr$^{-1}$.
+This is a simple estimate, though, which not account for the distribution of galaxies across different redshift or the actual volume within which a detector is sensitive.
+The launch of the LISA detector and the start of operations of the next generation of GW observatories like the Einstein Telescope (ET) will enable us to observe this kind of objects at cosmological distances.
+Therefore, to infer the IMRI merger rates, we need to take into account in our calculation how the number density of galaxies varies across redshift $z$.
+The GW source {\it horizon} determines the maximum distance in space, or the redshift $z_{\rm hor}$, at which the source signal is detected with a threshold signal-to-noise ratio (SNR), namely:
+\begin{equation}
+{\rm SNR^2} = \int_{f_1}^{f_2} \displaystyle{\frac{h_c^2(f,z_{\rm hor})}{S_n^2(f)}} {\rm d}f,
+\end{equation}
+with $f_{1,2}$ the initial and final frequency of the GW signal, $h_c(f,z)$ its characteristic strain, and $S_n(f)$ its sensitivity.
+To determine this quantity, we integrate the final stage of the IMRI signal assuming an observation time of 4 yr -- i.e.
+the nominal duration time of the LISA mission -- and we calculate the value of $z_{\rm hor}$ at which we get an SNR of 15.
+We assume the set of cosmological parameters measured by the Planck mission, namely $H_0 = 67.74$ km/s/Mpc$^{3}$, $\Omega_m = 0.3089$, $\Omega_\Lambda = 0.6911$ \citep{planck15}.
+To calculate $z_{\rm hor}$, we vary the IMBH mass in the range $50-10^6\Ms$ assuming that the companion has a mass of either $10$ or $30\Ms$.
+Figure \ref{fig:fhor} shows how the horizon redshift changes for four different detectors: the Laser Interferometer Space Antenna \citep[LISA\footnote{\url{https://www.elisascience.org/}},][]{amaro12}, the Deciherz Gravitational-Wave Observatory \citep[DECIGO\footnote{\url{http://tamago.mtk.nao.ac.jp/spacetime/decigo_e.html}},][]{seto01}, the Einstein Telescope \citep[ET\footnote{\url{http://www.et-gw.eu/}},][]{punturo10}, and LIGO.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{horizon_IMBH}
+\caption{Horizon redshift as a function of the IMBH mass assuming a BH companion with mass $10 \Ms$ (lower curves) or $30\Ms$ (upper curves).
+Different curve collections correspond to different detectors: LISA (straight lines), DECIGO (dashed lines), ET (dotted lines), LIGO (dot-dashed lines).
+}
+\label{fig:fhor}
+\end{figure}
+
+From the plot is evident that ground based telescopes provide a relatively limited view on the IMBH realm, although LIGO can provide insights on low-mass IMRIs ($<500\Ms$) up to redshift $z_{\rm hor} = $ and ET will enable the observation of IMRIs with mass $<10^3\Ms$ up to $z_{\rm hor} = 1-10$, the same range of redshift accessible with LISA to listen GWs from heavy IMRIs ($M_{\imri}>10^4\Ms$).
+Decihertz observatories like DECIGO \citep{KawamuraEtAl2011} and similarly designed mission \citep{arca19}, instead, will allow the detection of IMRIs in the whole $50-10^6\Ms$ mass range up to the dawn of the Universe, thus constituting ideal detectors to unveil the truly nature of IMBHs.
+
+Once that the dependence between the horizon redshift and the IMBH mass is determined, we can infer the IMRIs rate by calculating the total number of IMRIs inside the cosmological volume encompassed by $z_{\rm hor}$, a requirement that can be expressed as:
+\begin{align}
+\Gamma_{\imri} = & \Omega_s \int_{M_{\ibh ,1}}^{M_{\ibh ,2}} \int_{0}^{z_{\rm hor}} \frac{\derd n_{\imri}}{\derd M_\ibh\derd z} \times \nonumber \\
+& \times \frac{\derd V_c}{\derd z}  \derd z \derd M_\ibh,
+\end{align}
+being $\derd V_c/\derd z$ the comoving cosmological volume element, $\xi(M_\ibh)$ the IMBH mass function, and $\derd n_{\imri}/\derd M_\ibh$ the number of IMRIs per unit of IMBH mass.
+We can write the latter quantity as
+\begin{align}
+\frac{\derd n_{\imri}}{\derd M_\ibh} =& f_{\imri}(M_\ibh) p_\ibh e_{\imri}\times \nonumber \\
+& \times \frac{\derd n}{\derd M_g\derd z}\frac{\derd n_\gc}{\derd M_\gc}\frac{\derd M_\gc}{\derd M_\ibh}.
+\end{align}
+Here, $\derd n/(\derd M_g \derd z)$ represents the number of galaxies per unit of redshift and galaxy mass, $\derd n/\derd M_\gc$ is the number of clusters per cluster mass in a given galaxy, $\derd M_\gc/\derd M_\ibh$ connects GCs and IMBHs, $e_\imri$ is the number of times that the same IMBH can form an IMRI with a stellar companion, $f_{\imri}(M_\ibh)$ is the fraction of IMRIs that undergo merger within a Hubble time (a quantity that is extracted from our simulations), and $p_\ibh$ represents the probability for a cluster to host an IMBH.
+In the following, we assume $p_\ibh = 0.2$ \citep{giersz15}.
+
+The term $\derd M_\gc / \derd M_\ibh$ can be calculated by inverting Equation \ref{mcmibh} and performing the derative.
+For the number distribution of the GCs mass in a given galaxy, $\derd n/\derd M_\gc$, we assume a power-law
+\begin{equation}
+\frac{\derd n}{\derd M_\gc} = k M_\gc^{-s},
+\end{equation}
+with the slope $s = 2.2$ and the normalization constant given in Equation \ref{normal}.
+Following the previous calculations, we assume an average galaxy mass of $6\times 10^{10}\Ms$, and $M_{\gc 1,2} = (5\times 10^3 - 8\times 10^6) \Ms$, corresponding to an IMBH mass range $M_\ibh \simeq (30 - 4.6\times 10^4)\Ms$ according to Equation \ref{mcmibh}, which can also be used to write $M_\gc^{-s} = aM_\ibh^{-bs}$, with $a,b$ obtained manipulating conveniently the relation.
+The $\derd n/(\derd M_g\derd z)$ is obtained exploiting the results in \cite{conselice16}, who studied the distribution of galaxies with stellar masses up to $10^{12}\Ms$ up to redshift $z=8$.
+In particular, we exploit the following parametric expression of galaxies number density
+\begin{equation}
+\phi(z) = -\frac{\phi_* 10^{(\alpha_* + 1)(M_2-M_*)}}{\alpha_* + 1},
+\end{equation}
+with $\phi_*,~\alpha_*,~M_*$ depending on the redshift \citep[see Table 1 in][]{conselice16}, and $M_2 = 12$.
+
+Substituting all the terms and manipulating them conveniently, the total number of IMRI in the portion of Universe accessible to a given detector is thus given by
+\begin{align}
+N_{\imri,1} = & k a^{1-s} b p_\ibh e_\imri \times \nonumber \\
+& \times \int_{M_{1}}^{M_{2}} \int_0^{z_{hor(M_\ibh)}} M_\ibh^{(1-s)b-1}  \times \nonumber \\
+& \times  f_{\imri}(M_\ibh) \phi(z) \frac{\derd V_c}{\derd z} \derd z \derd M_\ibh.
+\end{align}
+
+Observations and models suggest that GCs formation peakes at redshift $z=2$, corresponding to a formation time of $t_{\gc ,f} = 3.285$ Gyr.
+This would imply that the maximum redshift at which a GC containing an IMBH can be observed is the maximum between the horizon redshift and the GC formation redshift.
+Even in the case in which we assume that GCs forms continuously, we need to set a maximum redshift above which stars did not form yet.
+We set $z = 6$, corresponding to the epoch of reionization.
+Thus, we capped the horizon redshift with either $z=2$ (peak of GC formation), or $z=6$ (formation of the first stars).
+
+The time over which these IMRI forms can be estimated as the sum of the cluster formation time, the IMBH formation time, the IMRIs formation time, and the IMRI merger timescale:
+\begin{equation}
+T = t_{\gc ,f} + t_{\ibh ,f} + t_{\imri, f} + t_{\rm GW}. 
+\end{equation}
+The physics that regulate IMBH formation is still debated and partly unknown.
+Depending on the formation scenario, models suggest that the IMBH growth can occur either on short ($\sim 1$ Gyr) or long ($\simeq 5-10$ Gyr) timescales.
+As discussed recently, {\it fast} IMBHs could outnumber those forming slowly \citep{giersz15,AAG19}, thus in our calculations we assume $t_{\ibh ,f} = 2$ Gyr.
+The formation of an IMRI scales with the mass-segregation timescale in the host cluster, which is expected to be of the order of $\sim 0.1-1$ Gyr, while for $t_\gw$ we calculate, from our models, the value at which the number of mergers is half the total number, i.e.
+$N_\gw(t_\gw) = 0.5 N_\gw$.
+This corresponds to $t_\gw = 0.6-1.5$ Gyr.
+
+An alternative way, yet similar, to calculate the merger rate is by exploiting the cosmological GC star formation rate $\rho_{\rm SFR}(z)$, which can be used to calculate the total number of GCs at a given redshift
+\begin{equation}
+N(z_{\rm max}) = \frac{1}{<M_\gc>} \int_0^{z_{\rm max}} \rho_{\rm SFR}(z)\frac{\derd V_c}{\derd z}\derd z.
+\end{equation} 
+Given the power-law GCs mass function used in the previous method, the normalization factor in this case become
+\begin{align}
+k  =&\frac{(1-s)}{M_{\gc, 1}^{1-s} - M_{\gc ,2}^{1-s}},
+\end{align}
+and the total number of IMRI inside a given cosmological volume is thus given by
+\begin{align}
+N_{\imri, 2} = & k a^{1-s} b p_\ibh e_\imri \int_{M_{1}}^{M_{2}} \int_0^{z_{hor(M_\ibh)}} M_\ibh^{(1-s)b-1} \times \nonumber \\
+& f_{\imri}(M_\ibh) N(z_{\rm max}) \frac{\derd V_c}{\derd z} \derd z \derd M_\ibh.
+\end{align}
+
+An estimate of the merger rate can therefore be calculated as $\Gamma_\imri = N_\imri / T$. 
+Table \ref{tab:5} summarizes the merger rates calculated for different instruments, and assuming different parameters.
+
+Our results suggest that LIGO can already be capable of observing up to $\sim 1.25-4.33$ mergers over a 4 yr observation involving IMRIs with a total mass $M_\imri = 40-230\Ms$ and mass ratio $M_\bh / M_\ibh = 0.05 - 1$ out to redshift $z = 0.15-0.57$.
+Over the same observation time, LISA would enable us to observe $\sim 1.9-30$ mergers with larger masses $M_\imri < 5\times 10^4\Ms$ and lower mass ratios, down to $q = 2\times 10^{-4}$, out to redshift $z \simeq 0.7-1.8$.
+
+While the constraints on "present-day" technologies is already quite encouraging, the next generation of both ground- and spaced-observatories could provide quite a large amount of observation up to the maximum redshift allowed ($z=2-6$).
+Assuming a 4 yr observation mission, ET could detected up to $120-2600$ IMRIs per yr with masses $M_\imri < 2000 \Ms$.
+The space-based DECIGO could provide an even larger amount of observations per yr ($\sim 250-4400$ in 4 yr of observation), enabling the observation of IMRIs with total mass up to $\sim 5\times 10^4\Ms$ up to the epoch of GC formation and even up to the reionization epoch.
+
+\begin{table*}
+\caption{IMRI merger rate for different detectors}
+\begin{center}
+\begin{tabular}{cccccccc}
+\hline
+Instrument & $M_{\rm SBH}$ & $z_{\rm max}$ & $M_{\ibh ,1}$ & $M_{\ibh ,2}$ & $T$ & $\Gamma_1$ & $\Gamma_2$ \\
+   & $\Ms$ & &$\Ms$ & $\Ms$ & Gyr & yr$^{-1}$ & yr$^{-1}$ \\ 
+\hline
+LIGO & $10$ & $0.38$ & $29$ & $200$ & $8$ & $1.25$ &$1.46$ \\
+LIGO & $10$ & $0.38$ & $29$ & $200$ & $8$ & $1.25$ &$1.46$ \\
+LIGO & $30$ & $0.57$ & $29$ & $200$ & $8$ & $3.00$ &$4.33$ \\
+LIGO & $30$ & $0.57$ & $29$ & $200$ & $8$ & $3.00$ &$4.33$ \\
+LISA & $10$ & $0.70$ & $29$ & $46240$ & $8$ & $1.90$ &$2.75$ \\
+LISA & $10$ & $0.70$ & $29$ & $46240$ & $8$ & $1.90$ &$2.75$ \\
+LISA & $30$ & $1.78$ & $29$ & $46240$ & $8$ & $29.34$ &$23.31$ \\
+LISA & $30$ & $1.78$ & $29$ & $46240$ & $8$ & $29.34$ &$23.31$ \\
+ET & $10$ & $2.00$ & $29$ & $2000$ & $8$ & $214.69$ &$123.87$ \\
+ET & $10$ & $6.00$ & $29$ & $2000$ & $8$ & $2155.25$ &$396.60$ \\
+ET & $30$ & $2.00$ & $29$ & $2000$ & $8$ & $238.18$ &$136.55$ \\
+ET & $30$ & $6.00$ & $29$ & $2000$ & $8$ & $2571.14$ &$458.30$ \\
+DECIGO & $10$ & $2.00$ & $29$ & $46240$ & $8$ & $357.06$ &$248.20$ \\
+DECIGO & $10$ & $6.00$ & $29$ & $46240$ & $8$ & $4227.86$ &$996.72$ \\
+DECIGO & $30$ & $2.00$ & $29$ & $46240$ & $8$ & $357.06$ &$248.20$ \\
+DECIGO & $30$ & $6.00$ & $29$ & $46240$ & $8$ & $4227.86$ &$996.72$ \\
+\hline
+\label{tab:5}
+\end{tabular}
+\end{center}
+\end{table*}
 
@@
 Using this definition, we show in Figure \ref{F10} how the peak frequency and eccentricity vary for mergers in our models.
-In order to understand whether these sources can be audible to GW observatories, we superpose our calculations to the observational windows of the Laser Interferometer Space Antenna \citep[LISA\footnote{\url{https://www.elisascience.org/}},][]{amaro12}, the Deciherz Gravitational-Wave Observatory \citep[DECIGO\footnote{\url{http://tamago.mtk.nao.ac.jp/spacetime/decigo_e.html}},][]{seto01}, and the Einstein Telescope \citep[ET\footnote{\url{http://www.et-gw.eu/}},][]{punturo10}.
+In order to understand whether these sources can be audible to GW observatories, we superpose our calculations to the observational windows LISA, DECIGO, ET, LIGO, and the Japanese observatory KAGRA.
 
@@
 \centering
-\includegraphics[width=8cm]{freq_evo}\\
+\includegraphics[width=\columnwidth]{freq_evo}\\
 \caption{Frequency (x-axis) and eccentricity (y-axis) evolution for merging binaries in our models.
@@
 Approximately $10\%$ instead are characterized by GW emission in DHz regime, being potentially observed with LIGO and, in the future, with DECIGO and ET.
-The numbers of sources appearing in different bands are summarized in Table \ref{tab:t4}
+The numbers of sources appearing in different bands are summarized in Table \ref{tab:t4}.
+From Table \ref{tab:t4} appears evident that the number of IMRIs entering the $> 10$ Hz band is larger than in the other two sets.
+This is due to the fact that, for IMBH masses $M_\ibh < 10^4\Ms$ the number of mergers in SET2 is up to two times larger, thus causing a larger number of high-frequency GW emitters.
+It is interesting to note that a handful of sources could have a non-negligible eccentricity both in the LISA and DECIGO observational band, while at larger frequencies the binaries are already completely circular.
+In order to better highlight the probability for low-frequency detectors to observe eccentric IMRIs, we show in Figure \ref{F11} the eccentricity distribution of sources entering the mHz and Hz frequency bands.
+We find that the amount of sources maintaining an eccentricity above 0.1 while transiting either the low- or high-frequency bands of GW detectors is limited to $1-5\%$, regardless of the models set.
 
@@
      \centering
-     \caption{IMRI frequency bands}
+     \caption{Number of IMRI in different frequency bands}
      \begin{tabular}{ccccccc}
@@
         \hline
-        model & IMRI - total number & $N_{\rm mHz}$ & $N_{\rm cHz}$ & $N_{\rm dHz}$ & $N_{\rm Hz}$ & $N_{\rm DHz}$ \\ 
-              &                     &$0.5-5$ mHz    & $ 0.5-5$ cHz  &  $0.5-5$ dHz & $0.5-10$ Hz & $>1$ DHz \\
+        model & IMRI & $N_{\rm mHz}$ & $N_{\rm cHz}$ & $N_{\rm dHz}$ & $N_{\rm Hz}$ & $N_{\rm DHz}$ \\ 
+              &    total number  &$0.5-5$ mHz    & $ 0.5-5$ cHz  &  $0.5-5$ dHz & $0.5-10$ Hz & $>10$ Hz \\
         \hline
-        SET0 & $211$ & $204$ &  $207$ & $120$ & $46$ & $22$   \\
-        SET1 & $268$ & $256$ &  $259$ & $144$ & $56$ & $28$   \\
+		SET0& 259 & 255 & 257 & 158 & 60  & 14 \\
+		SET1& 312 & 306 & 309 & 184 & 62  & 15 \\
+		SET2& 307 & 306 & 307 & 212 & 129 & 40 \\
         \hline
@@
 
-It is interesting to note that a handful of sources could have a non-negligible eccentricity both in the LISA and DECIGO observational band, while at larger frequencies the binaries are already completely circular.
-In order to better highlight the probability for low-frequency detectors to observe eccentric IMRIs, we show in Figure \ref{F11} the eccentricity distribution of sources entering the mHz and Hz frequency bands.
-We find that only $10\%$ of sources have high eccentricity in the LISA band, while for DECIGO this quantity is slightly smaller ($\sim 7\%$).
-
 \begin{figure}
 \centering
-\includegraphics[width=8cm]{mergers_eccen}\\
+\includegraphics[width=\columnwidth]{mergers_eccen}\\
 \caption{Eccentricity distribution for IMRIs in our models. The eccentricity is calculated at the moment in which a source cross the mHz (red filled steps) or Hz frequency band (black steps).}
@@
 In order to infer whether these sources might be audible to GW observatories, we calculated the strain following \cite{kocsis12} for all the frequencies containing the $95\%$ of the emitted power.
-We assume a luminosity distance $D_L = 463$ Mpc (redshift $z=0.1$), and a 5 yr observation time.
+We assume a luminosity distance $D_L = 463$ Mpc (redshift $z=0.1$), and a 4 yr observation time.
 Figure \ref{F12} shows the evolution of the strain-frequency evolution for two different mergers, altogether with the eccentricity decrease due to GW circularization.
-One merger refers to an IMRI with total mass $M_H$
 
@@
 \centering
-\includegraphics[width=8cm]{example_signal}\\
+\includegraphics[width=\columnwidth]{example_signal}\\
 \caption{Strain calculated for the dominant frequency for two different models, assuming an infinite observational time.
@@
 
+In this paper we presented the results of a suite of 6000 direct N-body simulations modelling the evolution of an IMBH-BH binary orbited by a third BH, taking into account post-Newtonian corrections up to order 2.5 and the gravitational field of the host cluster (treated as an external potential).
+The simulations are gathered into three sets: set 0 and 1 differ in the scaling relation adopted to connect the masses of the IMBH and its host cluster, whereas set 2 is similar to set 0 but we assumed a range of wider orbits for the outer BH.
+In all models, we vary the IMBH mass between $10^2-10^6\Ms$ with the aim to unveil the dependence between this quantity and the probability for IMRIs to form.
+Our results can be summarized as follows:
 \begin{itemize}
-\item {\bf Make your point!}
+\item at formation, IMRIs formed via the IMBH-BH-BH interactions exhibit an eccentricity distribution much steeper than the initially adopted one, i.e.
+$N(e) \propto e^5$.
+The distribution of semimajor axis, instead, shows a sharp decline at values above $\sim 50$ AU and a clear cut-off at $\sim 100$ AU (Figure 3, put ref: \ref{});
+\item the average eccentricity of IMRIs at formation seems to decrease with the IMBH mass, suggesting that the formation of highly eccentric IMRIs through the channel described here is favoured for IMBH masses below $10^5\Ms$ (Figure 4, put ref: \ref{});
+\item merger times for this class of sources shows a steep rise toward $\sim 1-10$ Gyr, with a broad 
+distribution down to $\sim 1$ yr. In all the models investigated, more than $50\%$ of IMRIs have a merger time below $0.1-1$ Gyr (Figure 5, put ref: \ref{});
+\item from our simulations, we infer an IMRI formation probability of $12-15\%$, regardless of the assumptions made.
+This quantity increases at increasing the IMBH mass and, correspondingly, heavier GCs, following a powerlaw for IMBH masses above $10^3\Ms$ (Figure 6 - 7, put refs: \ref{});
+\item in a few particular cases, we find that the two stellar BHs have orbits sufficiently similar to favour the formation of a bound pair that orbit the IMBH.
+The IMBH field exert on the stellar BH binary Kozai-Lidov oscillations that trigger the binary merger in $\sim 10^7$ yr, a timescale $\sim 5600$ times smaller than the merger time for the same binary in isolation (Figure 8, put ref: \ref{}).
+We find that the probability for these events to occur is $\sim 0.8\%$;
+\item upon simplistic assumptions, we derive an IMRI occurrence rate of $\sim 2.26\times 10^5$ yr$^{-1}$ in the MW and similar galaxies, which corresponds to $\sim 10$ yr$^{-1}$ events in the volume encompassed by a luminosity distance of $D_L = 470$ Mpc (i.e.
+redshift $z\leq 0.1$) (Equation 16, put ref: \ref{});
+\item assuming a 4 yr observation time and a signal-to-noise ratio of 15, we calculate the horizon redshift of IMRIs for four GW detectors: LIGO, LISA, ET, DECIGO.
+We find that LIGO can observe IMRI with mass ratios above $0.05$ and total mass $<250\Ms$ out to redshift $z<0.6$.
+LISA will permit the observations of heavier IMRIs (total mass up to $10^5-10^6\Ms$) out to redshift $z=10$, but the horizon redshift will be much smaller ($z < 1$) for IMBHs with a mass $M_\ibh<10^4\Ms$.
+The next generation of GW telescopes has the potential to chase IMBHs and IMRIs formation much farther in time and space.
+ET can provide observations of IMRIs in the IMBH mass range $10^2-10^3\Ms$ out to redshift 10, whereas DECIGO can potentially probe IMRIs formation up to redshift $z > 100-1000$, well beyond the time at which the first stars formed.
+The possible construction of GW detectors sensitive in the dHz frequency band thus appear to be a very promising way to chase these systems up to the dawn of the Universe (Figure 9, put ref: \ref{});
+\item combining our simulations, the calculated horizon redshift, and taking advantage of observational limits on the cosmological distribution of galaxies, we derive an IMRI merger rate for the four detectors discussed in the previous point and assuming a 4 yr observation time.
+We find that LIGO should be capable of observing up to 1-5 IMRIs per year with masses below $230\Ms$, whereas LISA could deliver up to 30 observations per yr for IMRIs with masses up to $5\times 10^4\Ms$.
+The next generation of detectors will definitely lead to an improvement of these numbers, being the inferred rate for ET in the range of $250-2000$ yr$^{-1}$ for IMRIs with masses below $10^3\Ms$ and for DECIGO up to $4400$ yr$^{-1}$ for IMRIs covering the whole mass range $10^2-10^5\Ms$ (Table 4, put ref: \ref{});
+\item for all IMRIs in our sample, we follow the evolution of the orbital parameters down to the merger.
+Despite IMRIs tend to have a high eccentricity at formation, circularization due to GW emission has already took place by the time in which the source enter in the frequency range accessible by GW detectors.
+We find that only $\sim 1\%$ of IMRIs have a residual eccentricity above $e = 0.1$ when entering the mHz regime (Figure 11, put ref: \ref{});
+\item we derive the GW strain for all IMRIs in our sample, showing that these sources has the potential to be interesting multiband sources.
+Once decihertz observatories will fly and third generation detectors will be operative, we could be able to observe the whole evolution of IMRIs with masses in the range $10^2-10^4\Ms$ with at least two instruments, covering both the spiralling and merger phase (Figure 12, put ref: \ref{});
+
 \end{itemize}

### 2020-01-16 article.tex

@@
 \newcommand{\ARCHAIN}{\texttt{ARCHAIN}}
+
+\newcommand{\manuel}{\textcolor{red}}
+\newcommand{\pau}{\textcolor{blue}}
+\newcommand{\xian}{\textcolor{green}}
 
@@
 %
+\manuel{Put your comments by using \textbackslash + YOUR NAME + $\{$TEXT$\}$}\\
 We study the formation and evolution of intermediate mass ratio inspirals (IMRIs) triggered by the interactions between two stellar black holes (BHs) and an intermediate black hole (IMBH) inhabiting a globular cluster.
@@
 To explore the dependence between IMRI candidates eccentricity at formation and IMBH mass, we take the eccentricity directly from the last snapshot for models targeted as ``Disrupted'' and ``Unstable'', while for ``Hierarchical'' we record the maximum eccentricity.
-We then calculate the mean eccentricity value $\langle e_\gw\rangle$  in different mass bins, making the same for the subset of IMRI candidates, as shown in Figure \ref{fig:f4}.
+We then calculate the mean eccentricity value $\langle e_\gw\rangle$  in different mass bins, making the same for the subset of IMRI candidates, as shown in Figure \ref{fig:f5}.
 In general, it seems that, regardless of the set, IMRI candidates with masses below $5\times10^3\Ms$ have, on average, $\langle e_\gw\rangle$ larger compared to the whole simulations sample, while this trend reverses for heavier IMRIs.

### 2020-01-16 article.tex
Updates from Overleaf

@@
 
-\author{Manuel Arca Sedda and Pau Amaro-Seoane}
+\author{Manuel Arca Sedda}
 \affil{Zentrum f\"{u}r Astronomie der Universit\"{a}t  Heidelberg\\
@@
 Heidelberg, D-69120, DE}
-\affil{
-Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC)\\
-at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain\\
-Institute of Applied Mathematics, Academy of Mathematics and Systems Science, CAS, Beijing 100190, China\\
-Kavli Institute for Astronomy and Astrophysics, Beijing 100871, China\\
-Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36, 10623 Berlin, Germany
-}
-
+\author{Pau Amaro-Seoane}
+\affil{Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC)\\
+at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain\\}
+\affil{Institute of Applied Mathematics, Academy of Mathematics and Systems Science, CAS, Beijing 100190, China\\
+Kavli Institute for Astronomy and }
+\affil{Astrophysics, Beijing 100871, China\\
+Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36, 10623 Berlin, Germany}
+\author{Xian Chen}
 \begin{abstract}

### 2020-01-17 article.tex
Added a section on detectability in MW and LMC

@@
 
-\title{Formation and evolution of intermediate-mass ratio inspirals}
+\title{Formation and evolution of intermediate-mass ratio inspirals: \\detecting IMBHs in Milky Way globular clusters and in the local Volume with LISA}
 
@@
 \author{Xian Chen}
+\affil{Astronomy Department, School of Physics, Peking University, Beijing 100871, P.R. China}
+\affil{Kavli Institute for Astronomy and Astrophysics at Peking University, Beijing 100871, P.R. China}
+
 \begin{abstract}
@@
 The next generation of detectors will allow us to observe IMRI out to the peak of GC formation and even beyond, with an expected rate of $200-2000$ yr$^{-1}$ for ET ($M_{\rm imri} < 10^3\Ms$) and $250-4400$ yr$^{-1}$ for DECIGO ($M_{\rm imri} < 60 - 5\times 10^4 \Ms$).
-We show that a considerable number of sources can be observed are multiband thus can be observed with both low- and high-frequency detectors, especially in the case of future detectors.
+\manuel{We explore the possibility that LISA can provide detections of IMRIs in the Milky Way or in the Large Magellanic Cloud.
+Assuming that the time remaining to the merger exceeds 100 yr, we find that LISA could detect an IMBH with mass $10^3-10^4\Ms$ in Galactic star clusters with a signal-to-noise ratio (SNR) of $20-100$, and in the LMC with a SNR$=8-40$.
+These estimates suggest that LISA could provide the first direct detection of IMBHs formed in a stellar environments.} We show that a considerable number of sources can be observed are multiband thus can be observed with both low- and high-frequency detectors, especially in the case of future detectors.
 Although highly eccentric at formation, we find that only $\sim 1\%$ of IMRI will preserve a high eccentricity when entering the mHz frequency band.
@@
 might be possibly connected with the host cluster observational properties
-\citep{AAG18a}. Due to this, finding an unique way to unravel the presence of
+\citep{AAG18a}. \xian{(There is a recent ARAA review on IMBH, by Greene et al., arXiv:1911.09678.)} Due to this, finding an unique way to unravel the presence of
 IMBHs in GCs represents one of the most interesting challenges in modern
@@
 In this paper, we model the potential formation of an IMRI from the
-interactions between an IMBH and two stellar mass BHs. To reach the aim, we use
-$N$-body simulations that take into account in particles' equations of motion
-both the star cluster gravitational potential and post-Newtonian corrections up
-to 2.5 order. Varying the IMBH and BHs masses, their orbital configuration, and
-the host cluster structural properties, we build-up three sets consisting of
-2000 models each, which allow us to uncover three possible scenarios for IMRIs
-formation.
+interactions between an IMBH and two stellar mass BHs.  \xian{(Can we give some
+reference here to argue that why we expect two stellar BHs to form around a
+IMBH in the first place? Such as checking Konstantinidis et al. 2013, which
+showed in their Fig. 2 the locations of the ten modest massive black holes in
+the simulation.  At any time, how many stellar BHs are abound to the IMBH?)} To
+reach the aim, we use $N$-body simulations that take into account in particles'
+equations of motion both the star cluster gravitational potential and
+post-Newtonian corrections up to 2.5 order. Varying the IMBH and BHs masses,
+their orbital configuration, and the host cluster structural properties, we
+build-up three sets consisting of 2000 models each, which allow us to uncover
+three possible scenarios for IMRIs formation.
 
@@
     \item {\bf Disrupted triple.} The three-body interaction undergoes a chaotic phases that ultimately lead to the ejection of a stellar BHs, whereas the inner binary either preserves its original components or undergoes a component swap.
+\xian{(The disruption is caused mainly by the three-body interaction, or by the intruding
+energetic unbound stars? Can we provide an argument that the latter, intruding stars are not
+important? For example, something related to the hardness of the inner/outer binary? The
+inclusion of the intruding stars is a novel feature of this work compared to the other
+isolated three-body simulations, the novelty of which may be worth stressing.)}
     \item {\bf Stable triple.} The triple arranges in a configuration that satisfies the stability criterion for three-body systems. 
@@
 
+\section{Gravitational waves}
+\subsection{Detecting IMBHs in Milky Way globular clusters and in the Large Magellanic Cloud}
+\manuel{
+In this section, we exploit our results to investigate whether the current design of LISA provide enough sensitivity to unveil the presence of IMBHs in our closest neighbourhood. 
+To perform such a study, we assume to have a nearly circular IMRI with an IMBH mass in the range $10^2-10^6\Ms$ and a BH companion weighing either $10$ or $30\Ms$. 
+We assume that the IMRI emission frequency is 1 mHz, corresponding to an orbital semimajor axis $10^{-3}-10^{-2}$ AU. 
+The merger time for IMRIs in this configuration ranges between $100 and 10^4$ yr, thus much larger than the observation time.
+Assuming 4 yr observation time, the IMRI frequency will not vary sensibly, being the frequency variation $\Delta \ln f < 10^{-4}$.
+As noted by \cite{robson19}, whenever the latter quantity remains below 0.5 GW source should be treated as nearly stationary.
+Upon this assumption, the signal-to-noise ratio can be written as
+\begin{equation}
+    {\rm SNR}^2 = h_{\rm GB}^2 f / h_n,
+\end{equation}
+where $f$ is the source initial frequency, $h_n$ is the adimensional instrument sensitivity, and 
+\begin{equation*}
+    h_{\rm GB} = \frac{8T_{\rm obs}^{1/2} (G\mathcal{M}/c^3)^{5/3} (\pi f)^{2/3}}{\sqrt{5}D_L/c},
+\end{equation*}
+with $T_{\rm obs}$ the observation time, $\mathcal{M}$ the IMRI chirp mass, and $D_L$ the luminosity distance. Note that the relation above implies that the SNR scales with $D_L^{-1/2}$.
+Figure \ref{SNRMW} shows the SNR calculated for the LISA instrument for IMRIs having an initial frequency $f=1$ mHz and masses in the $10^2-10^6 \Ms$ range, assuming a luminosity distance of $D_L = 8$ kpc.
+We find that an IMRI with mass $M_\imri = (30 + 10^3)\Ms$ has an associated SNR of 20, whereas this quantity rises up to 100 for a $10^4\Ms$ IMBH. 
+These estimates suggest that LISA can crucial role in probing the existence of IMBHs formed in a stellar environment. 
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{snr_MW}
+    \caption{SNR for several IMRIs assuming an initial frequency of $1$ mHz, 4 yr of observation time, and a luminosity distance of $D_L = 8$ kpc.}
+    \label{fig:my_label}
+\end{figure}
+LISA can also be used to provide clues about the presence of IMBHs in nearby galaxies.
+For instance, it has been recently suggested that the Large Magellanic Cloud might be harbouring an IMBH with a mass in the range $4\times 10^3-10^4\Ms$ \citep{erkal19} and up to $10^7\Ms$ \citep{boyce17}, and that some of the clusters residing in the cloud can host IMBHs as well with masses in the range $10^3-10^4\Ms$ \citep{gualandris07}.
+Assuming a distance to the LMC $D_L = 49.97 \pm 1.13$ kpc \citep{pietrzy13}, we find that LISA might deliver observations of {\it Magellanic} IMRIs with an $SNR = 8-40$, with the lower(upper) value corresponding to an IMBH with mass $10^3\Ms$($10^4\Ms$) and a BH companion of $30\Ms$.
+}
+
 \subsection{IMRIs merger rate}
@@
 Different curve collections correspond to different detectors: LISA (straight lines), DECIGO (dashed lines), ET (dotted lines), LIGO (dot-dashed lines).
-}
+\xian{How many IMRIs in the LISA band can later be detected by LIGO/DECIGO, i.e., are suitable for multiband observations?
+Maybe it only depends on the mass of the IMBH?}}
 \label{fig:fhor}
@@
 We find that the probability for these events to occur is $\sim 0.8\%$;
-\item upon simplistic assumptions, we derive an IMRI occurrence rate of $\sim 2.26\times 10^5$ yr$^{-1}$ in the MW and similar galaxies, which corresponds to $\sim 10$ yr$^{-1}$ events in the volume encompassed by a luminosity distance of $D_L = 470$ Mpc (i.e.
-redshift $z\leq 0.1$) (Equation 16, put ref: \ref{});
+\item upon simplistic assumptions, we derive an IMRI occurrence rate of $\sim 2.26\times 10^5$ yr$^{-1}$ in the MW \xian{(I guess there is a typo here. The rate looks crazy!)} 
+and similar galaxies, which corresponds to $\sim 10$ yr$^{-1}$ events in the volume encompassed by a luminosity distance of $D_L = 470$ Mpc (i.e. redshift $z\leq 0.1$) (Equation 16, put ref: \ref{});
 \item assuming a 4 yr observation time and a signal-to-noise ratio of 15, we calculate the horizon redshift of IMRIs for four GW detectors: LIGO, LISA, ET, DECIGO.
@@
 was supported by the National Key R\&D Program of China (2016YFA0400702) and
-the National Science Foundation of China (11721303).
+the National Science Foundation of China (11721303, 11873022).
 

### 2020-07-07 main.tex
New Version - reply to referee

\documentclass[article]{aa}  
\usepackage{graphicx}
\usepackage{txfonts}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{color}
\usepackage{appendix}
\usepackage{multirow}
%\usepackage[flushleft]{threeparttable}
%\usepackage{hyperref}
%\usepackage{nameref}

\newcommand{\derd}{{\rm d}}
\newcommand{\Log}{{\rm Log}}
\newcommand{\Ms}{{\rm M}_\odot}
\newcommand{\Zs}{{\rm Z}_\odot}
\newcommand{\au}{{\rm AU}}
\newcommand{\gw}{{\rm GW}}
\newcommand{\gc}{{\rm GC}}
\newcommand{\kl}{{\rm KL}}
\newcommand{\ibh}{{\rm IMBH}}
\newcommand{\imbh}{{\rm IMBH}}
\newcommand{\imri}{{\rm IMRI}}
\newcommand{\inn}{{\rm in}}
\newcommand{\out}{{\rm out}}
\newcommand{\bh}{{\rm BH}}
\newcommand{\bhu}{{\rm BH1}}
\newcommand{\bhd}{{\rm BH2}}
\newcommand{\ARGdf}{\texttt{ARGdf~}}
\newcommand{\ARCHAIN}{\texttt{ARCHAIN~}}

\newcommand{\manuel}{\textcolor{red}}
\newcommand{\pau}{\textcolor{blue}}
\newcommand{\xian}{\textcolor{green}}
\begin{document}

\title{Formation and evolution of intermediate-mass ratio inspirals.}

\subtitle{Detecting intermediate-mass black holes in Milky Way globular clusters \\ and the Local Volume with LISA}

\titlerunning{Formation of IMRIs in Milky Way globular clusters and the Local Volume}	
\authorrunning{Arca Sedda, Amaro-Seoane, Chen}
\author{Manuel Arca Sedda \inst{1} \and Pau Amaro-Seoane \inst{2,}\inst{3,}\inst{4,}\inst{5} \and Xian Chen \inst{6,}\inst{5} }

\institute{Astronomisches Rechen-Institut. Zentrum f\"{u}r Astronomie der Universit\"{a}t Heidelberg, M\"onchhofstrasse 12-14, Heidelberg, D-69120, DE              
         \and         
			  Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC) at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain
		\and         
			  Institute of Applied Mathematics, Academy of Mathematics and Systems Science, CAS, Beijing 100190, China
		\and
			  Zentrum f{\"u}r Astronomie und Astrophysik, TU Berlin, Hardenbergstra{\ss}e 36, 10623 Berlin, Germany
		\and         
			  Kavli Institute for Astronomy and Astrophysics at Peking University, Beijing 100871, P.R. China	
		\and
			Astronomy Department, School of Physics, Peking University, Beijing 100871, P.R. China	             
\\		\email{m.arcasedda@gmail.com}			
\\    	\email{pau@ice.cat}
\\		\email{xian.chen@pku.edu.cn }
}

\date{Received...; accepted...}

\abstract 
{The next generation of gravitational wave (GW) observatories would enable the detection of intermediate-mass black holes (IMBHs), an elusive type of black holes that are expected to lurk in the centre of massive clusters, dwarf galaxies and, possibly, AGN accretion discs. Intermediate mass ratio inspirals (IMRIs), composed of an IMBH and a compact stellar object, constitute one promising source of GWs audible to these detectors.} 
{We study the formation and evolution of IMRIs triggered by the interactions between two stellar BHs and an IMBH inhabiting the centre of a globular cluster, with the aim of placing constraints on IMRIs formation rate and detectability.}
{We exploit direct $N$-body models varying the IMBH mass, the stellar BH mass spectrum, and the star cluster properties. Our simulations take into account the host cluster gravitational field and General Relativistic effects via Post-Newtonian terms up to order 2.5.} 
{The chaotic dynamics involving the two BHs and the IMBHs has a significant impact on IMRIs formation: globally, the IMRIs formation probability attains values $\sim 5-50\%$, with larger values corresponding to larger IMBH masses. Merging IMRIs tend to map out the stellar BH mass spectrum, thus suggesting that their future detections can provide clues about the co-evolution of IMBHs and stellar BHs in star clusters. Given the post-merger GW recoil, we find that in typical globular clusters an IMBH with mass above $M_\ibh\sim 10^3\Ms$ have a retention probability above $50\%$ only if the companion mass is below $M_\bh\sim30\Ms$. Lower IMBHs, $M_\ibh \lesssim 200\Ms$, are expected to be ejected out of their cluster whenever the merging companion mass exceeds $M_\bh\sim 10\Ms$. Thus, localizing an IMBH in the center of a star cluster would give us insights on its past evolution. Our models show that the remnant spin encodes information about the IMBH evolution: at masses $M_\ibh = 10^2-10^3\Ms$ the final spin is strongly affected by the companion BH, whereas for $M_\ibh > 10^4\Ms$ the initial IMBH spin is preserved upon multiple mergers. Thus, depending on the IMBH mass, measuring the spin would shed a light on the IMBH evolutionary track. We show that IMRIs are powerful multiband sources that can be seen across different GW detectors during their last phases of life. We suggest that LISA can unravel the presence of IMBHs in Milky Way globular clusters, where the inferred signal-to-noise ratio (SNR) cumulated over 4 yr of observation is SNR$=10-100$, or in the Large Magellanic Cloud, for which we get an SNR$=8-40$. We infer the merger rate for several GW detectors, suggesting that LIGO should be able to see $0.9-2.5$ events per year involving an IMBH with mass $>100\Ms$, whereas LISA might detect $6-60$ events per year involving IMBHs as heavy as $4\times 10^4\Ms$. The next generation of detectors will shed further light on IMBHs: the Einstein Telescope can deliver up to $10^3$ events per year triggered by IMBHs with $M_\ibh \leq 2\times 10^3\Ms$, whereas DECIGO will allow $400-3800$ detections per yr involving $M_\ibh < 5\times 10^4\Ms$.}

\keywords{black hole physics --- gravitational waves ---  globular clusters: general --- Galaxy: general}

\maketitle
%
%-------------------------------------------------------------------

\section{Introduction}

Intermediate mass black holes (IMBH), with masses in the range $10^2-10^5\Ms$, might represent the missing link between stellar and supermassive mass black holes. Dense stellar systems, such as globular clusters (GCs), are thought to be ideal factories for IMBH production via formation and collapse of a very massive stars through stellar collisions \citep{zwart02, freitag06b,freitag06c, giersz15, mapelli16},
or via multiple interactions and mergers between stars and stellar-mass BHs \citep{giersz15}. Unfortunately, a striking observational evidence for the presence of IMBHs inhabiting GCs is still missing due to the little dynamical effects that these objects have on their surroundings \citep[for recent reviews see][]{mezcua17,greene19}. Indeed, models suggest that several processes can mimic an IMBH, like anisotropies inthe GC kinematic  properties \citep{zocchi}, or the presence of a dense cluster of stellar mass BHs -- namely a BH subsystem -- that dominate the inner cluster centre \citep{AAG18b,AS16,vandermarel10}. Nevertheless, a few observational IMBHs candidates have been found for Galactic GCs
\citep{noyola10,lu13,lanzoni13,kiziltan17} and their mass and influence radius might be possibly connected with the host cluster observational 
properties \citep{AAG18a}. Due to this, finding an unique way to unravel the presence of IMBHs in GCs represents one of the most interesting challenges in modern astronomy. Beside this, the presence of an IMBH sitting in the centre of a dense cluster represents a scenario particularly appealing from the perspectives of gravitational waves (GW) astronomy. Indeed, a compact remnants orbiting the IMBH can enter a regime where GWs emission dominates, leading to the formation of an intermediate mass-ratio inspiral \citep[IMRI,][]{konstantinidis13,leigh14,haster16,macleod16}, a class of sources possible audible with the next generation of GW observatories like LISA \citep{seoane07,amaro12,seoane18}. However, in the highly dense regions that characterize star clusters centres, the formation of IMRIs is not a smooth process. Indeed, due to the continuous interactions with stars, an IMRI ``progenitor'', namely a tight IMBH-BH binary, might be subjected to strong perturbation induced, for instance by a passing-by BH. The three-body interaction involving the IMBH and the two BHs can lead to a variety of end states, including the formation of an IMRI, a stellar BH binary, the ejection of one BH, or even both, or the development of a head-on collision. At some extent, this scenario is similar to what is expected to happen in galactic nuclei, where supermassive BHs (SMBHs) can capture a compact object to form an extreme mass ratio inspiral. However, in the case of IMRIs the picture is complicated by the fact that this chaotic process can transfer to the IMBH an amount of energy sufficient to displace it sensibly from the cluster centre. Differently from galactic nuclei, where the SMBH remains well seated in the galactic potential well, the IMBH motion makes hard the use of any analytical approach to solve IMRIs dynamics. Quantifying the branching ratio for IMRIs formation constitute a fundamental step to assess the probability to observe these GW sources with the next generation of space-based detectors like LISA\footnote{\url{https://www.elisascience.org/}} \citep{seoane07,amaro12}, TianQin \citep{tianqin16} or Taiji \citep{taiji17}. In this paper, we model the potential formation of an IMRI from the interactions between an IMBH and two stellar mass BHs. This type of  configuration can temporarily form in the centre of clusters with IMBH mass $\sim 100-1000\Ms$ \citep{konstantinidis13,macleod16} and could last up to $10^7$ yr \citep{macleod16} although this depends strongly on the cluster initial properties. In fact, it is difficult to predict the actual amount of BHs that, at any time, interact with the IMBH, primarily because the majority of the studies conducted in the literature assume that the IMBH is already at the centre of the host cluster when stellar BHs form and sink toward the cluster centre \citep{leigh14,haster16}. Models in which the IMBH is a byproduct of stellar evolution and collisions, indeed, seem to point out that after the IMBH grows only a handful of stellar BHs are still present in the cluster $<3-5$ \citep{AAG19}. To reach the aim, we use $N$-body simulations that take into account in particles' equations of motion both the star cluster gravitational potential and post-Newtonian corrections at 1, 2, and 2.5 order. Varying the IMBH and BHs masses, their orbital configuration, and the host cluster structural properties, we build-up three sets consisting of 2000 models each, which allow us to uncover three possible scenarios for IMRIs formation.  
The paper is organized as follows: in Section \ref{num} we
present and summarize the numerical setup used to model the IMBH - BH
interaction, in Section \ref{res} we present and discuss the main properties of
the simulations output, in Section \ref{gra} we discuss the implications for GW
astronomy, while Section \ref{res} is devoted to the results summary and
conclusions.

\section{Initial conditions} 
\label{num}

{\bf
We simulate the evolution of the innermost region of the cluster, modelling the IMBH and two stellar mass BHs as live particles and
the remaining cluster as an external static potential. In order to explore the parameter space, we create six different models, each one consisting 
of 4000 simulations gathered in four different sub-classes, depending on the IMBH mass, for a total of 48,000 simulations. Our model is sketched in Figure \ref{f1}.

\begin{figure}
    \centering
    \includegraphics[width=7cm]{triple}
    \caption{Sketch of the IMBH-BH-BH triple configuration.}    
\label{f1}
\end{figure}

We vary the central IMBH mass in four classes, namely ${\rm Log}(M_\ibh/\Ms) = 2-3-4-5$. This range covers typical values of putative IMBH masses forming in stellar systems of various sizes, from young and open clusters, to globular clusters, and up to low-mass nuclear clusters and dwarf galaxies.
We note that the lowest value taken for $M_\ibh$ will likely involve mergers with mass ratio $> 0.1$, thus they fall outside the range of IMRIs. Nonetheless, exploring the low end of IMBH mass function will help us in better understanding the perspectives of IMBH-BH mergers from the point of view of both low- and high-frequency GW detectors, as discussed in Section XX.

The properties of the cluster in which the IMBH is embedded, which define the cluster potential, are varied depending on the model. The cluster density profile is assumed to be either a Dehnen sphere with inner slope $\gamma_\gc = 0.5$ (model S0, S3, S4, S5, S6) or $1.0$ (model S1), or a Plummer sphere (model S2). In both cases, the cluster half-light radius is assumed to be $R_{\rm eff} = 3.4$ pc, namely the mean value of Milky Way globular clusters \citep{harris14}. The mass of the cluster is calculated via the scaling provided by \cite{AS16}, connecting the host cluster mass $M_\gc$ with the total ``dark'' mass, inhabiting the cluster's centre, comprised of either an IMBH or a sizable population of stellar BHs
\begin{equation}
\Log \left(\frac{M_\gc}{\Ms}\right) = \alpha \Log \left(\frac{M_\ibh}{\Ms}\right) + \beta.
\label{mcmibh}
\end{equation}
with $\alpha = 0.999 \pm 0.001$ and $\beta = 2.23 \pm 0.009$. The cluster typical radius is thus calculated from the assumed $R_{\rm eff}$ and the adopted mass profile. Upon these assumptions an IMBH with mass $M_\ibh = 10^2(10^5)\Ms$ is associated with a cluster mass of $ M_\gc = 1.7\times 10^4(1.7\times 10^7)\Ms$, thus our models ideally span the mass range of young clusters, globular clusters, and dwarf galaxies nuclei. We assume that the IMBH is orbited by two stellar BHs, since the IMBH is expected to be the most massive object in the cluster and the dominant element in determining the dynamics. The orbital eccentricity $e_{1,2}$ is extracted randomly according to a thermal distribution $P(e){\rm d} e = 2e{\rm d}e$, while the semimajor axis $a_{1,2}$ is selected according to the overall cluster density profile with the exception of model S6, in which we extract $a_{1,2} = 0.1-10^4$ AU assuming a distribution flat in logarithmic values.  
In models S0 to S5, the maximum semimajor axis allowed is set equal to the radius within which the host cluster contains two stellar BHs with average mass $30\Ms$.

The BH mass spectrum is also allowed to vary: we use the BH mass spectrum derived by \citep[SM17][]{spera17}, assuming a progenitor metallicity of $Z = 0.0002$ for models S0, S1, S2, and S5 and $Z = 0.02$ for model S6; a power-law mass spectrum with slope $2.2$ \citep[O16][]{oleary16} in the range $3-30 \Ms$ (model S3); or a flat distribution in the range $3-30 \Ms$ (hereafter FLAT, model S4). The three different BH mass spectrum adopted describes two possible situations, one in which the BH population reflect the original population of stars and another in which dynamics operated a selection on the BH mass distribution either mild (power-law distribution) or sufficiently strong to erase any memory of the original mass function (flat distribution). 
}

\begin{table*}
\caption{Main properties of our models}
\begin{center}
\begin{tabular}{cccccccccccc}
\hline
\hline
ID & $M_\ibh$ & $M_\gc$ & $\rho_\gc$ & $\gamma_\gc$ & $a$ &$e$ &BH & $m_{\bh, min/max}$ & $Z$ & $N_{\rm sim}$ \\ 
   & $\Ms$    & $\Ms$   &            &              &     &    &   & $\Ms$              &     & \\
\hline
S0 & $10^2-10^5$ & $1.7\times 10^4 - 1.7\times 10^7$ & Dehnen & $0.5$ & density & thermal & SM17 & $4-53.4$ & 0.0002 & 1,000 $\times$ 4 \\
S1 & $10^2-10^5$ & $1.7\times 10^4 - 1.7\times 10^7$ & Dehnen & $1.0$ & density & thermal & SM17 & $4-53.4$ & 0.0002 & 1,000 $\times$ 4 \\
S2 & $10^2-10^5$ & $1.7\times 10^4 - 1.7\times 10^7$ & Plummer& $0.0$ & density & thermal & SM17 & $4-53.4$ & 0.0002 & 1,000 $\times$ 4 \\
S3 & $10^2-10^5$ & $1.7\times 10^4 - 1.7\times 10^7$ & Dehnen & $0.5$ & density & thermal & O+16 & $3-30$ & 0.0002 & 1,000 $\times$ 4 \\
S4 & $10^2-10^5$ & $1.7\times 10^4 - 1.7\times 10^7$ & Dehnen & $0.5$ & density & thermal & FLAT & $3-30$ & 0.0002 & 1,000 $\times$ 4 \\
S5 & $10^2-10^5$ & $1.7\times 10^4 - 1.7\times 10^7$ & Dehnen & $0.5$ & logflat & thermal & SM17 & $4-53.4$ & 0.0002 & 1,000 $\times$ 4 \\
S6 & $10^2-10^5$ & $1.7\times 10^4 - 1.7\times 10^7$ & Dehnen & $0.5$ & density & thermal & SM17 & $4-53.4$ & 0.02   & 1,000 $\times$ 4 \\
\hline
\end{tabular}
\label{tabt1}
\end{center}
\end{table*}

{\bf 
All simulations are performed taking advantage of \ARGdf \citep{ASCD19}, a modified version of the \ARCHAIN code that implements post-Newtonian (PN) dynamics and {\it algorithmic regularization} to handle close encounters and strong collisions \citep{mikkola99,mikkola08}. For our purposes, we include in our treatment only 1, 2, and 2.5 order PN terms. Additionally, \ARGdf allows the user to take into account in particles' equations of motion the gravitational field generated by the host stellary system and a dynamical friction term. Simulations are halted either if one of the two BH merge with the IMBH, if one of the BHs is ejected away if the simulated time exceeds $t = 1$ Gyr, or if the runtime exceeded 1 hr. The $1$ Gyr time limit serves to cope with the fact that IMBH in the range of masses $>10^3\Ms$ are expected to build-up via stellar accretion and mergers with compact remnants over timescales that can range considerably $1-10$ Gyr depending on the formation pathway \citep[see for instance][]{giersz15}. A summary of all models considered is provided in Table \ref{tabt1}.
}

\section{Results}
\label{res}

\subsection{IMRIs formation and merger}
\label{sec:imris}

\begin{figure*}
    \centering
    \includegraphics[width=16cm]{Sketch_IMRI}
    \caption{Schematic view of IMBH-BH-BH triple evolution.}
    \label{fig:f3}
\end{figure*}

\begin{table*}
\caption{Main results of $N$-body simulations}
\label{tab:mergers}
%\centering{}
\begin{center}
\begin{tabular}{c|cccc|cccc}
\hline
\hline
ID   & $f_{\rm bnd}$ & $f_{\rm dis}$ & $f_{\rm mer}$ & $f_{\rm mer,d}$ & \multicolumn{4}{c}{$f_{\rm mer,ibh}$} \\
     & $\%$          & $\%$          & $\%$         & $\%$          & \multicolumn{4}{c}{$\%$}\\
     &               &               &              &               &$10^2\Ms$&$10^3\Ms$&$10^4\Ms$&$10^5\Ms$\\
\hline
S$0$ & $25.73$ & $47.77$ & $26.50$ & $2.08$ & $3.1 $ & $28.6 $ & $51.6 $ & $30.9 $ \\ 
S$1$ & $21.88$ & $58.12$ & $20.00$ & $2.33$ & $3.5 $ & $28.5 $ & $38.7 $ & $18.6 $ \\ 
S$2$ & $39.17$ & $36.08$ & $24.75$ & $0.28$ & $0.0 $ & $11.7 $ & $43.6 $ & $44.8 $ \\ 
S$3$ & $28.68$ & $40.05$ & $31.27$ & $1.15$ & $5.5 $ & $48.6 $ & $43.6 $ & $31.7 $ \\ 
S$4$ & $26.70$ & $44.88$ & $28.43$ & $2.08$ & $3.4 $ & $38.8 $ & $49.0 $ & $30.8 $ \\ 
S$5$ & $40.48$ & $41.03$ & $17.70$ & $29.35$& $30.5 $ & $42.5 $ & $50.1 $ & $64.8 $ \\ 
S$6$ & $29.57$ & $37.80$ & $32.62$ & $1.43$ & $3.6 $ & $50.3 $ & $49.2 $ & $33.1 $ \\ 
\hline
\end{tabular}
\label{tab:t2}
\end{center}
\end{table*}

{\bf

In this section we discuss the main results of our simulations. In the following, we refer indifferently to IMBH-BH and IMRI although the smallest value of the IMBH mass adopted ($10^2\Ms$) leads to IMBH-BH mergers with a mass ratio larger than expected for IMRIs. We discuss the implication for GW astronomy in the next section.

The outcomes of our simulations can be classified in three main categories: 
\begin{itemize}
\item[a)] the IMBH-BH-BH system remains bound over the simulated time ({\it bound});
\item[b)] one of the stellar BHs is ejected away leaving behind an IMBH-BH binary ({\it disrupted}); 
\item[c)] one of the BH merges with the IMBH ({\it mergers}). 
\end{itemize}
Figure \ref{fig:f3} provides a simplistic sketch of the possible outcomes of our simulations. Table \ref{tab:t2} shows the percentage of models falling in each of these categories for the different models explored. On average, we note that mergers constitute the $f_{\rm GW} \sim 20-32\%$ of models, with little dependence on the initial conditions assumed. 
Models falling in category a) or b) do not exclude automatically an IMBH-BH merger. In case a), i.e. a bound IMBH-BH-BH, the triplet can arrange in a configuration in which the IMBH forms a tighter bound with one of the BHs while the other orbits around their common centre of mass. In this case, the triple can either evolve chaotically or undergo secular effects like the so called Kozai-Lidov mechanism \citep{kozai62,lidov62} that can trigger the eccentricity of the innermost IMBH-BH binary to grow to values close to unity.

In case b), i.e. ejection of one of the stellar BHs, the evolution of the remaining IMBH-BH binary will be due to the sum of two contributes, namely energy removal from binary-single interactions and GW emission. The first contribute compromise the IMBH-BH survival over a typical {\it evaporation time} \citep{bt,stephan16,hoang18} 
\begin{align}
t_{\rm ev} =& \frac{\sqrt{3}\sigma_g}{32\sqrt{\pi}G\rho_g\ln\Lambda a} \frac{m}{m_*} = \nonumber \\
            & 1.3\times 10^{10} {\rm ~yr} 
            \left(\frac{\sigma_g}{5{\rm ~km~s^{-1}}}\right)
            \left(\frac{10^5{\rm ~M}_\odot ~pc^{-3}}{\rho_g}\right) \times \nonumber \\
            & \times \left(\frac{0.1{\rm ~AU}}{a}\right)\left(\frac{1030{\rm ~M}_\odot}{M_{\rm ibh}+M_{\rm bh}}\right)\left(\frac{m_*}{30{\rm ~M}_\odot}\right),
\label{eva}
\end{align}
where $m_*$ is the average stellar mass in the nucleus, $\rho_g$ is the stellar density, $\sigma_g$ is the cluster velocity dispersion, and $\ln\Lambda=6.5$ is the Couloumb logarithm. If the IMBH-BH entered the IMRI phase, binary-single interactions are expected to play little to no effect on its evolution \citep{seoane18}. In this case, the IMRI will continuously shrink emitting GWs until coalescence, which takes place on a timescale \citep{peters64}
\begin{align}
t_\gw =&  \displaystyle \frac{5}{256}\frac{c^5 a_\inn^4 (1-e_\inn^2)^{7/2}}{G^3M_\ibh M_\bh(M_\ibh+M_\bh)} = \nonumber \\
       & 10^6{\rm ~yr}\left(\frac{a_\inn}{0.1\au}\right)^4\left(1-e_\inn^2\right)^{7/2}\times \nonumber \\ 
       & \times \left(\frac{10^3\Ms}{M_\ibh}\right) \left(\frac{30\Ms}{M_\bh}\right)\left(\frac{1030\Ms}{M_\ibh+M_\bh}\right).
\label{peters}
\end{align}
In principle, a binary having $t_\gw < t_{\rm ev}$ is most likely to merge before dynamical encounters manage to break it.
Therefore, as summarized in Table \ref{tab:t2}, among all models we calculate both the percentage of ``direct mergers'' $f_{\rm mer}$ -- mergers that happen before the simulations end -- and ``delayed mergers'' $f_{\rm mer,d}$ -- i.e. IMBH-BH binaries that satisfy the $t_\gw < t_{\rm ev}$ criterion. The amount of delayed mergers represents about $0.2-2.3\%$ of the simulated cases.

Clearly, while the categorization provided suggests three well separate classes, it must be noted that models falling in case c) (mergers) might have undergone a chaotic triple phase, or secular effects that triggered the IMBH-BH merger. In fact, figure \ref{fig:example} shows a typical example of one of the simulations performed in which the merger takes place within the simulated time. In the example, an IMBH with mass $M_\ibh = 10^2\Ms$ forms a tight binary with a stellar BH with mass $M_\bh = 15\Ms$, the binary is subjected to perturbation of the outer BH with mass $M_\bh = 5\Ms$ that causes a continuous oscillation of the eccentricity up to the point -- around 300 Myr from the beginning of the simulation -- at which the eccentricity peaks at values $\sim 0.999998$ and GW start dominating the IMBH-BH binary evolution which culminate with a merger shortly after.  
}
\begin{figure}
\includegraphics[width=\columnwidth]{example}
    \caption{Time evolution of the semimajor axis (straight blue line) and eccentricity (dotted red line) for one of the simulations performed in SET0.}
	\label{fig:example}
\end{figure}

{\bf

The amount of both ``direct'' and ``delayed'' merger depends, as outlined in Table \ref{tab:t2}, on the IMBH mass and the model investigated. Figure \ref{fig:gwprob} shows the percentage of total mergers (direct + delayed, hereafter $f_{\rm GW}$) as a function of the IMBH mass for different models. We see that the scatter among different models and for a fixed IMBH mass value is considerable, spanning from $f_{\rm GW} = 10\%$ (SET 2) to $50 \%$ (SET 6) for $M_\ibh = 10^3\Ms$. 
\begin{figure}
\includegraphics[width=\columnwidth]{mergerprob}
    \caption{IMRIs merger probability as a function of the IMBH mass for all models explored.}
	\label{fig:gwprob}
\end{figure}

While it is difficult to find a trend in the different models, in general our results suggest that the IMRI merger probability maximizes at IMBH masses $M_\ibh\sim 10^4\Ms$, while it is limited to a few percent in the case $M_{\ibh} = 100\Ms$. In the next section, we will exploit these results to infer the cosmological merger rate of IMRIs associated with different IMBH mass ranges and GW detectors.

Another important property that can be inferred from our models is the mass distribution ${\rm d}N/{\rm d}M_{\rm bh}$ of IMRI lighter companion, which is shown in Figure \ref{fig:f8} for models SET0-5 (different cluster density profiles and BH mass spectrum) and Figure \ref{fig:f8} for models SET0, 6 (different stellar metallicity). Comparing SET0, 1, and 3 -- which differ only in the cluster density profile but adopt the same BH mass spectrum \citep{spera17} -- it is apparent that the ${\rm d}N/{\rm d}M_{\rm bh}$ not depend on the environment, but rather on the BH mass spectrum adopted. In all three cases, the mass distribution shows a clearly bimodal distribution peaked at $\sim 7\Ms$ and $34\Ms$. The picture changes significantly if another BH mass spectrum is adopted. In the case of a power-law mass spectrum in the range $M_\bh = 3-30\Ms$ we find that ${\rm d}N/{\rm d}M_{\rm bh}$ declines sharply starting from $3\Ms$ and truncates at $> 25 \Ms$, whereas for a flat mass spectrum in the same range the trend turns out to be opposite, with the ${\rm d}N/{\rm d}M_{\rm bh}$ parameter increasing toward $25 \Ms$ and abruptly dropping beyond this value. Assuming smaller values for the initial semimajor axis (SET5) does not affect significantly the merging BH mass distribution, which in fact resembles that obtained for SET0-3. We explored whether the IMBH mass plays a role in shaping the merging BH mass distribution but, on average, we find that the overall distribution remains the same across all the range of $M_\ibh$ explored. As shown in Figure \ref{fig:mbhdist}, increasing the stellar metallicity to solar values (SET6) leads to IMRIs with a secondary component mass that remains below $25\Ms$.

These results have two main implications. On the one hand, the IMRI secondary mass tells us something about the mass spectrum of BHs lurking around an IMBH. On the other hand, it provides clues about the IMBH formation process. In fact, if the IMBH formed during cluster's early life, we can expect that the BH mass spectrum isn't altered substantially by dynamics. However, if the IMBH develops after dynamical encounters shaped the BH reservoir -- for instance by causing the ejection of the most massive BHs -- we would expect that the IMRI secondary mass would preferentially attains lower values.

\begin{figure*}
\centering
\includegraphics[width=0.8\textwidth]{massdis}\\
%\includegraphics[width=0.8\textwidth]{massdisD}\\
    \caption{%Top panel: 
    Mass distribution of the IMRI secondary for SET0 to 5. Each color corresponds to a different set to facilitate the comparison between different panels and figures. 
    %Bottom panel: the same as above, but differentiating for different IMBH masses: $10^2\Ms$ (straight line), $10^3\Ms$ (dashed line), $10^4\Ms$ (dashed dotted line), $10^5\Ms$ (dotted line) as indicated in the legend. Each color corresponds to a different set to facilitate the comparison between the upper and lower panels.
    }
	\label{fig:f8}
\end{figure*}

\begin{figure}
\includegraphics[width=\columnwidth]{massdis06}
    \caption{Mass distribution of the IMRI secondary for SET0 and SET6, which rely on the same set of assumption except for the initial metallicity: $Z = 0.0002$ (SET0), and $Z = 0.02$ (SET6).}
	\label{fig:mbhdist}
\end{figure}

The distribution of merger times $t_\gw$ seems to be independent on the set of adopted initial conditions. As suggested by Figure \ref{fig:f10}, which shows the cumulative $t_\gw$ for all models, around $50\%$ of mergers have $t_{\gw} < 10^6 - 10^7$ yr, with the exception of SET2 for which  $t_{\gw} \sim 10^8$ yr.

\begin{figure}
\includegraphics[width=\columnwidth]{time}
    \caption{Distribution of IMRI merging times calculated for all mergers in all the models explored. Different colors and symbols correspond to a different model SET as indicated in the legend.}
	\label{fig:f10a}
\end{figure}

}

\subsection{IMBH survival in dense star clusters}
{\bf
Promptly after a merger event, the anysotropic emission of GWs can impart a recoil kick to the merger product, depending on the mass and spin of the two merging objects \citep{campanelli07,gonzalez07,lousto08,lousto12}. Depending on the kick amplitude, the recoil can kick out the IMBH from the cluster \citep[e.g.][]{bockelmann08}, leading it to wander forever outside the cluster. In fact, for low-velocity dispersion ($5$ km/s) star clusters the probability to retain a BH with mass $m_\bh> 100 \Ms$ after 1-2 consecutive mergers is rather low, $1-5\%$ \citep{arca20}. To place constraints on the IMBH retention probability, we create a catalogue of IMRI mergers proceeding on a step-by-step basis as follows: 
\begin{enumerate}
\item we divide the IMBH mass range -- $M_\ibh = 10^2-5\times 10^5\Ms$ -- in 15 values evenly distributed in logarithmic values;
\item for each IMBH mass, we create a sample of 100 stellar BHs with masses evenly drawn in the $M_\bh = 3.5-80 \Ms$ range;
\item we associate to the IMBH and BH a spin randomly drawn between 0-1;
\item we use \cite{jimenez17} numerical relativity fitting formulae to calculate the IMRI merger remnant mass $M_r$, spin $S_r$, and recoil velocity $v_r$, following the procedure depicted in \cite{arca20}.
\end{enumerate}
For each $M_\ibh -m_\bh$ pair, we repeat steps 3 and 4 100 times and, for each of them, we compare the recoil velocity with the escape velocity from the cluster centre, which we set to $\sigma = 5$ or $50$ km/s.

The result of this procedure is described in Figure \ref{fig:f11}, which shows the percentage of models for which $v_r < \sigma$. In the case of 
a ''normal'' cluster ($\sigma = 5$ km/s), we find that an IMBH with mass $M_\ibh < 200 \Ms$ gets ejected whenever the merging companion has a mass $m_\bh \geq 10 \Ms$. Even for heavier IMBHs, e.g. $M_\ibh = 1000\Ms$, the retention probability rapidly drops below $50\%$  if the companion mass exceeds $M_\bh > 20\Ms$. Only for quite heavy IMBHs ($M_\ibh \sim 10^4\Ms$) the retention probability attains values $>80\%$ regardless the secondary BH mass. In the case of a denser cluster ($\sigma=50$ km/s), we find that a moderate IMBH ($M_\ibh \sim 200-300 \Ms$) have a $50\%$ retention probability if $m_\bh < 30\Ms$, while for $M_\ibh = 1000\Ms$ the BH mass threshold to ensure a $50\%$ retaining probability increases to $m_\bh = 70\Ms$.

Therefore, localizing an IMBH in the centre of a star cluster and measuring its mass would enable us to get insights on its evolution. For instance, the presence of an IMBH with mass $>10^3\Ms$, even in dense clusters, would suggest that the IMBH growth process might be dominated  by matter accretion from disrupted star rather than by mergers with BHs heavier than $30-50\Ms$.
}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{survival}
\includegraphics[width=\columnwidth]{survival50}
\caption{Top panel: IMBH retention probability as a function of the merging BH mass for different values of the IMBH mass, identified by the color-coding, assuming for the star cluster an escape velocity of $\sigma = 5$ km/s. Bottom panel: same as above, but for an escape velocity of $\sigma = 50$ km/s.}
\label{fig:survival}
\end{figure}

\subsection{IMBHs spin evolution}
{\bf 
Since an IMBH-BH merger cause an inevitable variation of the IMBH spin, this quantity might be useful to get insights on the IMBH evolution.
To support this idea, we create a sample of IMBH-BH mergers as follows. We select an IMBH with mass of either $M_\ibh = 10^2 - 10^3 - 10^4 - 10^5$ and spin $S_\ibh = 0.1 - 0.5 - 0.9$ and we merge it with a stellar BH with mass in the range $3 - 60 \Ms$ drawn randomly and spin drawn accordingly to a Gaussian distribution with mean $S_\bh = 0.7$ -- i.e. the average value inferred from LIGO O1+O2 observations -- and dispersion 0.1.

Figure \ref{fig:f11a} shows the value of the remnant IMBH spin as a function of the IMRI mass ratio.

We see that as long as the mass ratio remains below $10^{-2}$ -- which implies an $M_\ibh > 10^4 \Ms$ -- the IMBH spin is not affected by the merger. However, for IMRIs with a mass ratio > 0.01, the remnant IMBH spin can change significantly. For mass ratios in the range $q = 0.01-0.1$ the spin variation is $\sim \pm 0.1$ with respect to the initial value, whereas at larger mass ratio values we see that the spin tend to move toward values close to the average value assumed for the BH spin distribution, being the remnant spin $S_r \sim 0.8\pm 0.2$.
The peculiar dependence between the remnant spin and the IMRI mass ratio has important consequences for the IMBH evolution. One the one hand, if the IMBH formed from the collapse of a gaseous cloud or a very massive star born out of stellar collisions and reach masses $\gtrsim 10^4\Ms$, measuring its spin in a IMRI merger would provide us with information on the processes that regulated the IMBH very formation. On the other hand,
if the IMBH formed via multiple mergers in a stellar environment rich in BHs, the remnant spin can provide clues on the spin distribution of the underlying population of stellar BHs.

To further investigate this point, we explore the effects of a series of subsequent mergers on the IMBH final spin in the case of 
an IMBH mass value  that ensure a retention probability of at least $50\%$ in an IMRI merger event involving a BH smaller than $40\Ms$.
From Figure \ref{fig:survival} and Figure\ref{fig:f11a} we thus select $M_\ibh = 10^3\Ms$, which satisfies the requirement above, and set its spin to either $S_\ibh = 0.1-0.5-0.9$. For each spin value, we model ten consecutive mergers with stellar BHs with masses $3-60\Ms$ and spin drawn from a Gaussian distribution with average $S_\bh = 0.5$ and dispersion 0.1. This sequence represents an {\it IMBH merger tree}. For each value of the spin we create 100 merger trees and calculate the IMBH spin evolution as shown in Figure \ref{fig:f11b}.
We note that all models tend to converge toward the mean value of the adopted spin distribution for stellar BHs, thus suggesting that it could be possible to link the IMBH spin with the overall spin distribution of stellar BHs inhabiting the star cluster. Infact, complementing a measure of the IMBH spin with the spin distribution inferred from stellar BH mergers observed as GW sources can help in unravelling the IMBH evolution, whether it was driven by mergers with compact objects or by stellar feeding.
}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{track}
\caption{Spin of the IMBH after one merger with a stellar BH as a function of the mass ratio. Different colors identify different values of the IMBH.}
\label{fig:f11a}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{track1000}
\caption{Spin evolution for an IMBH with initial mass $M_\ibh = 10^3\Ms$ and initial spin either $a_0 = 0.1$, $0.5$, or $0.9$ that undergoes 10 consecutive mergers with stellar mass BHs. For each value of $a_0$ we run 100 different merger trees, each shown in the plot
as connected by a thin black line. The colour-coding marks the effective spin parameter calculated at each IMBH-BH merger. The labels  show the initial value of the IMBH spin adopted, and the average value of the spin after the 10th merger. }
\label{fig:f11b}
\end{figure}

\section{Gravitational waves}
\label{gra}

\subsection{Gravitational wave signal}
{\bf
Our simulations encompass a wide range of IMRI models, in fact touching the layer of ``ordinary'' BH binaries (mass ratio $q>0.1$) and 
scratching the limit of extreme-mass ratio inspirals ($q < 3 \times10^{-5}$). This setup implies that the GW emission connected with our modelled mergers can populate a wide range of frequencies, from milli- to deca-Hz. Figure \ref{fig:f13} show the characteristic amplitude as a function of the frequency for a sample of IMRI mergers with different IMBH mass, assuming they are located at redshift $z=0.1$ ($\sim 460$ Mpc) and an observation time of 4 yr. We compare the modelled signal with the sensitivity curve of several detectors, namely LISA, ALIA, DO, DECIGO, LIGO, and the Einstein Telescope (ET). We see that mergers involving IMBHs with masses $< 10^5\Ms$ are promising multiband sources that can be seen in one detector during the inspiral phase and in another during the merger. The number of regions in which a detector is sensitive traversed by an IMRI widens at increasing the IMBH mass, in fact in principle an IMBH with mass $<10^3\Ms$ can be seen across the whole milli-decaHz frequency range.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{test}
\caption{Characteristic strain - frequency evolution for a sample of mergers in SET0. Each point in the plane refers to the signal associated with the IMRI dominant frequency. Different colors identify different IMBH mass ($M_\ibh$). The calculated signal is overlayed to the sensitivity curve of several detectors, from lower to higher frequency: LISA and LIGO (straight black line), DECIGO and Einstein Telescope (dashed black line), ALIA and Decihertz Observatory (dotted black lines).}
\label{fig:f13}
\end{figure}

}

\subsection{Eccentricity of IMRIs}
{\bf
One important parameter that could be inferred from GW observations is the eccentricity of the source. To better understand whether our IMRI models are expected to retain a significant eccentricity while transiting across different observational bands, we show in Figure \ref{fig:f10} the average value of the eccentricity calculated when IMRIs cross the milli-Hz, deci-Hz, and Hz bands for all simulations set. It is apparent that even when emitting low-frequency GWs, IMRIs have already significantly circularized, although apparently lower-mass IMRIs tend to have slightly larger eccentricities. The fact that our IMRIs are substantially circular when becoming observable to GW detectors has implications on their detectability, as we show in the next section.
}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{averageec}
\caption{Average eccentricity of IMRIs emitting in millihertz (top panel), decihertz (central panel), and Hertz (bottom panel). Different colors and symbols identify different models. }
\label{fig:f10}
\end{figure}

\subsection{Detecting IMBHs in Milky Way globular clusters and in the Large Magellanic Cloud}

In this section, we exploit our results to investigate whether the current design of LISA provide enough sensitivity to unveil the presence of IMBHs in our closest neighbourhood. 
To perform such a study, we assume to have a nearly circular IMRI with an IMBH mass in the range $10^2-10^6\Ms$ and a BH companion weighing either $10$ or $30\Ms$. 
We assume that the IMRI emission frequency is 1 mHz, corresponding to an orbital semimajor axis $10^{-3}-10^{-2}$ AU. 
The merger time for IMRIs in this configuration ranges between $100$ and $10^4$ yr, thus much larger than the observation time. Assuming 4 yr observation time, the IMRI frequency will not vary sensibly, being the frequency variation $\Delta \ln f < 10^{-4}$. As noted by \cite{robson19}, whenever the latter quantity remains below 0.5, a GW source should be treated as nearly stationary. Upon this assumption, the signal-to-noise (SNR) ratio can be written as
\begin{equation}
    {\rm SNR}^2 = h_{\rm GB}^2 f / h_n,
\end{equation}
where $f$ is the source initial frequency, $h_n$ is the adimensional instrument sensitivity, and 
\begin{equation*}
    h_{\rm GB} = \frac{8T_{\rm obs}^{1/2} (G\mathcal{M}/c^3)^{5/3} (\pi f)^{2/3}}{\sqrt{5}D_L/c},
\end{equation*}
with $T_{\rm obs}$ the observation time, $\mathcal{M}$ the IMRI chirp mass, and $D_L$ the luminosity distance. Note that the relation above implies that the SNR scales with $D_L^{-1/2}$.
Figure \ref{SNRMW} shows the SNR calculated for the LISA instrument for IMRIs having an initial frequency $f=1$ mHz and masses in the $10^2-10^6 \Ms$ range, assuming a luminosity distance of $D_L = 8$ kpc. 
We find that an IMRI with mass $M_\imri = (30 + 10^3)\Ms$ has an associated SNR of 20, whereas this quantity rises up to 100 for a $10^4\Ms$ IMBH. 
These estimates suggest that LISA can play a crucial role in probing the existence of IMBHs in the Galactic backyard. 
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{snr_MW}
    \caption{SNR for several IMRIs assuming an initial frequency of $1$ mHz, 4 yr of observation time, and a luminosity distance of $D_L = 8$ kpc.}
    \label{SNRMW}
\end{figure}

{\bf In fact, in the last decade a number of works pointed out the potential presence of IMBHs in Galactic globular clusters, although in most cases the results were inconclusive. Concerning clusters orbiting closer than 8 kpc to us candidates include: 47Tuc \citep{kiziltan17}, NGC6266 \citep{abbate19}, NGC6128 and NGC288 \citep{sollima16}, NGC6388 and NGC2808 \citep{miocchi07,lanzoni07}.
For instance, the inferred value for the 47Tuc IMBH mass goes from $M_\ibh > 2,000\Ms$ \citep{kiziltan17} to substantially lower values $\ll 1,000\Ms$ \citep{abbate19b}, depending on the observational technique adopted. A similar discussion involves other clusters, like NGC6388 \citep{lanzoni13,lutzgendorf13}. Therefore, LISA might play a crucial role in unravelling the presence (or not) of IMBHs in the Galaxy, at least the closest one.

Not only, in fact LISA can also be used to provide clues about the presence of IMBHs in nearby galaxies. For instance, it has been recently suggested that the Large Magellanic Cloud might be harbouring an IMBH with a mass in the range $4\times 10^3-10^4\Ms$ \citep{erkal19} and up to $10^7\Ms$ \citep{boyce17}, and that some of the clusters residing in the cloud can host IMBHs as well with masses in the range $10^3-10^4\Ms$ \citep{gualandris07}. Assuming a distance to the LMC $D_L = 49.97 \pm 1.13$ kpc \citep{pietrzy13}, we find that LISA might deliver observations of {\it Magellanic} IMRIs with an $SNR = 8-40$, with the lower(upper) value corresponding to an IMBH with mass $10^3\Ms$($10^4\Ms$) and a BH companion of $30\Ms$. 
}

\subsection{IMRIs merger rate}
%{\color{red} TO BE REVISED EVERYTHING BELOW!\\
%In particular, the discussion about the MW needs to be completely reshaped because the power-law approximation is no longer valid. We could use 
%an approximate stuff like 35./180. GCs might have an IMBH with mass 1,000 thus probability for IMRI is X, thus the probability for the MW is tot, thus
%the probability for MW analogs is tot, something like this could be ok-ish.
%}
%
%Previous studies based on full consistent N-body simulations of star clusters containing IMBHs with various masses and general properties  \citep{konstantinidis13,haster16,leigh14, macleod16} have shown that binary formation involving an IMBH takes place at a rate of $R_{\rm bin} \sim 10^{-7}$ yr. Assuming typical ages for globular-like star clusters of $t_{\rm age}\sim 10^{10}$ yr and assuming that IMBH buildup occurs in the clusters early lifetime ($\lesssim 1$ Gyr), we can use the merger probability fitting function depicted in Equation \ref{fmerg} to infer the total number of IMRIs formed for a given IMBH mass and over a cluster lifetime $t_{\rm age}$
%\begin{equation}
%    N_\gc(M_\ibh) = R_{\rm bin}t_{\rm age}f_{\rm mer} \sim 15\left(\frac{M_{\ibh}}{10^2\Ms}\right)^{0.38},
%\end{equation}
%ranging from $\Gamma_{\imri} = 15-90$ yr$^{-1}$ for $M_\ibh = 10^2-10^4\Ms$, respectively.
%To put such a quantity in the context of MW-like galaxies, we need to make assumptions on the IMBH putative mass function. Assuming that the initial mass function of GCs follows a power-law and exploiting Equation \ref{mcmibh}, we can write the IMBH mass function as $f(M_\ibh) = k (M_\ibh/10^\alpha)^{1/\beta}$. The normalization constant $k$ can be calculated by assuming that the mass in clusters constitute a fraction of the total galaxy mass:
%\begin{equation}
%k = \frac{\delta M_g (2-s)}{(M_{\gc 2}^{2-s} - M_{\gc 1}^{2-s})},
%\label{normal}
%\end{equation}
%with $\delta = 5\times 10^{-4}$ \citep{webb15,belczinski17}, $M_g = 6\times 10^{10}\Ms$ the Milky Way stellar mass, and $M_{\gc 1,2} = (5\times 10^3 - 8\times 10^6)\Ms$ the range of GC initial mass. 
%Combining equations above, we can infer the total number of IMRIs  MW-like galaxies as
%\begin{align}
%    N_{\rm MW} =& f_\ibh N_\gc \int_{M_{\ibh ,1}}^{M_{\ibh ,2}} \Gamma(M_\ibh) \times \nonumber \\
%    & \times f(M_\ibh) \frac{\derd M_\gc}{\derd M_\ibh} {\rm d}M_\ibh,
%\end{align}
%where $f_\ibh N_\gc$ is the number of GCs containing an IMBH, and the term $\derd M_\gc / \derd M_\ibh$ is used to perform a change of variable from the GC to the IMBH mass. The integral has analytical solution in the form
%\begin{equation}
%N_{\rm MW} = K \frac{M_{\ibh ,2}^{\beta + b(1-s)} - M_{\ibh ,1}^{\beta + b(1-s)}}{\beta + b(1-s)},
%\end{equation}
%with the parameter $K$ containing all the constant factors.
%Assuming $t_{\rm age} = 10$ Gyr and in the IMBH mass range of $10^2 - 10^4\Ms$, we derive an IMRI merger rates for MW-like galaxies of
%\begin{equation}
%\Gamma_{\rm MW} = 2.26\times 10^{-5} {\rm ~yr} \left(\frac{10{\rm ~Gyr}}{t_{\rm age}}\right)\left(\frac{f_\ibh}{0.2}\right)\left(\frac{N_\gc}{180}\right).
%\label{eqMW}
%\end{equation}
%The number of MW-analogs in the local Universe (redshift $z<0.1$) is roughly proportional to the luminosity distance $D_L$, namely $P_{\rm MW} = 4\pi/3 \times 0.0116(2.26)^{-3}D_L^3$ with $D_L$ expressed in Mpc \citep{abadie10}. Thus a rough estimate of potential IMRIs developing in MW-like galaxies in the local Universe is given by $\Gamma_{\rm MW} \times P_{\rm MW} = 10.5$ yr$^{-1}$.
%This is a simple estimate, though, which not account for the distribution of galaxies across different redshift or the actual volume within which a detector is sensitive.

The launch of the LISA detector and the start of operations of the next generation of GW observatories like the Einstein Telescope (ET) will enable us to observe this kind of objects at cosmological distances. Therefore, to infer the IMRI merger rates, we need to take into account in our calculation how the number density of galaxies varies across redshift $z$.
The GW source {\it horizon} determines the maximum distance in space, or the redshift $z_{\rm hor}$, at which the source signal is detected with a threshold signal-to-noise ratio (SNR), namely:
\begin{equation}
{\rm SNR^2} = \int_{f_1}^{f_2} \displaystyle{\frac{h_c^2(f,z_{\rm hor})}{S_n^2(f)}} {\rm d}f,
\end{equation}
with $f_{1,2}$ the initial and final frequency of the GW signal, $h_c(f,z)$ its characteristic strain, and $S_n(f)$ its sensitivity. To determine this quantity, we integrate the final stage of the IMRI signal assuming an observation time of 4 yr -- i.e. the nominal duration time of the LISA mission -- and we calculate the value of $z_{\rm hor}$ at which we get an SNR of 15. We assume the set of cosmological parameters measured by the Planck mission, namely $H_0 = 67.74$ km/s/Mpc$^{3}$, $\Omega_m = 0.3089$, $\Omega_\Lambda = 0.6911$ \citep{planck15}. To calculate $z_{\rm hor}$, we vary the IMBH mass in the range $50-10^6\Ms$ assuming that the companion has a mass of either $10$ or $30\Ms$. Figure \ref{fig:fhor} shows how the horizon redshift changes for four different detectors: the Laser Interferometer Space Antenna \citep[LISA\footnote{\url{https://www.elisascience.org/}},][]{amaro12}, the Deciherz Gravitational-Wave Observatory \citep[DECIGO\footnote{\url{http://tamago.mtk.nao.ac.jp/spacetime/decigo_e.html}},][]{seto01}, the Einstein Telescope \citep[ET\footnote{\url{http://www.et-gw.eu/}},][]{punturo10}, and LIGO.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{horizon}
\caption{Horizon redshift as a function of the IMBH mass assuming a BH companion with mass $10 \Ms$ (lower curves) or $30\Ms$ (upper curves). Different curve collections correspond to different detectors: LISA (straight lines), DECIGO (dashed lines), ET (dotted lines), LIGO (dot-dashed lines). In the next section, we discuss whether some classes of IMRIs can appear as multiband sources}.
\label{fig:fhor}
\end{figure}

From the plot is evident that ground based telescopes provide a relatively limited view on the IMBH realm, although LIGO can provide insights on low-mass IMRIs ($<500\Ms$) up to redshift $z_{\rm hor} \leq 0.2$ and ET will enable the observation of IMRIs with mass $<10^3\Ms$ up to $z_{\rm hor} = 1-10$, the same range of redshift accessible with LISA to listen GWs from heavy IMRIs ($M_{\imri}>10^4\Ms$). Decihertz observatories like DECIGO \citep{Kawamura11} and similarly designed mission \citep{arca19}, instead, will allow the detection of IMRIs in the whole $50-10^6\Ms$ mass range up to the dawn of the Universe, thus constituting ideal detectors to unveil the truly nature of IMBHs.

Once that the dependence between the horizon redshift and the IMBH mass is determined, we can infer the IMRIs rate by calculating the total number of IMRIs inside the cosmological volume encompassed by $z_{\rm hor}$, a requirement that can be expressed as:
\begin{align}
\Gamma_{\imri} = & \Omega_s \int_{M_{1}}^{M_{2}} \int_{0}^{z_{\rm hor}} \frac{\derd n_{\imri}}{\derd M_\ibh\derd z} \times \nonumber \\
& \times \frac{\derd V_c}{\derd z}  \frac{\derd z}{1+z} \derd M_\ibh,
\end{align}
being $\derd V_c/\derd z$ the comoving cosmological volume element, $(1+z)^{-1}$ the term that account for the dilation time, and $\derd n_{\imri}/\derd M_\ibh$ the number of IMRIs per unit of IMBH mass. We can write the latter quantity as
\begin{align}
\frac{\derd n_{\imri}}{\derd M_\ibh} =& \xi_\bh f_{\gw} p_\ibh n_{\rm rep}\times \nonumber \\
& \times \frac{\derd n}{\derd M_g\derd z}\frac{\derd n_\gc}{\derd M_\gc}\frac{\derd M_\gc}{\derd M_\ibh}.
\end{align}
Here, $\xi_\bh$ represents the probability for the IMBH to form a binary with a stellar BH, $\derd n/(\derd M_g \derd z)$ represents the number of galaxies per unit of redshift and galaxy mass, $\derd n/\derd M_\gc$ is the number of clusters per cluster mass in a given galaxy, $\derd M_\gc/\derd M_\ibh$ connects GCs and IMBHs, $n_{\rm rep}$ is the number of times that the same IMBH can form an IMRI with a stellar companion, $f_{\gw}$ is the fraction of IMRIs that undergo merger within a Hubble time (a quantity that is extracted from our simulations, see Figure \ref{fig:gwprob}), and $p_\ibh$ represents the probability for a cluster to host an IMBH. In the following, we assume $p_\ibh = 0.2$ \citep{giersz15}.

The term $\derd M_\gc / \derd M_\ibh$ can be calculated by inverting Equation \ref{mcmibh} and performing the derivative. For the number distribution of the GCs mass in a given galaxy, $\derd n/\derd M_\gc$, we assume a power-law
\begin{equation}
\frac{\derd n}{\derd M_\gc} = k M_\gc^{-s},
\end{equation}
with the slope $s = 2.2$ and the normalization constant 
\begin{equation*}
k = \frac{\delta M_g (2-s)}{(M_{\gc 2}^{2-s} - M_{\gc 1}^{2-s})}.
\end{equation*}
Assuming Galactic values for the galaxy stellar mass, $M_g = 6\times 10^{10}\Ms$, and star clusters mass range, $M_{\gc 1,2} = (5\times 10^3 - 8\times 10^6) \Ms$, we calculate the corresponding IMBH mass range $M_\ibh \simeq (30 - 4.6\times 10^4)\Ms$ according to Equation \ref{mcmibh}, which can also be used to write $M_\gc^{-s} = aM_\ibh^{-bs}$\footnote{The parameters $a,b$ are obtained manipulating Equation \ref{mcmibh}.}. The $\derd n/(\derd M_g\derd z)$ is obtained exploiting the results in \cite{conselice16}, who studied the distribution of galaxies with stellar masses up to $10^{12}\Ms$ up to redshift $z=8$. In particular, we exploit the following parametric expression of galaxies number density 
\begin{equation}
\phi(z) = -\frac{\phi_* 10^{(\alpha_* + 1)(M_2-M_*)}}{\alpha_* + 1},
\end{equation}
with $\phi_*,~\alpha_*,~M_*$ depending on the redshift \citep[see Table 1 in][]{conselice16}, and $M_2 = 12$.

Substituting all the terms and manipulating them conveniently, the total number of IMRI in the portion of Universe accessible to a given detector is thus given by
\begin{align}
N_{\imri,1} = & k a^{1-s} b p_\ibh n_{\rm rep} \xi_\bh \times \nonumber \\
& \times \int_{M_{1}}^{M_{2}} \int_0^{z_{hor}} f_{\gw} M_\ibh^{(1-s)b-1}  \derd M_\ibh \times \nonumber \\
& \times   \frac{\phi(z)}{1+z} \frac{\derd V_c}{\derd z}\derd z .
\label{eq:nimri1}
\end{align}

Observations and models suggest that GCs formation peaks at redshift $z=2$, corresponding to a formation time of $t_{\gc ,f} = 3.285$ Gyr. This would imply that the maximum redshift at which a GC containing an IMBH can be observed is the minimum between the horizon redshift and the GC formation redshift. Even in the case in which we assume that GCs forms continuously, we need to set a maximum redshift above which stars did not form yet. Thus, we capped the horizon redshift with either $z=2$ (peak of GC formation), or $z=6$ (formation of the first stars).

The parameter $\xi_\bh$ represents the probability that the IMBH is in a tight binary with a compact remnant. In a typical ensemble of stars with masses following a \cite{kroupa01} initial mass function, the number of stellar BH progenitors is a fraction $\sim 10^{-3}$ of the whole population. In absence of mass segregation and a mass spectrum, we might expect that the probability for an IMBH to be paired with a BH should simply be $10^{-3}$. However, in real systems mass-segregated stellar BHs tend to prevent other stars to migrate into the innermost cluster regions and thus they inhibit the IMBH to capture other stellar types. The direct implication of the dominant effect of stellar BHs on dynamics of the central cluster regions is a high probability for the IMBH to engage a long-term relationship with a stellar BH rather than with a star, thus suggesting $\xi_\bh \rightarrow 1$.

The time over which these IMRI forms can be estimated as the sum of the cluster formation time, the IMBH formation time, the IMRIs formation time, and the IMRI merger timescale:
\begin{equation}
T = t_{\gc ,f} + t_{\ibh ,f} + t_{\imri, f} + t_{\rm GW}. 
\end{equation}
The physics that regulate IMBH formation is still debated and partly unknown. Depending on the formation scenario, models suggest that the IMBH growth can occur either on short ($\sim 1$ Gyr) or long ($\simeq 5-10$ Gyr) timescales. As discussed recently, {\it fast} IMBHs could outnumber those forming slowly \citep{giersz15,AAG19}, thus in our calculations we assume $t_{\ibh ,f} = 2$ Gyr. 
The formation of an IMRI scales with the mass-segregation timescale in the host cluster, which is expected to be of the order of $\sim 0.1-1$ Gyr, while for $t_\gw$ we calculate, from our models, the value at which the number of mergers is half the total number, i.e. $N_\gw(t_\gw) = 0.5 N_\gw$. This corresponds to $t_\gw = 0.6-1.5$ Gyr.

An alternative way, yet similar, to calculate the merger rate is by exploiting the cosmological GC star formation rate $\rho_{\rm SFR}(z)$, which can be used to calculate the total number of GCs at a given redshift
\begin{equation}
N(z_{\rm max}) =  \int_0^{z_{\rm max}} \frac{\rho_{\rm SFR}(z)}{<M_\gc>}\frac{\derd V_c}{\derd z}\frac{\derd z}{1+z}.
\end{equation} 
Given the power-law GCs mass function used in the previous method, the normalization factor in this case become
\begin{align}
k  =&\frac{(1-s)}{M_{\gc, 1}^{1-s} - M_{\gc ,2}^{1-s}},
\end{align}
and the total number of IMRI inside a given cosmological volume is thus given by
\begin{align}
N_{\imri, 2} = & k a^{1-s} b p_\ibh n_{\rm rep} \int_{M_{1}}^{M_{2}} \int_0^{z_{hor}} M_\ibh^{(1-s)b-1} \times \nonumber \\
& f_{\gw}  \rho_{\rm SFR}(z)\frac{\derd V_c}{\derd z} \frac{\derd z}{1+z} \derd M_\ibh.
\label{eq:nimri2}
\end{align}

We can convert the number of IMRIs in Eqs. \ref{eq:nimri1} - \ref{eq:nimri2} within a given redshift into a merger rate via $\Gamma_\imri = N_\imri / T$. Table \ref{tab:5} summarizes the prospective merger rate calculated for different instruments in units of event per yr.

Assuming a 4 yr long observation run, our estimates suggest that LIGO might be able to detect up to $1-5$ observations of low-mass IMRIs with an IMBH with mass $M_\ibh \simeq 100\Ms$. So far, the three observation runs accomplished by the LIGO-Virgo-Kagra collaboration (LVK), which covers a $\sim 2$ yr time span, seem not to contain such a massive BH, although the loot of detections cumulated during the last run (O3) -- which led to the discovery of around $\sim 60$ new candidates\footnote{\url{https://gracedb.ligo.org/}} -- has not been fully disclosed yet.

At lower frequencies, LISA might record up to $\sim 6-60$ events per yr, pushing the limit for the IMBH mass to up to $40,000\Ms$ and thus allowing to explore the mass range typical of IMRIs $q \simeq 10^{-4}$.

While the constraints on "present-day" technologies are already quite encouraging, the next generation of both ground- and spaced-observatories could enable us to deliver a much larger amount of observations up to the maximum redshift allowed ($z=2-6$), thus allowning us to probe IMBHs all the way from formation to full growth.

For instance, ET could detected up to $100-800$ IMRIs per yr with masses $M_\imri < 2,000 \Ms$, while space observatories sensitive at decihertz frequencies like DECIGO might record up to $3800$ events per yr.

\begin{table*}
\caption{IMRI merger rate for different detectors }
\begin{center}
\begin{tabular}{cccccccc}
\hline
Instrument & $M_{\rm SBH}$ & $z_{\rm max}$ & $M_{\ibh ,1}$ & $M_{\ibh ,2}$ & $T$ & $\Gamma_1$ & $\Gamma_2$ \\
   & $\Ms$ & &$\Ms$ & $\Ms$ & Gyr & yr$^{-1}$ & yr$^{-1}$ \\ 
\hline
LIGO & $10$ & $0.38$ & $29$ & $200$ & $8$ & $0.81$ &$0.89$ \\
LIGO & $10$ & $0.38$ & $29$ & $200$ & $8$ & $0.81$ &$0.89$ \\
LIGO & $30$ & $0.57$ & $29$ & $200$ & $8$ & $1.89$ &$2.50$ \\
LIGO & $30$ & $0.57$ & $29$ & $200$ & $8$ & $1.89$ &$2.50$ \\
LISA & $10$ & $0.70$ & $29$ & $46240$ & $8$ & $6.01$ &$7.74$ \\
LISA & $10$ & $0.70$ & $29$ & $46240$ & $8$ & $6.01$ &$7.74$ \\
LISA & $30$ & $1.78$ & $29$ & $46240$ & $8$ & $66.40$ &$59.09$ \\
LISA & $30$ & $1.78$ & $29$ & $46240$ & $8$ & $66.40$ &$59.09$ \\
ET & $10$ & $2.00$ & $29$ & $2000$ & $8$ & $140.66$ &$109.04$ \\
ET & $10$ & $6.00$ & $29$ & $2000$ & $8$ & $564.60$ &$215.66$ \\
ET & $30$ & $2.00$ & $29$ & $2000$ & $8$ & $190.53$ &$144.74$ \\
ET & $30$ & $6.00$ & $29$ & $2000$ & $8$ & $812.52$ &$298.68$ \\
DECIGO & $10$ & $2.00$ & $29$ & $46240$ & $8$ & $635.03$ &$486.93$ \\
DECIGO & $10$ & $6.00$ & $29$ & $46240$ & $8$ & $3828.50$ &$1506.62$ \\
DECIGO & $30$ & $2.00$ & $29$ & $46240$ & $8$ & $635.03$ &$486.93$ \\
DECIGO & $30$ & $6.00$ & $29$ & $46240$ & $8$ & $3828.50$ &$1506.62$ \\
\hline
\label{tab:5}
\end{tabular}
\end{center}
\end{table*}

\section{Conclusions}

In this work we studied the dynamical interaction of an IMBH with two stellar BHs under the assumption
that these three massive object dominate completely the dynamics in the innermost regions of a massive star cluster.
We used $28,000$ direct $N$-body models aimed at exploring the formation and evolution of IMRIs, which in this paper we 
broadly define as tight binaries involving an IMBH with mass $> 100 \Ms$ and a stellar BH with mass $\lesssim 50 \Ms$.
In order to assess the role of environments and dynamics on IMRIs formation, we vary the density and metallicity of the 
host cluster, the IMBH mass, the mass spectrum of stellar BHs, and the orbital properties of the three objects.

Our main results can be summarized as follows:
\begin{itemize}
\item we find that the chaotic interaction between the two BHs and the IMBH favours the formation and merger of IMRIs in a non-negligible fraction of cases. In general, one BH tends to form a more bound binary with the IMBH while the other BH perturbs such a binary. These perturbations are chaotic but can drive the IMBH-BH eccentricity to rise sufficiently for GW emission to kick in, leading to the swift formation
of a merging IMRI [Figure \ref{fig:example}];
\item the merger probability $f_\gw$ increases with the IMBH mass ($M_\ibh$), although in a non trivial way. ``Small'' IMBHs, with mass $M_\ibh \sim 100 \Ms$, have an associated $f_\gw = 5-20\%$ whereas IMRI formation and merger is more frequent for heavier IMBHs, being $f_\gw = 10-60\%$. The large scatter depends mostly on the star cluster density profile and the orbital properties of the IMBH-BH-BH triplet [Figure \ref{fig:gwprob}];
\item our models suggest that the IMRI secondary maps out the overal BH mass distribution. Therefore, the observation of IMRIs would enable us to place constraints on the population of BHs inhabiting the centre of massive star clusters [Figure \ref{fig:mbhdist}];
\item assuming typical values of the cluster velocity dispersion, $\sigma = 5$ km/s for Galactic globular clusters, we show that IMBHs heavier than $M_\ibh \simeq 10^3\Ms$ have $>50\%$ probability to be retained in the cluster after a merger if the companion mass is $<20-30 \Ms$. Lighter IMBHs ($M_\ibh \leq 200\Ms$) are ejected from the cluster whenever the IMRI secondary mass exceeds $10\Ms$. This suggests that an IMBH heavier than $200\Ms$ lurking in the centre of a star cluster has grown more likely via stellar consumption, rather than trhough GW mergers [Figure \ref{fig:survival}];
\item the IMBH spin is another parameter that encodes information about the IMBH evolution. At $M_\ibh>10^4\Ms$, a merger event won't change the IMBH spin, whereas the remnant spin changes significantly if $M_\ibh\simeq10^2-10^3\Ms$. This implies that measuring the IMBH spin prior and after an IMRI can shed a light on the spin distribution of stellar BHs and on the processes that drove the IMBH build-up [Figures \ref{fig:f11a}-\ref{fig:11b}];
\item LISA can help to unravel the presence of IMBHs in our neighbourhood. Assuming a 4 yr long mission, we suggest that LISA can identify IMRIs involving $M_\ibh \sim 10^3-10^4\Ms$ in Galactic GCs, with a signal-to-noise ratio SNR$=10-100$, and in the centre of the Large Magellanic Cloud, where we infer SNR$=8-40$;
\item IMRIs are multiband sources that can be observed with several GW detectors. Assuming 4 yr of observations, we calculate that within the corresponding horizon redshift LIGO can detect up to $0.9-2.5$ events per yr involving an IMBH with mass $M_\ibh \lesssim 200\Ms$. Such a kind of event might have been already recorded during the O3 observation run. LISA has the chance of detecting $6-60$ events yr$^{-1}$ involving $M_\ibh < 46,000\Ms$, whereas the Einstein Telescope ($\sim 10^3$ events yr$^{-1}$ for $M_\ibh < 2000\Ms$) and DECIGO ($\sim 400-3800$ events yr$^{-1}$ for $M_\ibh < 50,000\Ms$) will boost signicantly IMRIs detections, shedding a light on the processes that regulate IMBH seeding and growth at cosmic scales.
\end{itemize}

\clearpage

\section*{Acknowledgements}

MAS acknowledges the Alexander von Humboldt Foundation for the financial
support provided in the framework of the research program "The evolution of
black holes from stellar to galactic scales", and the Sonderforschungsbereich
SFB 881 "The Milky Way System"  -- Project-ID 138713538 -- funded by the German
Research Foundation (DFG).  PAS is indebted with the THAT Group at DESY Zeuthen
for an extended visit, where this work was finished. PAS acknowledges support
from the Ram{\'o}n y Cajal Programme of the Ministry of Economy, Industry and
Competitiveness of Spain.  This work was supported by the National Key R\&D
Program of China (2016YFA0400702) and the National Science Foundation of China
(11873022, 11991053).  The authors acknowledge support from the COST Action
GWverse CA16104. The authors acknowledge the use of the Kepler computer at ARI
Heidelberg, funded by Volkswagen Foundation through the project GRACE 2:
"Scientific simulations using programmable hardware" (VW grants I84678/84680),
and the bwForCluster of the Baden-W\"urttemberg's High Performance Computing
(HPC) facilities, which is supported by the state of Baden-Württemberg through
bwHPC and the German Research Foundation (DFG) through grant INST 35/1134-1
FUGG.

\bibliographystyle{aa}
\newpage
\footnotesize{
\bibliography{ASetal2015}
}

\end{document}

### 2020-07-07 main.tex
ready for resubmission

@@
 interaction, in Section \ref{res} we present and discuss the main properties of
-the simulations output, in Section \ref{gra} we discuss the implications for GW
-astronomy, while Section \ref{res} is devoted to the results summary and
-conclusions.
+the simulations output and the implications for IMBH formation and evolution, in Section \ref{gra} we discuss the implications for GW astronomy, while Section \ref{end} is devoted to the results summary and conclusions.
 
@@
 We note that the lowest value taken for $M_\ibh$ will likely involve mergers with mass ratio $> 0.1$, thus they fall outside the range of IMRIs.
-Nonetheless, exploring the low end of IMBH mass function will help us in better understanding the perspectives of IMBH-BH mergers from the point of view of both low- and high-frequency GW detectors, as discussed in Section XX.
+Nonetheless, exploring the low end of IMBH mass function will help us in better understanding the perspectives of IMBH-BH mergers from the point of view of both low- and high-frequency GW detectors, as discussed in Section \ref{gra}.
 
@@
 The cluster typical radius is thus calculated from the assumed $R_{\rm eff}$ and the adopted mass profile.
-Upon these assumptions an IMBH with mass $M_\ibh = 10^2(10^5)\Ms$ is associated with a cluster mass of $ M_\gc = 1.7\times 10^4(1.7\times 10^7)\Ms$, thus our models ideally span the mass range of young clusters, globular clusters, and dwarf galaxies nuclei.
+Upon these assumptions an IMBH with mass $M_\ibh = 10^2(10^5)\Ms$ is associated with a cluster mass of $ M_\gc = 1.7\times 10^4(1.7\times 10^7)\Ms$, thus our models ideally span the mass range of young clusters, globular clusters, nuclear clusters, and dwarf galaxies nuclei.
 We assume that the IMBH is orbited by two stellar BHs, since the IMBH is expected to be the most massive object in the cluster and the dominant element in determining the dynamics.
+The choice of limiting the number of BH companions to two is dictated by the numerical evidence that IMBHs tend to form after the reservoir of BH population diminished severely through dynamical interactions \citep{zwart02,giersz15}.
+Compared to other works focused on a similar topics, our models do not rely on any  preferential configuration or initial hierarchy for the IMBH-BH-BH system, since we expect that the evolution around the IMBH will be mostly driven by the chaotic interactions involving the compact objects surrounding the IMBH \citep[e.g.][]{konstantinidis13}.
 The orbital eccentricity $e_{1,2}$ is extracted randomly according to a thermal distribution $P(e){\rm d} e = 2e{\rm d}e$, while the semimajor axis $a_{1,2}$ is selected according to the overall cluster density profile with the exception of model S6, in which we extract $a_{1,2} = 0.1-10^4$ AU assuming a distribution flat in logarithmic values.
+This allows us to explore the role of the BHs spatial distribution in determining the IMRIs formation and merger.
+
 In models S0 to S5, the maximum semimajor axis allowed is set equal to the radius within which the host cluster contains two stellar BHs with average mass $30\Ms$.
@@
 Additionally, \ARGdf allows the user to take into account in particles' equations of motion the gravitational field generated by the host stellary system and a dynamical friction term.
-Simulations are halted either if one of the two BH merge with the IMBH, if one of the BHs is ejected away if the simulated time exceeds $t = 1$ Gyr, or if the runtime exceeded 1 hr.
+Simulations are halted either if: one of the two BH merge with the IMBH, one of the BHs is ejected away, the simulated time exceeds $t = 1$ Gyr, or the runtime exceeded 1 hr.
 The $1$ Gyr time limit serves to cope with the fact that IMBH in the range of masses $>10^3\Ms$ are expected to build-up via stellar accretion and mergers with compact remnants over timescales that can range considerably $1-10$ Gyr depending on the formation pathway \citep[see for instance][]{giersz15}.
@@
 Clearly, while the categorization provided suggests three well separate classes, it must be noted that models falling in case c) (mergers) might have undergone a chaotic triple phase, or secular effects that triggered the IMBH-BH merger.
-In fact, figure \ref{fig:example} shows a typical example of one of the simulations performed in which the merger takes place within the simulated time.
-In the example, an IMBH with mass $M_\ibh = 10^2\Ms$ forms a tight binary with a stellar BH with mass $M_\bh = 15\Ms$, the binary is subjected to perturbation of the outer BH with mass $M_\bh = 5\Ms$ that causes a continuous oscillation of the eccentricity up to the point -- around 300 Myr from the beginning of the simulation -- at which the eccentricity peaks at values $\sim 0.999998$ and GW start dominating the IMBH-BH binary evolution which culminate with a merger shortly after.
+Figure \ref{fig:example} shows a typical example of one of the simulations performed in which the merger takes place within the simulated time: an IMBH with mass $M_\ibh = 10^2\Ms$ forms a tight binary with a stellar BH with mass $M_\bh = 15\Ms$, the binary is subjected to perturbation of the outer BH with mass $M_\bh = 5\Ms$ that causes a continuous oscillation of the eccentricity up to the point -- around 300 Myr from the beginning of the simulation -- at which the eccentricity peaks at values $\sim 0.999998$, GW emission kicks in and start dominating the IMBH-BH binary evolution eventually culminating in a merger.
 }
@@
 {\bf 
-
-The amount of both ``direct'' and ``delayed'' merger depends, as outlined in Table \ref{tab:t2}, on the IMBH mass and the model investigated.
+As outlined in Table \ref{tab:t2}, the amount of both ``direct'' and ``delayed'' merger depends on the IMBH mass and the model adopted.
 Figure \ref{fig:gwprob} shows the percentage of total mergers (direct + delayed, hereafter $f_{\rm GW}$) as a function of the IMBH mass for different models.
@@
 
-Another important property that can be inferred from our models is the mass distribution ${\rm d}N/{\rm d}M_{\rm bh}$ of IMRI lighter companion, which is shown in Figure \ref{fig:f8} for models SET0-5 (different cluster density profiles and BH mass spectrum) and Figure \ref{fig:f8} for models SET0, 6 (different stellar metallicity).
+Another important property that can be inferred from our models is the mass distribution ${\rm d}N/{\rm d}M_{\rm bh}$ of the IMRI secondary, which is shown in Figure \ref{fig:f8} for models SET0-5 (different cluster density profiles and BH mass spectrum) and Figure \ref{fig:mbhdist} for models SET0, 6 (different stellar metallicity).
 Comparing SET0, 1, and 3 -- which differ only in the cluster density profile but adopt the same BH mass spectrum \citep{spera17} -- it is apparent that the ${\rm d}N/{\rm d}M_{\rm bh}$ not depend on the environment, but rather on the BH mass spectrum adopted.
@@
 We explored whether the IMBH mass plays a role in shaping the merging BH mass distribution but, on average, we find that the overall distribution remains the same across all the range of $M_\ibh$ explored.
-As shown in Figure \ref{fig:mbhdist}, increasing the stellar metallicity to solar values (SET6) leads to IMRIs with a secondary component mass that remains below $25\Ms$.
+As shown in Figure \ref{fig:mbhdist}, increasing the stellar metallicity to solar values (SET6) implies a reduction of the maximum value of the IMRI secondary mass to $25\Ms$.
 
@@
 On the other hand, it provides clues about the IMBH formation process.
-In fact, if the IMBH formed during cluster's early life, we can expect that the BH mass spectrum isn't altered substantially by dynamics.
-However, if the IMBH develops after dynamical encounters shaped the BH reservoir -- for instance by causing the ejection of the most massive BHs -- we would expect that the IMRI secondary mass would preferentially attains lower values.
+In fact, if the IMBH formed during cluster's early life, we might expect that the mass spectrum of IMRIs secondary maps roughly the stellar BH mass spectrum.
+If, instead, dynamical interactions have enough time to shape the BHs reservoir, we might expect that the mass spectrum of IMRI secondaries will reflect the outcome of stellar dynamics.
 
@@
 Depending on the kick amplitude, the recoil can kick out the IMBH from the cluster \citep[e.g.][]{bockelmann08}, leading it to wander forever outside the cluster.
-In fact, for low-velocity dispersion ($5$ km/s) star clusters the probability to retain a BH with mass $m_\bh> 100 \Ms$ after 1-2 consecutive mergers is rather low, $1-5\%$ \citep{arca20}.
-To place constraints on the IMBH retention probability, we create a catalogue of IMRI mergers proceeding on a step-by-step basis as follows:
+This can significantly affect the retention probability of low-velocity dispersion ($5$ km/s) star clusters, which is limited to $1-5\%$ for BHs with mass $m_\bh \sim 100 \Ms$ that undergo 1-2 consecutive mergers \citep{arca20}.
+
+Assessing the retention probability for IMBHs is crucial to place constraints on their possible presence in star clusters.
+To explore this aspect, we use our models to create a catalogue of IMRI mergers proceeding on a step-by-step basis as follows:
 \begin{enumerate}
@@
 
-The result of this procedure is described in Figure \ref{fig:f11}, which shows the percentage of models for which $v_r < \sigma$. In the case of 
+The result of this procedure is described in Figure \ref{fig:survival}, which shows the percentage of models for which $v_r < \sigma$. In the case of 
 a ''normal'' cluster ($\sigma = 5$ km/s), we find that an IMBH with mass $M_\ibh < 200 \Ms$ gets ejected whenever the merging companion has a mass $m_\bh \geq 10 \Ms$.
@@
 $M_\ibh = 1000\Ms$, the retention probability rapidly drops below $50\%$  if the companion mass exceeds $M_\bh > 20\Ms$.
-Only for quite heavy IMBHs ($M_\ibh \sim 10^4\Ms$) the retention probability attains values $>80\%$ regardless the secondary BH mass.
-In the case of a denser cluster ($\sigma=50$ km/s), we find that a moderate IMBH ($M_\ibh \sim 200-300 \Ms$) have a $50\%$ retention probability if $m_\bh < 30\Ms$, while for $M_\ibh = 1000\Ms$ the BH mass threshold to ensure a $50\%$ retaining probability increases to $m_\bh = 70\Ms$.
+The retention probability attains values $>80\%$ regardless the secondary BH mass only for quite heavier IMBHs ($M_\ibh \sim 10^4\Ms$).
+The picture changes slightly in the case of a denser cluster.
+Assuming $\sigma=50$ km/s, we find that a moderate IMBH ($M_\ibh \sim 200-300 \Ms$) have a $50\%$ retention probability if $m_\bh < 30\Ms$, while for $M_\ibh = 1000\Ms$ the BH mass threshold to ensure a $50\%$ retaining probability increases to $m_\bh = 70\Ms$.
 
-Therefore, localizing an IMBH in the centre of a star cluster and measuring its mass would enable us to get insights on its evolution.
-For instance, the presence of an IMBH with mass $>10^3\Ms$, even in dense clusters, would suggest that the IMBH growth process might be dominated  by matter accretion from disrupted star rather than by mergers with BHs heavier than $30-50\Ms$.
+Our analysis suggests that localizing an IMBH in the centre of a star cluster and measuring its mass would enable us to get insights on the IMBH evolution.
+For instance, in the case of $M_\ibh > 10^3\Ms$ would suggest that the IMBH build-up was unlikely dominated by mergers with stellar BH companions, rather the major contribution came from accreted matter from disrupted stars.
 }
@@
 {\bf
-Since an IMBH-BH merger cause an inevitable variation of the IMBH spin, this quantity might be useful to get insights on the IMBH evolution.
-To support this idea, we create a sample of IMBH-BH mergers as follows.
+
+In this section we investigate whether the effects of a merging events can be encoded in the remnant IMBH spin.
+
+To support this idea, we create a sample of IMBH-BH mergers based on our previous experiments as follows.
 We select an IMBH with mass of either $M_\ibh = 10^2 - 10^3 - 10^4 - 10^5$ and spin $S_\ibh = 0.1 - 0.5 - 0.9$ and we merge it with a stellar BH with mass in the range $3 - 60 \Ms$ drawn randomly and spin drawn accordingly to a Gaussian distribution with mean $S_\bh = 0.7$ -- i.e.
@@
 We see that as long as the mass ratio remains below $10^{-2}$ -- which implies an $M_\ibh > 10^4 \Ms$ -- the IMBH spin is not affected by the merger.
-However, for IMRIs with a mass ratio > 0.01, the remnant IMBH spin can change significantly.
-For mass ratios in the range $q = 0.01-0.1$ the spin variation is $\sim \pm 0.1$ with respect to the initial value, whereas at larger mass ratio values we see that the spin tend to move toward values close to the average value assumed for the BH spin distribution, being the remnant spin $S_r \sim 0.8\pm 0.2$.
+However, for IMRIs with a mass ratio > 0.01, the remnant IMBH spin can change significantly, with a spin variation $\sim \pm 0.1$ for mass ratios in the range $q = 0.01-0.1$.
+At mass ratio $q>0.1$, the remnant IMBH spin ($S_r \sim 0.8\pm 0.2$) tends to attain a value close to the average value assumed for the BH spin distribution.
 The peculiar dependence between the remnant spin and the IMRI mass ratio has important consequences for the IMBH evolution.
@@
 On the other hand,
-if the IMBH formed via multiple mergers in a stellar environment rich in BHs, the remnant spin can provide clues on the spin distribution of the underlying population of stellar BHs.
+if the IMBH formed via multiple mergers in a ''BH-rich'' stellar environment, the remnant spin can provide clues on the spin distribution of the underlying population of stellar BHs.
 
-To further investigate this point, we explore the effects of a series of subsequent mergers on the IMBH final spin in the case of 
-an IMBH mass value  that ensure a retention probability of at least $50\%$ in an IMRI merger event involving a BH smaller than $40\Ms$.
-From Figure \ref{fig:survival} and Figure\ref{fig:f11a} we thus select $M_\ibh = 10^3\Ms$, which satisfies the requirement above, and set its spin to either $S_\ibh = 0.1-0.5-0.9$.
+To further investigate this point, we explore the effects of a series of subsequent mergers on the IMBH final spin.
+We assume $M_\ibh = 10^3\Ms$, i.e.
+a mass such to ensure a retention probability of at least $50\%$ in an IMRI merger event involving a BH smaller than $40\Ms$ (see Figures  \ref{fig:survival} and \ref{fig:f11a}).
+We set the IMBH spin to either $S_\ibh = 0.1-0.5-0.9$.
 For each spin value, we model ten consecutive mergers with stellar BHs with masses $3-60\Ms$ and spin drawn from a Gaussian distribution with average $S_\bh = 0.5$ and dispersion 0.1.
-This sequence represents an {\it IMBH merger tree}.
-For each value of the spin we create 100 merger trees and calculate the IMBH spin evolution as shown in Figure \ref{fig:f11b}.
+The resulting merger sequence represents an {\it IMBH merger tree}.
+For each value of the spin we thus create 100 merger trees and calculate the IMBH spin at each successive merger as shown in Figure \ref{fig:f11b}.
 We note that all models tend to converge toward the mean value of the adopted spin distribution for stellar BHs, thus suggesting that it could be possible to link the IMBH spin with the overall spin distribution of stellar BHs inhabiting the star cluster.
-Infact, complementing a measure of the IMBH spin with the spin distribution inferred from stellar BH mergers observed as GW sources can help in unravelling the IMBH evolution, whether it was driven by mergers with compact objects or by stellar feeding.
+In fact, complementing a measure of the IMBH spin with the spin distribution inferred from stellar BH mergers observed as GW sources can help in unravelling the IMBH evolution, whether it was driven by mergers with compact objects or by stellar feeding.
 }
@@
 This setup implies that the GW emission connected with our modelled mergers can populate a wide range of frequencies, from milli- to deca-Hz.
-Figure \ref{fig:f13} show the characteristic amplitude as a function of the frequency for a sample of IMRI mergers with different IMBH mass, assuming they are located at redshift $z=0.1$ ($\sim 460$ Mpc) and an observation time of 4 yr.
-We compare the modelled signal with the sensitivity curve of several detectors, namely LISA, ALIA, DO, DECIGO, LIGO, and the Einstein Telescope (ET).
+Figure \ref{fig:f13} show the characteristic amplitude \citep{kocsis12,ASLiK18,seoane18,robson19} as a function of the frequency for a sample of IMRI mergers with different IMBH mass, assuming they are located at redshift $z=0.1$ ($\sim 460$ Mpc) and an observation time of 4 yr.
+We compare the modelled signal with the sensitivity curve of several detectors, namely the laser interferometer space antenna \citep[LISA,][]{eLISA13,amaro17lisa}, the advanced laser interferometer antenna \citep[ALIA,][]{bender13}, the decihertz observatory \citep[DO,]{arca19}, the Deciherz Gravitational-Wave Observator \citep[DECIGO,]{Kawamura11}, LIGO \citep{abbott16}, and the Einstein Telescope \citep[ET]{punturo10}.
 We see that mergers involving IMBHs with masses $< 10^5\Ms$ are promising multiband sources that can be seen in one detector during the inspiral phase and in another during the merger.
@@
 One important parameter that could be inferred from GW observations is the eccentricity of the source.
-To better understand whether our IMRI models are expected to retain a significant eccentricity while transiting across different observational bands, we show in Figure \ref{fig:f10} the average value of the eccentricity calculated when IMRIs cross the milli-Hz, deci-Hz, and Hz bands for all simulations set.
-It is apparent that even when emitting low-frequency GWs, IMRIs have already significantly circularized, although apparently lower-mass IMRIs tend to have slightly larger eccentricities.
+To better understand whether our IMRI models are expected to retain a significant eccentricity while transiting across different observational bands, we show in Figure \ref{fig:f10} the average value of the eccentricity calculated when IMRIs cross the frequency windows $10^{-3}-10^{-1}-1$ Hz for all simulation sets.
+It is apparent that even when emitting low-frequency GWs, our modelled IMRIs have already significantly circularized, although apparently lower-mass IMRIs tend to have slightly larger eccentricities.
 The fact that our IMRIs are substantially circular when becoming observable to GW detectors has implications on their detectability, as we show in the next section.
@@
 
-{\bf In fact, in the last decade a number of works pointed out the potential presence of IMBHs in Galactic globular clusters, although in most cases the results were inconclusive.
-Concerning clusters orbiting closer than 8 kpc to us candidates include: 47Tuc \citep{kiziltan17}, NGC6266 \citep{abbate19}, NGC6128 and NGC288 \citep{sollima16}, NGC6388 and NGC2808 \citep{miocchi07,lanzoni07}.
+{\bf Over the last decade a number of works pointed out the potential presence of IMBHs in Galactic globular clusters, although in most cases the results were inconclusive.
+The family of clusters orbiting closer than 8 kpc to us include several IMBH host candidates: 47Tuc \citep{kiziltan17}, NGC6266 \citep{abbate19}, NGC6128 and NGC288 \citep{sollima16}, NGC6388 and NGC2808 \citep{miocchi07,lanzoni07}.
+
+However, whether this clusters actually host an IMBH is a still open question.
 For instance, the inferred value for the 47Tuc IMBH mass goes from $M_\ibh > 2,000\Ms$ \citep{kiziltan17} to substantially lower values $\ll 1,000\Ms$ \citep{abbate19b}, depending on the observational technique adopted.
 A similar discussion involves other clusters, like NGC6388 \citep{lanzoni13,lutzgendorf13}.
-Therefore, LISA might play a crucial role in unravelling the presence (or not) of IMBHs in the Galaxy, at least the closest one.
+Therefore, LISA might play a crucial role in unravelling the presence (or not) of IMBHs in the Galaxy, at least in the closest ones.
 
-Not only, in fact LISA can also be used to provide clues about the presence of IMBHs in nearby galaxies.
-For instance, it has been recently suggested that the Large Magellanic Cloud might be harbouring an IMBH with a mass in the range $4\times 10^3-10^4\Ms$ \citep{erkal19} and up to $10^7\Ms$ \citep{boyce17}, and that some of the clusters residing in the cloud can host IMBHs as well with masses in the range $10^3-10^4\Ms$ \citep{gualandris07}.
-Assuming a distance to the LMC $D_L = 49.97 \pm 1.13$ kpc \citep{pietrzy13}, we find that LISA might deliver observations of {\it Magellanic} IMRIs with an $SNR = 8-40$, with the lower(upper) value corresponding to an IMBH with mass $10^3\Ms$($10^4\Ms$) and a BH companion of $30\Ms$.
+LISA can also enable us to probe IMBHs even in nearby galaxies.
+For instance, it has been recently suggested that the Large Magellanic Cloud (LMC) might be harbouring an IMBH with a mass in the range $4\times 10^3-10^4\Ms$ \citep{erkal19} and up to $10^7\Ms$ \citep{boyce17}, while some of the clusters residing in the LMC can host IMBHs with masses in the range $10^3-10^4\Ms$ \citep{gualandris07}.
+Assuming a distance to the LMC $D_L = 49.97 \pm 1.13$ kpc \citep{pietrzy13}, LISA might deliver observations of {\it Magellanic} IMRIs with an SNR$= 8-40$, with the lower(upper) value corresponding to an IMBH with mass $10^3\Ms$($10^4\Ms$) and a BH companion of $30\Ms$.
 }
@@
 \subsection{IMRIs merger rate}
-%{\color{red} TO BE REVISED EVERYTHING BELOW!\\
-%In particular, the discussion about the MW needs to be completely reshaped because the power-law approximation is no longer valid. We could use 
-%an approximate stuff like 35./180. GCs might have an IMBH with mass 1,000 thus probability for IMRI is X, thus the probability for the MW is tot, thus
-%the probability for MW analogs is tot, something like this could be ok-ish.
-%}
-%
-%Previous studies based on full consistent N-body simulations of star clusters containing IMBHs with various masses and general properties  \citep{konstantinidis13,haster16,leigh14, macleod16} have shown that binary formation involving an IMBH takes place at a rate of $R_{\rm bin} \sim 10^{-7}$ yr.
-Assuming typical ages for globular-like star clusters of $t_{\rm age}\sim 10^{10}$ yr and assuming that IMBH buildup occurs in the clusters early lifetime ($\lesssim 1$ Gyr), we can use the merger probability fitting function depicted in Equation \ref{fmerg} to infer the total number of IMRIs formed for a given IMBH mass and over a cluster lifetime $t_{\rm age}$
-%\begin{equation}
-%    N_\gc(M_\ibh) = R_{\rm bin}t_{\rm age}f_{\rm mer} \sim 15\left(\frac{M_{\ibh}}{10^2\Ms}\right)^{0.38},
-%\end{equation}
-%ranging from $\Gamma_{\imri} = 15-90$ yr$^{-1}$ for $M_\ibh = 10^2-10^4\Ms$, respectively.
-%To put such a quantity in the context of MW-like galaxies, we need to make assumptions on the IMBH putative mass function.
-Assuming that the initial mass function of GCs follows a power-law and exploiting Equation \ref{mcmibh}, we can write the IMBH mass function as $f(M_\ibh) = k (M_\ibh/10^\alpha)^{1/\beta}$.
-The normalization constant $k$ can be calculated by assuming that the mass in clusters constitute a fraction of the total galaxy mass:
-%\begin{equation}
-%k = \frac{\delta M_g (2-s)}{(M_{\gc 2}^{2-s} - M_{\gc 1}^{2-s})},
-%\label{normal}
-%\end{equation}
-%with $\delta = 5\times 10^{-4}$ \citep{webb15,belczinski17}, $M_g = 6\times 10^{10}\Ms$ the Milky Way stellar mass, and $M_{\gc 1,2} = (5\times 10^3 - 8\times 10^6)\Ms$ the range of GC initial mass. 
-%Combining equations above, we can infer the total number of IMRIs  MW-like galaxies as
-%\begin{align}
-%    N_{\rm MW} =& f_\ibh N_\gc \int_{M_{\ibh ,1}}^{M_{\ibh ,2}} \Gamma(M_\ibh) \times \nonumber \\
-%    & \times f(M_\ibh) \frac{\derd M_\gc}{\derd M_\ibh} {\rm d}M_\ibh,
-%\end{align}
-%where $f_\ibh N_\gc$ is the number of GCs containing an IMBH, and the term $\derd M_\gc / \derd M_\ibh$ is used to perform a change of variable from the GC to the IMBH mass.
-The integral has analytical solution in the form
-%\begin{equation}
-%N_{\rm MW} = K \frac{M_{\ibh ,2}^{\beta + b(1-s)} - M_{\ibh ,1}^{\beta + b(1-s)}}{\beta + b(1-s)},
-%\end{equation}
-%with the parameter $K$ containing all the constant factors.
-%Assuming $t_{\rm age} = 10$ Gyr and in the IMBH mass range of $10^2 - 10^4\Ms$, we derive an IMRI merger rates for MW-like galaxies of
-%\begin{equation}
-%\Gamma_{\rm MW} = 2.26\times 10^{-5} {\rm ~yr} \left(\frac{10{\rm ~Gyr}}{t_{\rm age}}\right)\left(\frac{f_\ibh}{0.2}\right)\left(\frac{N_\gc}{180}\right).
-%\label{eqMW}
-%\end{equation}
-%The number of MW-analogs in the local Universe (redshift $z<0.1$) is roughly proportional to the luminosity distance $D_L$, namely $P_{\rm MW} = 4\pi/3 \times 0.0116(2.26)^{-3}D_L^3$ with $D_L$ expressed in Mpc \citep{abadie10}.
-Thus a rough estimate of potential IMRIs developing in MW-like galaxies in the local Universe is given by $\Gamma_{\rm MW} \times P_{\rm MW} = 10.5$ yr$^{-1}$.
-%This is a simple estimate, though, which not account for the distribution of galaxies across different redshift or the actual volume within which a detector is sensitive.
 
-The launch of the LISA detector and the start of operations of the next generation of GW observatories like the Einstein Telescope (ET) will enable us to observe this kind of objects at cosmological distances.
-Therefore, to infer the IMRI merger rates, we need to take into account in our calculation how the number density of galaxies varies across redshift $z$.
+The launch of the LISA detector and the start of operations of the next generation of GW observatories like ET will enable us to unveil IMRIs at cosmological distances, provided that their number is sufficiently large to guarantee detection within the mission lifetime.
+
+To make predictions on IMRIs detectability, in this section we infer the merger rate for different detectors.
+To perform such calculations we need to account for the variation of galaxies number density across different redshifts $z$.
 The GW source {\it horizon} determines the maximum distance in space, or the redshift $z_{\rm hor}$, at which the source signal is detected with a threshold signal-to-noise ratio (SNR), namely:
@@
 with $f_{1,2}$ the initial and final frequency of the GW signal, $h_c(f,z)$ its characteristic strain, and $S_n(f)$ its sensitivity.
-To determine this quantity, we integrate the final stage of the IMRI signal assuming an observation time of 4 yr -- i.e.
-the nominal duration time of the LISA mission -- and we calculate the value of $z_{\rm hor}$ at which we get an SNR of 15.
-We assume the set of cosmological parameters measured by the Planck mission, namely $H_0 = 67.74$ km/s/Mpc$^{3}$, $\Omega_m = 0.3089$, $\Omega_\Lambda = 0.6911$ \citep{planck15}.
-To calculate $z_{\rm hor}$, we vary the IMBH mass in the range $50-10^6\Ms$ assuming that the companion has a mass of either $10$ or $30\Ms$.
-Figure \ref{fig:fhor} shows how the horizon redshift changes for four different detectors: the Laser Interferometer Space Antenna \citep[LISA\footnote{\url{https://www.elisascience.org/}},][]{amaro12}, the Deciherz Gravitational-Wave Observatory \citep[DECIGO\footnote{\url{http://tamago.mtk.nao.ac.jp/spacetime/decigo_e.html}},][]{seto01}, the Einstein Telescope \citep[ET\footnote{\url{http://www.et-gw.eu/}},][]{punturo10}, and LIGO.
+To determine $z_{\rm hor}$ we integrate the final stage of the IMRI signal assuming an observation time of 4 yr -- i.e.
+the nominal duration time of the LISA mission -- and we assume an SNR of 15.
+We adopt the set of cosmological parameters measured by the Planck mission, namely $H_0 = 67.74$ km/s/Mpc$^{3}$, $\Omega_m = 0.3089$, $\Omega_\Lambda = 0.6911$ \citep{planck15}.
+Moreover, we vary the IMBH mass in the range $50-10^6\Ms$ assuming that the companion has a mass of either $10$ or $30\Ms$.
+Figure \ref{fig:fhor} shows how the horizon redshift changes for four different detectors: LIGO\footnote{https://www.ligo.caltech.edu/}, LISA\footnote{\url{https://www.elisascience.org/}}, DECIGO\footnote{\url{http://tamago.mtk.nao.ac.jp/spacetime/decigo_e.html}}, and ET\footnote{\url{http://www.et-gw.eu/}}.
 
@@
 \section{Conclusions}
+\label{end}
 

### 2020-07-13 main.tex
final remarks added

@@
 \authorrunning{Arca Sedda, Amaro-Seoane, Chen}
-\author{Manuel Arca Sedda \inst{1} \and Pau Amaro-Seoane \inst{2,}\inst{3,}\inst{4,}\inst{5} \and Xian Chen \inst{6,}\inst{5} }
+\author{Manuel Arca Sedda \inst{1} \and Pau Amaro-Seoane \inst{2,}\inst{3,}\inst{4,}\inst{5} \and Xian Chen \inst{6,}\inst{3} }
 
@@
          \and         
-			  Institute of Space Sciences (ICE, CSIC) \& Institut d'Estudis Espacials de Catalunya (IEEC) at Campus UAB, Carrer de Can Magrans s/n 08193 Barcelona, Spain
+			  Universitat Polit{\`e}cnica de Val{\`e}ncia, IGIC, 46022 Valencia, Spain
+		\and         
+			  Kavli Institute for Astronomy and Astrophysics at Peking University, Beijing 100871, P.R. China
 		\and	  
@@
 		\and
-			  Kavli Institute for Astronomy and Astrophysics at Peking University, Beijing 100871, P.R. China	
-		\and
 			Astronomy Department, School of Physics, Peking University, Beijing 100871, P.R. China	             
 \\		\email{m.arcasedda@gmail.com}			
-\\    	\email{pau@ice.cat}
+\\    	\email{amaro@upv.es}
 \\		\email{xian.chen@pku.edu.cn }
@@
 or via multiple interactions and mergers between stars and stellar-mass BHs \citep{giersz15}. 
-Unfortunately, a striking observational evidence for the presence of IMBHs inhabiting GCs is still missing due to the little dynamical effects that these objects have on their surroundings \citep[for recent reviews see][]{mezcua17,greene19}.
+{\bf Aside from the scenario above, several mechanisms have been proposed for IMBH formation. In fact, IMBHs with masses in the range 
+$10^2-10^4\Ms$ can form out of the direct collapse of massive stars extremely poor in metals \citep{madau01,bromm02,ohkubo09,spera17} or of gaseous clouds in the early Universe \citep{latif13}, or can form in high redshift, metal poor, galactic halos \citep{bellovary11}.
+A further possibility is that IMBHs form in the centre of satellite galaxies, later accreted in their host galaxy halo \citep{bellovary10}, or can form in galactic nuclei, either in AGN accretion discs \citep{mckernan12} or in galactic discs circumnuclear regions \citep{taniguchi00}.}
+
+Unfortunately, a striking observational evidence for the presence of IMBHs inhabiting GCs is still missing due to the {\bf impossibility to resolve the region in which they dominate dynamics} \citep[for recent reviews see][]{mezcua17,greene19}.
 Indeed, models suggest that several processes can mimic an IMBH, like anisotropies inthe GC kinematic  properties \citep{zocchi}, or the presence of a dense cluster of stellar mass BHs -- namely a BH subsystem -- that dominate the inner cluster centre \citep{AAG18b,AS16,vandermarel10}.
@@
 \citep{noyola10,lu13,lanzoni13,kiziltan17} and their mass and influence radius might be possibly connected with the host cluster observational 
-properties \citep{AAG18a}.
+properties \citep{Baumgardt17,AAG18a,AAG19}.
 Due to this, finding an unique way to unravel the presence of IMBHs in GCs represents one of the most interesting challenges in modern astronomy.
 Beside this, the presence of an IMBH sitting in the centre of a dense cluster represents a scenario particularly appealing from the perspectives of gravitational waves (GW) astronomy.
-Indeed, a compact remnants orbiting the IMBH can enter a regime where GWs emission dominates, leading to the formation of an intermediate mass-ratio inspiral \citep[IMRI,][]{konstantinidis13,leigh14,haster16,macleod16}, a class of sources possible audible with the next generation of GW observatories like LISA \citep{seoane07,amaro12,seoane18}.
+Indeed, a compact remnants orbiting the IMBH can enter a regime where GWs emission dominates, leading to the formation of an intermediate mass-ratio inspiral \citep[IMRI,][]{konstantinidis13,leigh14,haster16,macleod16}, a class of sources possible audible with the next generation of GW observatories like LISA \citep{Will04,seoane07,amaro12,seoane18}.
 However, in the highly dense regions that characterize star clusters centres, the formation of IMRIs is not a smooth process.
@@
 Differently from galactic nuclei, where the SMBH remains well seated in the galactic potential well, the IMBH motion makes hard the use of any analytical approach to solve IMRIs dynamics.
-Quantifying the branching ratio for IMRIs formation constitute a fundamental step to assess the probability to observe these GW sources with the next generation of space-based detectors like LISA\footnote{\url{https://www.elisascience.org/}} \citep{seoane07,amaro12}, TianQin \citep{tianqin16} or Taiji \citep{taiji17}.
+Quantifying the branching ratio for IMRIs formation constitute a fundamental step to assess the probability to observe these GW sources with the next generation of space-based detectors like LISA\footnote{\url{https://www.elisascience.org/}} \citep{Will04,seoane07,amaro12}, TianQin \citep{tianqin16} or Taiji \citep{taiji17}.
 In this paper, we model the potential formation of an IMRI from the interactions between an IMBH and two stellar mass BHs.
@@
 We simulate the evolution of the innermost region of the cluster, modelling the IMBH and two stellar mass BHs as live particles and
-the remaining cluster as an external static potential. In order to explore the parameter space, we create six different models, each one consisting 
-of 4000 simulations gathered in four different sub-classes, depending on the IMBH mass, for a total of 48,000 simulations. Our model is sketched in Figure \ref{f1}.
+the remaining cluster as an external static potential.
+In order to explore the parameter space, we create 7 different models, each one consisting of 4000 simulations gathered in four different sub-classes, depending on the IMBH mass, for a total of \manuel{28,000} simulations.
+Our model is sketched in Figure \ref{f1}.
 
@@
     \includegraphics[width=7cm]{triple}
-    \caption{Sketch of the IMBH-BH-BH triple configuration.}    
+    \caption{Sketch of the IMBH-BH-BH triple configuration.
+{\bf We mark the main quantities that characterise the triple -- IMBH mass ($M_\ibh$), stellar BH masses ($M_{\rm bh 1,2}$, orbital semimajor axis and eccentricity of the IMBH-BH1 ($a_1,~e_1$) and IMBH-BH2 ($a_2,~e_2$) systems -- and the host cluster -- gravitational potential ($\Phi_\gc$), total mass ($M_\gc$), typical radius ($r_\gc$), and velocity dispersion ($\sigma_\gc$).} }
 \label{f1}
@@
 
-We vary the central IMBH mass in four classes, namely ${\rm Log}(M_\ibh/\Ms) = 2-3-4-5$.
+We vary the central IMBH mass in four classes, namely ${\rm Log}(M_\ibh/\Ms) = 2,~3,~4,~5$.
 This range covers typical values of putative IMBH masses forming in stellar systems of various sizes, from young and open clusters, to globular clusters, and up to low-mass nuclear clusters and dwarf galaxies.
 We note that the lowest value taken for $M_\ibh$ will likely involve mergers with mass ratio $> 0.1$, thus they fall outside the range of IMRIs.
-Nonetheless, exploring the low end of IMBH mass function will help us in better understanding the perspectives of IMBH-BH mergers from the point of view of both low- and high-frequency GW detectors, as discussed in Section \ref{gra}.
+Nonetheless, exploring the low end of IMBH mass function will help us in better understanding the perspectives of IMBH-BH mergers from the point of view of both low- \citep[e.g.][]{Will04,seoane18} and high- \citep[e.g.][]{MandelEtAl2008,gair11,abbott17f} frequency GW detectors, as discussed in Section \ref{gra}.
 
@@
 
-These results have two main implications.
-On the one hand, the IMRI secondary mass tells us something about the mass spectrum of BHs lurking around an IMBH.
-On the other hand, it provides clues about the IMBH formation process.
-In fact, if the IMBH formed during cluster's early life, we might expect that the mass spectrum of IMRIs secondary maps roughly the stellar BH mass spectrum.
-If, instead, dynamical interactions have enough time to shape the BHs reservoir, we might expect that the mass spectrum of IMRI secondaries will reflect the outcome of stellar dynamics.
+These results have two main implications. \manuel{
+Since the IMRI secondary mass reflects the underlying BH mass spectrum, this quantity 
+encodes information on the population of BHs lurking in the host cluster.
+If dynamics had enough time to affect BHs -- e.g.
+causing the ejection of the most massive via strong scatterings -- or the reservoir of BHs have diminished during the IMBH build-up, the IMRI companion mass distribution will tell us how strongly dynamical processes affected BHs.
+If, instead, dynamics did not play a major role in shaping the IMBH growth, we would expect that the mass spectrum of IMRI companion would resemble the typical mass spectrum of BHs forming out of a standard stellar initial mass function \citep[e.g.][]{kroupa01}.}
 
@@
     Mass distribution of the IMRI secondary for SET0 to 5. Each color corresponds to a different set to facilitate the comparison between different panels and figures. 
-    %Bottom panel: the same as above, but differentiating for different IMBH masses: $10^2\Ms$ (straight line), $10^3\Ms$ (dashed line), $10^4\Ms$ (dashed dotted line), $10^5\Ms$ (dotted line) as indicated in the legend.
-Each color corresponds to a different set to facilitate the comparison between the upper and lower panels.
+    Dashed lines mark the mass function adopted for stellar BHs.
     }
@@
 Promptly after a merger event, the anysotropic emission of GWs can impart a recoil kick to the merger product, depending on the mass and spin of the two merging objects \citep{campanelli07,gonzalez07,lousto08,lousto12}.
-Depending on the kick amplitude, the recoil can kick out the IMBH from the cluster \citep[e.g.][]{bockelmann08}, leading it to wander forever outside the cluster.
+Depending on the kick amplitude, the recoil can kick out the IMBH from the cluster \citep[e.g.][]{bockelmann08,fragione17c}, leading it to wander forever outside the cluster.
 This can significantly affect the retention probability of low-velocity dispersion ($5$ km/s) star clusters, which is limited to $1-5\%$ for BHs with mass $m_\bh \sim 100 \Ms$ that undergo 1-2 consecutive mergers \citep{arca20}.
@@
 \item we divide the IMBH mass range -- $M_\ibh = 10^2-5\times 10^5\Ms$ -- in 15 values evenly distributed in logarithmic values;
-\item for each IMBH mass, we create a sample of 100 stellar BHs with masses evenly drawn in the $M_\bh = 3.5-80 \Ms$ range;
+\item for each IMBH mass, we create a sample of 100 stellar BHs with masses evenly drawn in the $M_\bh = 3.5-80 \Ms$ range.
+\manuel{This conservative choice allows us to explore from a general perspective the possible ejection of the IMBH via GW recoil and cope with our ignorance about the actual mass spectrum of stellar BHs involved in an IMRI.};
 \item we associate to the IMBH and BH a spin randomly drawn between 0-1;
@@
 
-Figure \ref{fig:f11a} shows the value of the remnant IMBH spin as a function of the IMRI mass ratio.
+\manuel{As in the previous section, for each merger event we calculate the merger remnant mass, spin, and recoil kick using the numerical relativity fitting formulae described in \cite{jimenez17} following \cite{arca20}.} Figure \ref{fig:f11a} shows the value of the remnant IMBH spin as a function of the IMRI mass ratio.
 
@@
 The peculiar dependence between the remnant spin and the IMRI mass ratio has important consequences for the IMBH evolution.
-One the one hand, if the IMBH formed from the collapse of a gaseous cloud or a very massive star born out of stellar collisions and reach masses $\gtrsim 10^4\Ms$, measuring its spin in a IMRI merger would provide us with information on the processes that regulated the IMBH very formation.
+One the one hand, if the IMBH formed from the collapse of a gaseous cloud or a very massive star born out of stellar collisions and reach masses $\gtrsim 10^4\Ms$, measuring its spin in a IMRI merger would provide us with information on the processes that regulated the IMBH formation.
 On the other hand,
@@
 For each value of the spin we thus create 100 merger trees and calculate the IMBH spin at each successive merger as shown in Figure \ref{fig:f11b}.
-We note that all models tend to converge toward the mean value of the adopted spin distribution for stellar BHs, thus suggesting that it could be possible to link the IMBH spin with the overall spin distribution of stellar BHs inhabiting the star cluster.
+We note that all models tend to converge toward the \manuel{same region  of the spin-mass plane, likely close to the spin value adopted for stellar BHs}, thus suggesting that it could be possible to link the IMBH spin with the overall spin distribution of stellar BHs inhabiting the star cluster.
 In fact, complementing a measure of the IMBH spin with the spin distribution inferred from stellar BH mergers observed as GW sources can help in unravelling the IMBH evolution, whether it was driven by mergers with compact objects or by stellar feeding.
@@
 We see that mergers involving IMBHs with masses $< 10^5\Ms$ are promising multiband sources that can be seen in one detector during the inspiral phase and in another during the merger.
-The number of regions in which a detector is sensitive traversed by an IMRI widens at increasing the IMBH mass, in fact in principle an IMBH with mass $<10^3\Ms$ can be seen across the whole milli-decaHz frequency range.
 
@@
 \end{equation}
-with the slope $s = 2.2$ and the normalization constant 
+with the slope $s = 2.2$\footnote{{\bf Note that this is compatible with the expected initial mass function of young and old star clusters in galaxies \citep[e.g.][]{gieles09}.}} and the normalization constant
 \begin{equation*}
@@
 The physics that regulate IMBH formation is still debated and partly unknown.
-Depending on the formation scenario, models suggest that the IMBH growth can occur either on short ($\sim 1$ Gyr) or long ($\simeq 5-10$ Gyr) timescales.
-As discussed recently, {\it fast} IMBHs could outnumber those forming slowly \citep{giersz15,AAG19}, thus in our calculations we assume $t_{\ibh ,f} = 2$ Gyr.
-The formation of an IMRI scales with the mass-segregation timescale in the host cluster, which is expected to be of the order of $\sim 0.1-1$ Gyr, while for $t_\gw$ we calculate, from our models, the value at which the number of mergers is half the total number, i.e.
+Depending on the formation scenario, models suggest that the IMBH growth can occur either on short ($\lesssim 1$ Gyr) or long ($\simeq 5-10$ Gyr) timescales.
+As discussed recently, {\bf slowly formed IMBHs could outnumber those forming rapidly by a factor 3-5 \citep{giersz15,AAG19}, thus we assume a weighted formation time defined as $t_{\ibh ,f} = (2/3\times 9) + (1/3\times 0.05) = 2$ Gyr.
+} The formation of an IMRI scales with the mass-segregation timescale in the host cluster, which is expected to be of the order of $\sim 0.1-1$ Gyr, while for $t_\gw$ we calculate, from our models, the value at which the number of mergers is half the total number, i.e.
 $N_\gw(t_\gw) = 0.5 N_\gw$.
@@
 \label{end}
-
+{\bf 
 In this work we studied the dynamical interaction of an IMBH with two stellar BHs under the assumption
@@
 At $M_\ibh>10^4\Ms$, a merger event won't change the IMBH spin, whereas the remnant spin changes significantly if $M_\ibh\simeq10^2-10^3\Ms$.
-This implies that measuring the IMBH spin prior and after an IMRI can shed a light on the spin distribution of stellar BHs and on the processes that drove the IMBH build-up [Figures \ref{fig:f11a}-\ref{fig:11b}];
+This implies that measuring the IMBH spin prior and after an IMRI can shed a light on the spin distribution of stellar BHs and on the processes that drove the IMBH build-up [Figures \ref{fig:f11a}-\ref{fig:f11b}];
 \item LISA can help to unravel the presence of IMBHs in our neighbourhood.
@@
 \end{itemize}
+}
 

### 2020-07-13 main.tex
Final 13 july 2020

@@
 the remaining cluster as an external static potential.
-In order to explore the parameter space, we create 7 different models, each one consisting of 4000 simulations gathered in four different sub-classes, depending on the IMBH mass, for a total of \manuel{28,000} simulations.
+In order to explore the parameter space, we create 7 different models, each one consisting of 4000 simulations gathered in four different sub-classes, depending on the IMBH mass, for a total of {\bf 28,000} simulations.
 Our model is sketched in Figure \ref{f1}.
@@
 
-These results have two main implications. \manuel{
+These results have two main implications. {\bf
 Since the IMRI secondary mass reflects the underlying BH mass spectrum, this quantity 
@@
 \item for each IMBH mass, we create a sample of 100 stellar BHs with masses evenly drawn in the $M_\bh = 3.5-80 \Ms$ range.
-\manuel{This conservative choice allows us to explore from a general perspective the possible ejection of the IMBH via GW recoil and cope with our ignorance about the actual mass spectrum of stellar BHs involved in an IMRI.};
+{\bf This conservative choice allows us to explore from a general perspective the possible ejection of the IMBH via GW recoil and cope with our ignorance about the actual mass spectrum of stellar BHs involved in an IMRI.};
 \item we associate to the IMBH and BH a spin randomly drawn between 0-1;
@@
 
-\manuel{As in the previous section, for each merger event we calculate the merger remnant mass, spin, and recoil kick using the numerical relativity fitting formulae described in \cite{jimenez17} following \cite{arca20}.} Figure \ref{fig:f11a} shows the value of the remnant IMBH spin as a function of the IMRI mass ratio.
+{\bf As in the previous section, for each merger event we calculate the merger remnant mass, spin, and recoil kick using the numerical relativity fitting formulae described in \cite{jimenez17} following \cite{arca20}.} Figure \ref{fig:f11a} shows the value of the remnant IMBH spin as a function of the IMRI mass ratio.
 
@@
 For each value of the spin we thus create 100 merger trees and calculate the IMBH spin at each successive merger as shown in Figure \ref{fig:f11b}.
-We note that all models tend to converge toward the \manuel{same region  of the spin-mass plane, likely close to the spin value adopted for stellar BHs}, thus suggesting that it could be possible to link the IMBH spin with the overall spin distribution of stellar BHs inhabiting the star cluster.
+We note that all models tend to converge toward the {\bf same region of the spin-mass plane, likely close to the spin value adopted for stellar BHs}, thus suggesting that it could be possible to link the IMBH spin with the overall spin distribution of stellar BHs inhabiting the star cluster.
 In fact, complementing a measure of the IMBH spin with the spin distribution inferred from stellar BH mergers observed as GW sources can help in unravelling the IMBH evolution, whether it was driven by mergers with compact objects or by stellar feeding.
